### 2016-07-26 src/ack.tex
Renamed the ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\section{Acknowledgements}
The authors are grateful for the assistance and support of the following people
and institutions without which this work would not have been possible.

\textbf{FIXME!}

This work has been supported by the US Department of Energy, Offices of Nuclear
Energy (DOE-NE) and Energy Efficiency and Renewable Energy (DOE-EERE), and by
the ORNL Undergraduate Research Participation Program, which is sponsored by
ORNL and administered jointly by ORNL and the Oak Ridge Institute for Science
and Education (ORISE). This work was also supported in part by the Oak Ridge
National Laboratory Director's Research and Development Fund. ORNL is managed by
UT-Battelle, LLC, for the US Department of Energy under contract no.
DE-AC05-00OR22725. ORISE is managed by Oak Ridge Associated Universities for
the US Department of Energy under contract no. DE-AC05-00OR22750.

\textbf{LDRD ACK?!}

### 2016-07-26 src/intro.tex
Renamed the ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\section{Introduction}

High performance modeling and simulation software is hard to use. Much of the
challenge comes from the inherent nature of the science
under consideration, but perhaps just as much of the problem comes from
focusing very heavily on raw compute performance. Focusing on performance is
understandable, given the field, but it leaves the rest of us to figure out how
to actually use the software in a way that scales for a much larger set of
users, many of whom may be novices or migrate between software packages regularly.

In previous work, Billings et. al., discovered through requirements gathering
interviews that many of the difficulties using high performance modeling and
simulation software fall broadly into five distinct categories,
\cite{billings_cbhpc}. This includes input generation and preprocessing (also
called ``model setup''); job execution and monitoring; postprocessing,
visualization and data analysis; data management; and customizing the software.
There are many tools that address these problems individually, but the same
work found that the excess number and specialization of these tools also
contribute to the learning curve.

Efforts to address these five issues typically fall in with general purpose
scientific workflow tools like Kepler, \cite{kepler}, or are reduced to myopic
tools that satisfy some set of requirements for a single piece of software or
platform. That is, the proposed solution to this problem is often to shoe-horn
it into existing workflow tools that are so general that they focus on nothing
in particular or to ignore the general problem entirely and deploy a completely
tailored solution for the given application. These are opposing extremes, but a
middle-of-the-road solution is also possible. A workflow engine could be
developed that limits its scope to High-Performance Computing (HPC) and to the
set of possible workflows that come from the previously mentioned five
activities. A rich enough Application Programming Interface (API) could be
exposed so that highly customized solutions could still be made based on this
limited workflow engine with only a relatively minor amount of additional
development required.

It is not clear that one of these solutions is better than the others.
Practical requirements will ultimately dictate which way projects go. This work
considers the middle ground sollution and presents the Eclipse Integrated
Computational Environment (ICE) as proof that it is possible to create such a
system. Specifically, we show
\begin{itemize}
\item an architecture for such a workflow system that accomplishes all five of
the required activities outlined above in a simple, extensible way, \ref{}.
\item that such a system can be cross-platform for workstations and
simultaneously deployable on the web, \ref{}.
\item that smart design decisions enable not only authoring code for simulation
software, but also make it possible for the system to extend itself, thereby
enabling heavy customization, \ref{}.
\item that the system can be easily integrated with other tools, including the
general-purpose workflow engines and single-focus tools on opposite ends of this
tool space, \ref{}.
\end{itemize}

### 2016-07-26 src/main.tex
Renamed the ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

%%This is a very basic article template.
%%There is just one section and two subsections.
\documentclass[]{elsart}

\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}

\begin{document}

\begin{frontmatter}

\title{The Eclipse Integrated Computational Environment}

\author{Jay Jay Billings$^{1,2}$}
\ead{billingsjj@ornl.gov}
\author{Alexander J. McCaskey$^{1}$}
\author{ADD ALL OTHER AUTHORS}

%%%%% ----- FIXME! Add all ICE & NiCE contributors

\address{$^1$Computer Science and Mathematics Division, Oak Ridge National
Laboratory, Oak Ridge, TN 37830, USA}
\address{$^2$The Bredesen Center for Interdisciplinary Research and Graduate
Education, University of Tennessee, Knoxville, TN 37996-1200, USA}

%----------------\input{abstract}

\begin{keyword}
\sep 
\sep 
supercomputing

\vspace{1ex}

\PACS
07.05.Tp % Computer modeling and simulation

\end{keyword}

\end{frontmatter}

\input{intro}
%--------\input{background}
%--------\input{design}
%--------\input{comparisons}
%--------\input{future}
%--------\input{availability}
\input{conclusions}
\input{ack}

\bibliographystyle{unsrt}
\bibliography{bib}

\end{document}

### 2017-01-01 src/content.tex
Committing first draft of ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\section{Motivation and Significance}\label{motivation-and-significance}

High performance modeling and simulation software is hard to use. Much
of the challenge comes from the inherent nature of the science under
consideration, but perhaps just as much of the problem comes from
focusing very heavily on raw compute performance. Focusing on
performance is understandable, given the field, but it leaves the rest
of us to figure out how to actually use the software in a way that
scales for a much larger set of users, many of whom may be novices or
migrate between software packages regularly.

** REMOVE or merge with text below!**

In previous work, Billings et. al., discovered through requirements
gathering interviews that many of the difficulties using high
performance modeling and simulation software fall broadly into five
distinct categories, \cite{billings_cbhpc}. This includes input
generation and preprocessing (also called ``model setup''); job
execution and monitoring; postprocessing, visualization and data
analysis; data management; and customizing the software. There are many
tools that address these problems individually, but the same work found
that the excess number and specialization of these tools also contribute
to the learning curve.

Efforts to address these five issues typically fall in with general
purpose scientific workflow tools like Kepler, \cite{kepler}, or are
reduced to myopic tools that satisfy some set of requirements for a
single piece of software or platform. That is, the proposed solution to
this problem is often to shoe-horn it into existing workflow tools that
are so general that they focus on nothing in particular or to ignore the
general problem entirely and deploy a completely tailored solution for
the given application. These are opposing extremes, but a
middle-of-the-road solution is also possible. A workflow engine could be
developed that limits its scope to High-Performance Computing (HPC) and
to the set of possible workflows that come from the previously mentioned
five activities. A rich enough Application Programming Interface (API)
could be exposed so that highly customized solutions could still be made
based on this limited workflow engine with only a relatively minor
amount of additional development required.

It is not clear that one of these solutions is better than the others.
Practical requirements will ultimately dictate which way projects go.
This work considers a middle ground solution and presents the Eclipse
Integrated Computational Environment (ICE) as proof that it is possible
to create such a system. Specifically, we show * an architecture for
such a workflow system that satisfies the model of workflows presented
below in an extensible way. * that such a system can be cross-platform
for workstations and simultaneously deployable on the web. * that smart
design decisions enable not only authoring code for simulation software,
but also make it possible for the system to extend itself, thereby
enabling heavy customization.

\textbf{FIXME! Needs to transition smoothly!}

\subsubsection{Workflow Model}\label{workflow-model}

Computational scientists perform a variety of tasks with respect to
modeling and simulation that can be abstracted into a lightweight
theoretical framework broadly based on five high-level
\emph{activities}: creating input, executing jobs, analyzing results,
managing data, and modifying code. The same computational scientist
would most likely find these activities difficult for all codes with
which they lack experience, whereas with their own codes or those with
which they are most familiar these tasks may be so easy that they are
taken for granted. Any particular combination of these activities across
one or more scientific software packages or codes results in a unique
\emph{workflow}. Such a workflow is normally, but not always, requested
by a human user and orchestrated by a \emph{Workflow Management System
(WMS)}.

The most obvious workflow for any individual simulation code or
collection of codes is to string the activities together: the user's
workflow is to create the input, launch the job, perform some analysis
and manage their data, possibly modifying their code in the process.
There are many other combinations though, such as re-running jobs with
conditions or modifications or analyzing someone else's data. (See
footnote 1.)

\textbf{Creating input} is the process of describing the physical model
or state of a system that will be simulated. This could include creating
an input file or file(s), but could also include external calls to a
process to configure a running program. In most situations a
computational scientist will modify existing input or create new input
from a template. ``Input'' generally includes runtime parameters for the
simulation framework (tolerances, etc.); configuration options (data
locations, output locations, module configurations, etc.); material
properties for the materials that will be simulated; and a
discretization of the simulation space (mesh, grid, particle
distribution, etc.). The collection of all required input can be quite
large and may go by many names such as ``input set,'' ``input package,''
``problem,'' or, simply, ``input.'' Often the set of input files will be
described in a ``main'' input file that acts as a kind of manifest,
describing and providing links to all necessary information for the
given problem.

In this work, it should be assumed unless otherwise noted that ``input''
refers to the entire set of input, not a single file.

\textbf{Executing jobs} or ``running the workflow'' in this context is
the process of performing some calculation based on the input with a
simulation code or framework. Modeling and simulation codes are normally
run locally for small jobs or development. Large simulations typically
require equally large hardware resources that are utilized remotely
through Secure Shell (SSH) connections or similar protocols. Remote
execution requires moving the input in advance of the execution and
copying or moving the output to the user's machine, if possible and
desirable. (In many cases the output cannot be moved because it is too
large.)

Local and remote jobs are often monitored in one or more ways to
ascertain the status of job. This can include simply checking whether or
not execution has finished or monitoring the output of individual
quantities to examine the calculation state. The latter is often used to
detect calculation errors that will result in incorrect results. If such
results are found, the job is typically cancelled (``killed'') to save
compute resources and re-run later.

In this work, it should be assumed unless otherwise noted that
``executing a job'' includes monitoring that job in one or more ways,
possibly including real-time updates to visualizations.

\textbf{Analyzing results} includes executing special jobs to transform
data in one or more prescribed ways and producing artifacts with
scientific significance from the transformed data. This may include, for
example, post-processing results and visualizing the new data with
dedicated visualization tools. For many types of scientific computing
this includes viewing the results of a simulation on a mesh or grid and
extracting publication quality images or movies from that data. Other
cases may include analyzing results in preparation for follow
simulations or performing feature extraction, classification or
activities for machine learning and data mining.

While this has many similarities to executing a job, it is distinctly
different because the activity changes focus to satisfy the needs of a
human operator. Simple data reduction where the exact reduction is known
certainly qualifies as executing a job, but analysis of modeling and
simulation results is far from simple data reduction. It is generally a
far more interactive process for computational scientists.

\textbf{Managing data} includes moving, copying, storing, sharing or
otherwise interacting with data for or from simulations. This activity
is the most pervasive of all the activities because each of the others
requires interacting with data in some way. In many cases though, data
is still managed its own purposes, without performing a simulation,
generating new input, or analysing results. Examples include archiving
data, packaging data for publications, and updating values manually
(often in light of new information from publications).

\textbf{Modifying code} is not typically considered a part of a
scientific computing workflow. However, modeling and simulation use
cases often require users to explicitly modify code before execution,
such as with the computational fluid dynamics code Nek5000,
{[}Nek5000{]}; or to issue special re-build instructions. Many
computational scientists consider ``their workflow'' to be re-running
software after modifications for purely exploratory purposes. This may
be required if the model the author is manipulating can not be
configured as part of the input directly but can be easily manipulated
by hand.

\subsubsection{Comparison to Other
Models}\label{comparison-to-other-models}

This model of workflows differs significantly from those of similar
efforts in workflow science because it defines workflows in terms of
activities. Others in the literature define a workflow as a collection
of computing processes. For example, Yu and Buyya define grid workflows
as ``a collection of tasks that are processed on distributed resources
in a wel-defined order to accomplish a specific goal,'' {[}Yu, 2005{]}.
Others such as Pizzi et al. subscribe to similar definitions, {[}Pizzi,
2015{]}. This ``process'' view is acceptable where the workflow is
static and does not require additional human input or ``human in the
loop'' behavior after the all the initial human input is provided. That
is, a ``process-oriented'' definition is acceptable where all human
input is provided in advance. However, workflows within ICE are fully
interactive with regular call-backs to humans. It is simpler to discuss
``activities'' than it is to create a distinction between ``human
processes'' and ``computer processes.'' Focusing on ``activities'' over
processes (human or computer) also has the benefit of removing concrete
elements such as hardware properties or software details that distract
from details of workflows and WMSes per se. That is, considerations such
as memory usage and raw performance are important, but questions about
the abstract workflow or what the WMS should do are far more important.

\section{Software Description}\label{software-description}

ICE was specifically created to address the workflow model described
above, which is to say that it was created specifically to address
hands-on workflows for computational scientists. Users download and
execute ICE locally and it orchestrates workflows locally or remotely as
required. It provides a comprehensive workbench for modeling and
simulation that includes tools for workflows, visualization, data
management, and software development.

\subsection{Software Architecture}\label{software-architecture}

Workflows and tasks in ICE are not explicitly treated as trees -
Directed Acyclic Graphs, (DAGS) - as is common with grid workflow tools,
{[}Yu, 2005{]}. Instead, ICE's design is inspired by Representational
State Transfer (REST), {[}Fielding, 2000{]}.

Users initiate requests to create, edit, update or delete workflows from
the \emph{ICE Client} (the workbench). The list of available workflow
that can be created is provided dynamically to the \emph{ICE Client} by
the \emph{ICE Core}, which acts as a kind of server. This information is
provided dynamically since it often changes as run time based on the
configuration of available workflow components in the registry and on
persisted workflows that users have saved in their workspace.
Information about workflows are provided from the Core to the Client
through \emph{stateless Forms} that describe the workflow and provide
all the necessary information to understand \emph{what} should process
the workflow, (but not \emph{how} it should be processed). Once users
modify the description of the workflow in the Form to provide their
specific details, the Client dispatches a request to the Core to modify
or process the workflow. The Core then uses the information in the Form
to perform a service lookup for \emph{what} should process the workflow.

Workflows in ICE are encoded in and processed by \emph{Items} and each
workflow type is a subclass of Item. Items are registered dynamically
through a service registry in ICE, (see section \ref{framework}), and
provide the Forms for the ICE Core and Client. Since ICE's design is
highly object oriented, it is easiest to think of the Item class as a
description of an abstract workflow and an Item object (an instance of
the class) as a concrete workflow with all required execution details
provided by its Form.

Individual components of workflows, i.e. - workflow ``tasks'' or
``nodes'' - are either encoded directly in the workflow's subclass of
Item or provided as \emph{Actions} that are dynamically registered with
an \emph{Action Factory} and obtained at runtime. Table 1. describes the
differences between Items, Actions, and Forms. (See footnote 2.)

Table 1: Class Descriptions for Items, Forms and Actions

\begin{longtable}[c]{@{}lll@{}}
\toprule
Class & Class Description & Object Description\tabularnewline
\midrule
\endhead
Item & Java class with code to execute an abstract workflow. Provides a
Form. & Concrete workflow executor.\tabularnewline
Form & Description and template of the data needed for the Item to
process the workflow. & User-modified workflow data.\tabularnewline
Action & Java class for executing a specific task in the workflow. Used
by Items. & Concrete workflow task executor.\tabularnewline
\bottomrule
\end{longtable}

In addition to running as a desktop workbench, ICE can be run as a
headless web server with a remote service interface and a web
Application Programming Interface (API). The web API is also used as the
primary means of providing real-time feedback and monitoring support in
ICE.

\subsubsection{Item States}\label{item-states}

All Items in ICE are finite state machines where the states represent
the abstract state of the workflow. For example, when an Item is first
created, it enters the ``Form Ready'' state to indicate that it could,
in theory, be processed after a user reviews it. After that review it
enters the ``Ready to Process'' state before and the ``Processed'' state
after it is processed. There are several additional states for errors.

This design is very important. First, it means that all workflows in
ICE, regardless of their actual details and function, can only behave in
a specific set of known, predictable ways. This greatly simplifies the
way that the Core manages and interacts with Items. Second, it
explicitly delineates which workflows can be executed from those that
must still receive some configuration because it formalizes state and
error checks. Finally, it allows developers implementing Items and
Actions to specify by contract what is required before proceeding to the
next task, processing the workflow, or declaring a successful execution.

\subsubsection{Persistence and
Workspaces}\label{persistence-and-workspaces}

ICE persists permanent copies of Forms to disk when workflows are
created and modified in a special directory called a \emph{workspace}.
Workspaces can contain projects, folders and files, including data,
code, input and output. ICE automatically manages local and remote (or
even local \emph{to} remote) transfers of data files when executing
workflows if the files are detected in the same directory of the
workspace as the workflow itself. For example, when executing a remote
job, ICE will automatically move the input file if it is specified in
the workflow and available in the project directory of the workspace.
Likewise, if output is small enough, ICE will automatically move it back
to local directory. By conventional, all paths in ICE's Forms are
relative to the workspace root path. Workspace directories are specified
by the user.

ICE handles persistence using a \emph{persistence provider}. The only
default persistence provider uses JAX-RS, {[}Burke, 2009{]}, to write
Forms to XML. In principle other persistence providers could replace the
XML-based provider since it is registered as a dynamic service, and in
the past a JAX-P based provider has been used.

\subsubsection{Extending the Framework to Add Custom
Workflows}\label{extending-the-framework-to-add-custom-workflows}

ICE is an Eclipse Rich Client Platform (RCP) application, {[}McAffer 2,
2010{]}. It has a plugin architecture based on Equinox, the reference
implementation of the Open Service Gateway Initiative (OSGi) framework
specification, {[}McAffer, 2010{]}. It uses over 1200 additional
packages from the Eclipse ecosystem to provide services such as language
support and visualization to users. Each unique element of ICE described
in this work, including the client, core, all Items, data structures and
many others are provided as plugins to Equinox. Most plugins are
dynamically managed and provided as services that can be obtained from a
service registry. All file I/O in ICE, with only a few exceptions,
interacts with the RCP's Resources plugin. This includes remote
resources that are managed with the Eclipse Parallel Tools Platform,
{[}Tibbitts, 2009{]}.

It is not possible to graphically create new Items in ICE. Users can
only use the workflow Items provided with their version of ICE unless
they provide their own plugin to the framework. This can seem like an
onerous task to the novice user especially if they do not know Java, but
this design was chosen because it is, in the opinion of the authors, a
far more sophisticated and sustainable way to create workflows than
through wiring diagram.

ICE provides built-in development tools to auto-generate ``stubs'' of
plugins that can then be installed into the framework. This
``self-hosting'' makes it possible for new users to create complex,
sophisticated workflows very quickly because they are not required to
know how to interact with the framework. Furthermore, ICE provides a
rich API, documentation, tutorials, and tools to further simply the
process.

There are many situations where graphically configuring workflows is
unacceptable, such as when a very large number of workflows will be
executed or the type of information required is very fine-grained. In
these cases, it is often necessary to provide scripts to the workflow
management system. ICE includes the Eclipse Advanced Scripting
Environment, {[}Pontesegger, 2017{]}, (EASE), for scripting because it
provides a native way to script Eclipse RCP projects in Javascript,
Jython, and Python. This also makes it possible to extend the
environment by adding Items in these languages.

\subsection{Software Functionalities}\label{software-functionalities}

The most important function of ICE is to serve as an easily extended
workflow management system for computational scientists in support of
the activities described above. In practice, it is most often used as a
combination of workflow management system and development environment
since it contains a significant amount of Eclipse's software development
tooling in addition to the workflow tools. The project has many users,
but it is most heavily used by the development team to support workflow
science and software development for energy science projects. The
development team regularly uses the platform to quickly deploy new
domain-specific workbenches in a matter of hours for small collections
of workflows that are easy to encode.

Outside of the development team, ICE is commonly deployed as a
sophisticated user environment for computational science projects (see
``Impact'' below) and as a visualization tool. ICE originally a
significant amount of visualization support, but at the request of users
in the community that support was ``spun off'' in early 2016 as a
separate visualization project, the Eclipse Advanced Visualization
Project, EAVP, {[}EAVP, 2009{]}.

\section{Illustrative Examples}\label{illustrative-examples}

The role that ICE plays as a workflow tool is best illustrated by the
various ways that it has been deployed.

\subsection{Virtual Battery
Simulations}\label{virtual-battery-simulations}

Pannala et al. developed a Virtual Integrated Battery Environment (VIBE)
as part of their research into safety and performance characteristics of
lithium ion batteries, {[}Pannala, 2015{]}. VIBE provides ICE to users
as part of its distribution. New workflows were added to ICE to create
multiple types of input, configure the simulation software, and launch
simulations of virtual batteries. Interactive 3D visualizations of the
results were embedded in the launcher so that users would quickly find
their results. Figure 1 shows the results from a temperature
distribution of a prismatic cell battery simulated during discharge.

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{images/vibe_20151016.png}
\caption{vibe}
\end{figure}

VIBE 1.0 is available as a virtual machine in which the simulation
software and ICE are provided side by side. More recent efforts for VIBE
1.1 by the VIBE development team include providing the simulation
software in Docker containers so that users can download the latest,
native version of ICE for their machine while simultaneously benefiting
from a smaller virtual machine for the simulator.

\subsection{Multiphysics Simulations with
MOOSE}\label{multiphysics-simulations-with-moose}

The MOOSE Framework is a powerful, easy to use multiphysics framework
developed at the Idaho National Laboratory, {[}Gaston, 2009{]}. ICE
provides workflow tools for MOOSE as well as specialized class
generation utilities for developing custom MOOSE kernels. Many of the
MOOSE tools in ICE were developed closely with the MOOSE team to closely
reproduce various aspects of MOOSE's user interface, Peacock. Figure 2
shows an example of the ICE workbench for a simple structural mechanics
problem solved with the MOOSE framework, {[}McCaskey, 2016{]}.

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{images/ice-moose.png}
\caption{moose}
\end{figure}

There are over three hundred MOOSE-based applications and it is very
easy to create new MOOSE applications. The ICE development team uses ICE
and MOOSE to quickly solve energy science problems with high-performance
computing resources and deploy domain specific workbenches. ICE includes
support for automatically downloading and building MOOSE from its GitHub
project, which then makes it possible to immediately begin developing
complex multiphysics applications using the Eclipse C Development Tools,
which are pre-installed in ICE to facilitate this interaction. Once the
new MOOSE-based application is built, it will automatically work with
the MOOSE workflow tools in ICE, although developers can also create
customized workflow tools as needed.

\subsection{Binder Jet Modeling}\label{binder-jet-modeling}

Solid-state sintering of parts printed using binder jetting
significantly increases part strength by decreasing the part porosity
and eliminating voids. The downside of this process is that it causes
the part to shrink and warp. An ideal near-net-shape process that
combined binder jetting with solid-state sintering would thus consider
warpage and deformation due to sintering in the design phase of the
part. Figure 3 shows an ICE-based workbench for perform simulations of
this process with visualizations of the pre- and post-simulation
properties of a central body with eight cantilevers. The primary
deformation in this type of geometry is bending or drooping of the
cantilevers, and ICE currently calls a custom MOOSE-based application
(which was written in ICE as described above) for simulating the
deformation of the cantilevers.

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{images/ice-bjm.png}
\caption{bjm}
\end{figure}

The full application for this work is expected to be released near the
end of 2017.

\subsection{Neutron Reflectivity}\label{neutron-reflectivity}

ICE includes a small utility for simulating neutron reflectivity and
comparing the results to data, {[}Billings, 2015{]}. This was developed
in collaboration with colleagues at the Spallation Neutron Source to
replace an older utility written in Visual Basic and distributed via
Excel macros. The newer utility in ICE is capable of processing a single
workflow and is shown in figure 4.

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{images/reflectivity-screenshot.png}
\caption{reflectivity}
\end{figure}

\subsection{Quantum Computing}\label{quantum-computing}

As quantum computing grows, so to does the need for sophisticated
software that can utilize quantum hardware or perform calculations on
simulated quantum hardware. Humble et al. created a simulator for
adiabatic quantum computers where workflows were added to ICE to support
interaction with the simulator, but also to process large sets of
quadratic binary optimimzation problems, {[}Humble, 2014{]}. Figure 5
shows the workbench for this project.

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{images/jaded.png}
\caption{qc}
\end{figure}

ICE also supports other quantum computing projects, including the
eXtreme-scale ACCelerator (XACC) programming framework,
{[}ORNL-QCI/XACC, 2016{]}. XACC is a programming framework for
extreme-scale, post-exascale accelerator architectures that integrates
alongside existing conventional applications.

\subsection{Nuclear Energy}\label{nuclear-energy}

There are many examples of ICE's role in modeling and simulation
projects for nuclear energy, but readers are referred to the work in
{[}Billings, 2015{]} for an extreme example of the level of
customization that is possible in ICE. Support for the ``Reactor
Analyzer'' was dropped in ICE 2.1.8, but it demonstrated ICE's ability
to integrate many different nuclear energy tools for complex analysis.

\section{Impact}\label{impact}

The impact of software tools such as ICE are hard to quantify. However,
there are several places where ICE has significantly assisted its
development team and others.

One pressing area of interest and impact is that of interoperability
between workflow systems. There is significant prior art in combining
large workflow management systems, such as that Mandal et al.,
{[}Mandal, 2007{]}, but the end goal of gaining the greatest advantage
by using the best capabilities from multiple systems remains elusive.
ICE's unique perspective on workflows and its well-defined API make it
possible to integrate multiple systems in a straightforward way. This
allows it to connect to other workflow environments, such as Triquetrum,
quite easily, {[}Brooks 1, 2015{]}. Triquetrum, (like Kepler in
{[}Mandal, 2007{]}), is a Ptolemy-based workflow engine, {[}Brooks 2,
2015{]}. Several of the authors of this paper are using it to
investigate these issues.

It is widely known that tools that make researchers more productive tend
to improve the pursuit of existing research. The high extensibility of
ICE and the tools that it combines from the larger Eclipse ecosystem
have made it possible for researchers on the development team to quickly
deploy new simulation environments for problems, such as the binder jet
modeler and reflectivity tools mentioned earlier. Other tools create
with ICE may not radically invent something new, but they tend to
streamline interactions with those tools. Many ICE users (and certainly
the development team!) have experienced improvements in software
development activities because of the tools that ICE provides or learned
new technologies because access to new tooling was a simple as
installing more plugins through the Eclipse Marketplace.

The ICE development team does not track ICE's user base, as useful as
that would be, because of the extra work involved. However, various
sources such as the VIBE mailing list, ICE's own mailing lists, and
website download statistics suggest that ICE has been used by over 350
people at one time or another and currently has about twenty
``superusers,'' including the development team.

A new cloud based development tool based on ICE is under development by
RNET LLC out of Dayton, Ohio in response to an SBIR award from the U.S.
Department of Energy. This web based version of ICE will continue ICE's
support for nuclear energy and integrate with cloud services such as
Amazon Web Services and Oak Ridge National Laboratory's Compute and Data
Environment for Science (CADES). Additionally, while ICE has not led to
the development of ``spin-off'' companies, ICE source code has been used
in two spin-off projects: EAVP (mentioned earlier) for advanced
visualizations and the Eclipse January project for scientific data
structures, {[}Graham, 2016{]}. ICE was also one of the founding
projects of the Eclipse Science Working Group.

\section{Sample Code, Tutorials and Other
Resources}\label{sample-code-tutorials-and-other-resources}

The quintessential resource for information on ICE is the projects web
page, {[}ICE, 2016{]}. The ``Resources'' menu includes links to detailed
tutorials and documentation of multiple types. Examples of how to create
new workflow Items are available at
https://github.com/eclipse/ice/tree/master/org.eclipse.ice.demo.
Examples of how to use the scripting engine (in this case for neutron
reflectivity) are available at
https://github.com/eclipse/ice/tree/master/examples. ICE includes an
extensive test suite of unit, integration, and UI tests and these are
also excellent examples of how to work with the platform.

\section{Conclusions}\label{conclusions}

Workflows for computational scientists in modeling and simulation differ
greatly from experimentalists or those who primarily interact with
grid-based workflow management systems. This work presented the Eclipse
Integrated Computational Environment (ICE) and described how its has
been used to address interdisciplinary problems in modeling and
simulation for energy science. One interesting avenue for future
exploration is coupling or integrating ICE with other workflow tools
such as Aiida, Triquetrum, Kepler and Pegasus. It remains as abundantly
clear now as it was in Mandal's 2007 paper that the best of all workflow
management tools will be needed to address high-performance computing
problems at the exascale and beyond.

\section*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

The authors are grateful for the assistance and support of the following
people and institutions without which this work would not have been
possible. This includes many people who directly contributed to the
project, either in its early days as ``NiCE'' or once it moved to
Eclipse, including: Ronald Allen, Andrew Belt, Tim Bohn, David E.
Bernholdt, Erica Grant, Mike Guidry, Forest Hull, Eric J. Lingerfelt,
Sebastien Jourdain, JiSoo Kim, Allison Koenecke, Fangzhou Lin, Greg
Lyon, Tony McCrary, John M. Hetrick III, Elizabeth Piersall, Neeti
Pokhriyal, Adrian Sanchez, Claire Saunders, Nick Stanish, Matthew Wang,
Scott Wittenberg. The support of both the NEAMS and CASL programs is
greatly appreciated. The authors would like to acknowledge the special
contribution of the Eclipse Foundation, the Eclipse Community, the
Eclipse Science Working Group and our many colleagues who use and
contribute to open source projects in the Eclipse ecosystem.

Finally, the development team is especially grateful to Barney Maccabe,
David Pointer and John Turner of Oak Ridge National Laboratory for their
endless support and advocacy for this work.

This work has been supported by the US Department of Energy, Offices of
Nuclear Energy (DOE-NE) and Energy Efficiency and Renewable Energy
(DOE-EERE), and by the ORNL Undergraduate Research Participation
Program, which is sponsored by ORNL and administered jointly by ORNL and
the Oak Ridge Institute for Science and Education (ORISE). This work was
also supported in part by the Oak Ridge National Laboratory Director's
Research and Development Fund. ORNL is managed by UT-Battelle, LLC, for
the US Department of Energy under contract no. DE-AC05-00OR22725. ORISE
is managed by Oak Ridge Associated Universities for the US Department of
Energy under contract no. DE-AC05-00OR22750.

\section*{Required Metadata}\label{required-metadata}
\addcontentsline{toc}{section}{Required Metadata}

\section*{Current code version}\label{current-code-version}
\addcontentsline{toc}{section}{Current code version}

--------- \textbar{}
:-----------------------------------------------------------------:
\textbar{} :-------------------------------------------------------- :
\textbar{}\\C1 \textbar{} Current Code Version \textbar{} `next'
\textbar{}\\C2 \textbar{} Permanent link to code/repository used for
this code version \textbar{} https://github.com/eclipse/ice/tree/next
\textbar{}\\C3 \textbar{} Legal Code License \textbar{} Eclipse Public
License 1.0 \textbar{}\\C4 \textbar{} Code versioning system use
\textbar{} Git \textbar{}\\C5 \textbar{} Software code languages, tools,
and services used \textbar{} Java, OSGi, Eclipse Rich Client Platform,
and Maven \textbar{}\\C6 \textbar{} Compilation requirements, operating
environments \& dependencies \textbar{} Java 1.8 or greater, Maven, and
an internet connection for dependencies \textbar{}\\C7 \textbar{} If
available Link to developer documentation/manual \textbar{}
https://wiki.eclipse.org/ICE \textbar{}\\C8 \textbar{} Support email for
questions \textbar{} ice-dev@eclipse.org \textbar{}

\section*{Current executable software
version}\label{current-executable-software-version}
\addcontentsline{toc}{section}{Current executable software version}

--------- \textbar{}
:-----------------------------------------------------------------:
\textbar{} :-------------------------------------------------------- :
\textbar{}\\S1 \textbar{} Current Code Version \textbar{} 2.2.1
\textbar{}\\S2 \textbar{} Permanent link to executables of this version
\textbar{}
http://www.eclipse.org/downloads/download.php?file=/ice/builds/2.2.1/
\textbar{}\\S3 \textbar{} Legal Software License \textbar{} Eclipse
Public License 1.0 \textbar{}\\S4 \textbar{} Computing
platforms/Operating Systems \textbar{} Windows (32/64-bit), Mac OS/X,
Linux (32/64-bit) \textbar{}\\S5 \textbar{} Installation requirements \&
dependencies \textbar{} Java 1.8 or greater \textbar{}\\S6 \textbar{} If
available, link to user manual - if formally published include a
reference to the publication in the reference list \textbar{}
https://wiki.eclipse.org/ICE \textbar{}\\S7 \textbar{} Support email for
questions \textbar{} ice-users@eclipse.org \textbar{}

\section{References}\label{references}

Yu, Jia, and Rajkumar Buyya. ``A Taxonomy of Workflow Management Systems
for Grid Computing.'' Journal of Grid Computing 3.3--4 (2005): 171--200.
link.springer.com. Web.

Billings, Jay J. et al. ``Designing a Component-Based Architecture for
the Modeling and Simulation of Nuclear Fuels and Reactors.'' Proceedings
of the 2009 Workshop on Component-Based High Performance Computing. New
York, NY, USA: ACM, 2009. 6:1--6:4. ACM Digital Library. Web. 25 May
2016. CBHPC '09.

Pizzi, Giovanni et al. ``AiiDA: Automated Interactive Infrastructure and
Database for Computational Science.'' Computational Materials Science
111 (2016): 218--230. ScienceDirect. Web.

The Nek5000 Team. ``Nek5000 \textbar{} A Spectral Element Code for
CFD.'' Nek5000 Website. 22 Oct. 2014. Web. 29 Dec. 2016.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  McAffer, Jeff, Paul VanderLei, and Simon Archer. OSGi and Equinox.
  Boston: Addison-Wesley, 2010. Print.
\item
  McAffer, Jeff, Jean-Michel Lemieux, and Chris Aniszczyk. Eclipse Rich
  Client Platform Second Edition. Boston: Addison-Wesley, 2010. Print.
\end{enumerate}

Gaston, Derek et al. ``MOOSE: A Parallel Computational Framework for
Coupled Systems of Nonlinear Equations.'' Nuclear Engineering and Design
239.10 (2009): n. pag. Print.

Fielding, Roy Thomas. ``Architectural Styles and the Design of
Network-Based Software Architectures.'' University of California,
Irvine, 2000. Print.

Burke, Bill. RESTful Java with JAX-RS. California: O-Reilly, 2010.
Print.

Pontesegger, Christian. ``Eclipse Advanced Scripting Environment.''
N.p., n.d. Web. 1 Jan. 2017.

Billings, Jay Jay. ``Eclipse ICE.'' Project Website. Eclipse ICE. N.p.,
21 Oct. 2016. Web. 1 Jan. 2017.

Tibbitts, Beth R., Gregory R. Watson, and Craig E. Rasmussen. ``An
Integrated Approach to Improving the Parallel Application Development
Process.'' 2009 IEEE International Symposium on Parallel \& Distributed
Processing (IPDPS). Los Alamitos, CA, USA: IEEE Computer Society, 2009.
1--8. IEEE Computer Society. Web.

Billings, Jay Jay. ``Eclipse Advanced Visualization Project.'' Text.
projects.eclipse.org. N.p., 16 Dec. 2015. Web. 1 Jan. 2017.

Billings, Jay Jay et al. ``A Domain-Specific Analysis System for
Examining Nuclear Reactor Simulation Data for Light-Water and
Sodium-Cooled Fast Reactors.'' Annals of Nuclear Energy 85 (2015):
856--868. ScienceDirect. Web.

Billings, Jay Jay. ``The Brand New Neutron Reflectivity Simulator in
Eclipse ICE and What It Took to Make It.'' EclipseCon Europe 2015.
Ludwigsburg Germany: Eclipse Foundation, 2015. Web. 25 May 2016.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Brooks, Christopher. ``Triquetrum: Models of Computation for
  Workflows.'' EclipseCon NA 2016. N.p., 4 Dec. 2015. Web. 1 Jan. 2017.
\item
  Brooks, Christopher, and Jay Jay Billings. ``Introducing Triquetrum, A
  Possible Future for Kepler and Ptolemy II.'' Procedia Computer Science
  80 (2016): 2449--2454. ScienceDirect. Web. International Conference on
  Computational Science 2016, ICCS 2016, 6-8 June 2016, San Diego,
  California, USA.
\end{enumerate}

Humble, T. S. et al. ``An Integrated Programming and Development
Environment for Adiabatic Quantum Optimization.'' Computational Science
\& Discovery 7.1 (2014): 015006. Institute of Physics. Web.

McCaskey. ``Scientific Simulation with Eclipse - From Zero Code to
Running on Lots of Cores in 10 Minutes.'' EclipseCon NA 2016. Reston VA:
Eclipse Foundation, 2015. Web. 26 May 2016.

Pannala, S. et al. ``Multiscale Modeling and Characterization for
Performance and Safety of Lithium-Ion Batteries.'' Journal of Applied
Physics 118.7 (2015): 072017. scitation.aip.org. Web.

``ORNL-QCI/Xacc.'' GitHub. N.p., n.d. Web. 1 Jan. 2017.

Mandal, Nandita et al. ``Integrating Existing Scientific Workflow
Systems: The Kepler/Pegasus Example.'' Proceedings of the 2Nd Workshop
on Workflows in Support of Large-Scale Science. New York, NY, USA: ACM,
2007. 21--28. ACM Digital Library. Web. 20 Dec. 2016. WORKS '07.

Graham, Jonah. ``Eclipse January.'' Text. projects.eclipse.org. N.p., 6
Apr. 2016. Web. 1 Jan. 2017.

\section{Footnotes}\label{footnotes}

1: The authors have identified many different combinations of these
activities that define workflow ``classes.'' When possible, every effort
is made to give the classes funny names such as ``The Re-Run'' or ``The
Graduate Student.''

2: An upcoming update to the API will see the formal introduction of
IWorkflow, IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's
API language closer to other systems. This must be done with care to
satisfy backwards compatibility requirements on the present API.

### 2017-01-01 src/description.tex
Committing first draft of ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\section{Software description}
\label{}

Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.

\subsection{Software Architecture}
\label{}

Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.

\subsection{Software Functionalities}
\label{}

Present the major functionalities of the software.

\subsection{Sample code snippets analysis (optional)}
\label{}

\section{Illustrative Examples}
\label{}

Provide at least one illustrative example to demonstrate the major functions.

Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel. (Please upload any video as a single supplementary file with your article. Only one MP4 formatted, with 50MB maximum size, video is possible per article. Recommended video dimensions are 640 x 480 at a maximum of 30 frames/second. Prior to submission please test and validate your .mp4 file at $ http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification$. This tool will display your video exactly in the same way as it will appear on ScienceDirect.).

### 2017-01-01 src/impact.tex
Committing first draft of ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\section{Impact}
\label{}

\textbf{This is the main section of the article and the reviewers weight the description here appropriately}

Indicate in what way new research questions can be pursued as a result of the software (if any).

Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).

Indicate in what way the software has changed the daily practice of its users (if so).

Indicate how widespread the use of the software is within and outside the intended user group.

Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).

### 2017-01-01 src/main.tex
Committing first draft of ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 %%There is just one section and two subsections.
-\documentclass[]{elsart}
+\documentclass{elsart}
 
@@
 \usepackage{amsmath}
+\usepackage{tabularx}
+\usepackage{supertabular}
+\usepackage{longtable}
+\usepackage{booktabs}
 
@@
 \author{Jay Jay Billings$^{1,2}$}
-\ead{billingsjj@ornl.gov}
+\ead{billingsjj@ornl.gov, Twitter: @jayjaybillings}
+\author{Andrew R. Bennett$^{1,3}$}
+\author{Jordan Deyton$^{1,4}$}
+\author{Kasper Gammeltoft$^{1,5}$}
+\author{Jonah Graham$^{6}$}
+\author{Dasha Gorin$^{1,7}$}
+\author{Hari Krishnan$^{8}$}
+\author{Menghan Li$^{9}$}
 \author{Alexander J. McCaskey$^{1}$}
-\author{ADD ALL OTHER AUTHORS}
-
-%%%%% ----- FIXME! Add all ICE & NiCE contributors
+\author{Taylor Patterson$^{1,10}$}
+\author{Robert Smith$^{1}$}
+\author{Gregory R. Watson$^{1}$}
+\author{Anna Wojtowicz$^{1,11}$}
 
@@
 \address{$^2$The Bredesen Center for Interdisciplinary Research and Graduate
-Education, University of Tennessee, Knoxville, TN 37996-1200, USA}
+Education, University of Tennessee, 444 Greve Hall, 821 Volunteer
+  Blvd. Knoxville, TN 37996-3394}
+\address{$^3$University of Washington, Seattle, WA 98105}
+\address{$^4$General Electric Company, 3200 North Grandview Blvd Waukesha, WI
+53188-1678}
+\address{$^5$Georgia Institute of Technology North Avenue, Atlanta, GA 30332}
+\address{$^6$Kichwa Coders Ltd. 1 Plomer Green Avenue Downley, High Wycombe
+HP13 5LN United Kingdom}
+\address{$^7$Northwestern University 633 Clark Street Evanston, IL 60208}
+\address{$^8$Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley,
+CA 94720}
+\address{$^9$Department of Computer Science, and Department of Biological
+Sciences, Purdue University, West Lafayette, IN 47906} 
+\address{$^10$Acato Information Management, LLC 114 Union Valley Rd. Oak Ridge,
+TN 37830}
+\address{$^11$Colorado State University Fort Collins, CO 80523}
 
-%----------------\input{abstract}
+\begin{abstract}
+
+Problems in modeling and simulation require significantly different
+workflow management technologies than standard grid-based workflow
+management systems. Computational scientists typically interact with
+simulation software in a feedback driven way were solutions and
+workflows are developed iteratively and simultaneously. This work
+describes common activities in workflows and how combinations of these
+activities form unique workflows. It presents the Eclipse Integrated
+Computational Environment as a workflow management system and
+development environment for the modeling and simulation community.
+Examples of the Environment's applicability to problems in energy
+science, general multiphysics simulations, quantum computing and other
+areas are presented as well as its impact on the community.
+
+%---------------FIXME! Table reference!
+%\begin{table*}[t]
+%\begin{tabularx}{\textwidth}{|l|X|l|}
+%\hline
+%Class & Class Description & Object Description\tabularnewline\hline
+%Item & Java class with code to execute an abstract workflow. Provides a
+%Form. & Concrete workflow executor.\tabularnewline\hline
+%Form & Description and template of the data needed for the Item to
+%process the workflow. & User-modified workflow data.\tabularnewline\hline
+%Action & Java class for executing a specific task in the workflow. Used
+%by Items. & Concrete workflow task executor.\tabularnewline\hline
+%\end{tabularx}
+%\caption{Class Descriptions for Items, Forms and Actions}
+%\end{table*}
+
+\end{abstract}
 
@@
 
-\input{intro}
-%--------\input{background}
-%--------\input{design}
-%--------\input{comparisons}
-%--------\input{future}
-%--------\input{availability}
-\input{conclusions}
-\input{ack}
+\section{Notice of Copyright}\label{notice-of-copyright}
+
+This manuscript has been authored by UT-Battelle, LLC under Contract No.
+DEAC05-00OR22725 with the U.S. Department of Energy. The United States
+Government retains and the publisher, by accepting the article for
+publication, acknowledges that the United States Government retains a
+nonexclusive, paid-up, irrevocable, world-wide license to publish or
+reproduce the published form of this manuscript, or allow others to do
+so, for United States Government purposes. The Department of Energy will
+provide public access to these results of federally sponsored research
+in accordance with the DOE Public Access Plan
+(http://energy.gov/downloads/doe-public-access-plan ).
+
+\input{content}
 

### 2017-01-01 src/metadata.tex
Committing first draft of ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\section*{Required Metadata}
\label{}

\section*{Current code version}
\label{}

Ancillary data table required for subversion of the codebase. Kindly replace examples in right column with the correct information about your current code, and leave the left column as it is.

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & For example v42 \\
\hline
C2 & Permanent link to code/repository used for this code version & For example: $https://github.com/mozart/mozart2$ \\
\hline
C3 & Legal Code License   & List one of the approved licenses \\
\hline
C4 & Code versioning system used & For example svn, git, mercurial, etc. put none if none \\
\hline
C5 & Software code languages, tools, and services used & For example C++, python, r, MPI, OpenCL, etc. \\
\hline
C6 & Compilation requirements, operating environments \& dependencies & \\
\hline
C7 & If available Link to developer documentation/manual & For example: $http://mozart.github.io/documentation/$ \\
\hline
C8 & Support email for questions & \\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

\section*{Current executable software version}
\label{}

Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Please fill in this column} \\
\hline
S1 & Current software version & For example 1.1, 2.4 etc. \\
\hline
S2 & Permanent link to executables of this version  & For example: $https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
\hline
S3 & Legal Software License & List one of the approved licenses \\
\hline
S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS, Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based etc. \\
\hline
S5 & Installation requirements \& dependencies & \\
\hline
S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & For example: $http://mozart.github.io/documentation/$ \\
\hline
S7 & Support email for questions & \\
\hline
\end{tabular}
\caption{Software metadata (optional)}
\label{} 
\end{table}

### 2017-01-01 src/motivation.tex
Committing first draft of ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\section{Motivation and significance}
\label{}

Introduce the scientific background and the motivation for developing the software.

Explain why the software is important, and describe the exact (scientific) problem(s) it solves.

Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.

Provide a description of the experimental setting (how does the user use the software?).

Introduce related work in literature (cite or list algorithms used, other software etc.).

### 2017-01-09 src/content.tex
First full draft of the article.
Merged manually from github.com/jayjaybillings/thesis. Includes edits
from Sam Crawford and the most recent copy of the article and
bibliography.

Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 
-High performance modeling and simulation software is hard to use. Much
-of the challenge comes from the inherent nature of the science under
-consideration, but perhaps just as much of the problem comes from
-focusing very heavily on raw compute performance. Focusing on
-performance is understandable, given the field, but it leaves the rest
-of us to figure out how to actually use the software in a way that
-scales for a much larger set of users, many of whom may be novices or
-migrate between software packages regularly.
+In previous work, Billings et. al., discovered through requirements
+gathering interviews that many of the difficulties using
+high-performance modeling and simulation software fall broadly into five
+distinct categories, \cite{billings_designing_2009}. These activities,
+detailed in section \ref{workflow-model}, include (1) creating input,
+(2) executing jobs, (3) analyzing results, (4) managing data, and (5)
+modifying code. There are many tools that address these problems
+individually, but the same research found that the excess number and
+specialization of these tools also contribute to the learning curve.
 
-** REMOVE or merge with text below!**
+Efforts to address these five issues have previously resulted in general
+purpose scientific workflow tools like Kepler, 
+\cite{ludascher_scientific_2006}, or myopic tools that only satisfy a single
+set of requirements for a single piece of software or platform. These
+are opposing extremes, but a middle-of-the-road solution is also
+possible. A workflow engine could be developed that limits its scope to
+high-performance computing (HPC) and to the set of possible workflows
+associated with the five previously mentioned activities. With only
+minor additional development, a rich application programming interface
+(API) could be exposed so that highly-customized solutions could still
+be made based on this limited workflow engine.
 
-In previous work, Billings et. al., discovered through requirements
-gathering interviews that many of the difficulties using high
-performance modeling and simulation software fall broadly into five
-distinct categories, \cite{billings_cbhpc}. This includes input
-generation and preprocessing (also called ``model setup''); job
-execution and monitoring; postprocessing, visualization and data
-analysis; data management; and customizing the software. There are many
-tools that address these problems individually, but the same work found
-that the excess number and specialization of these tools also contribute
-to the learning curve.
+It is not clear which, if any, of these solutions is better than the
+others, and practical requirements will ultimately dictate the path of a
+project's progress. This work considers a middle ground solution and
+presents the Eclipse Integrated Computational Environment (ICE) as proof
+that it is possible to create such a system. Specifically, the work
+described here shows that:
 
-Efforts to address these five issues typically fall in with general
-purpose scientific workflow tools like Kepler, \cite{kepler}, or are
-reduced to myopic tools that satisfy some set of requirements for a
-single piece of software or platform. That is, the proposed solution to
-this problem is often to shoe-horn it into existing workflow tools that
-are so general that they focus on nothing in particular or to ignore the
-general problem entirely and deploy a completely tailored solution for
-the given application. These are opposing extremes, but a
-middle-of-the-road solution is also possible. A workflow engine could be
-developed that limits its scope to High-Performance Computing (HPC) and
-to the set of possible workflows that come from the previously mentioned
-five activities. A rich enough Application Programming Interface (API)
-could be exposed so that highly customized solutions could still be made
-based on this limited workflow engine with only a relatively minor
-amount of additional development required.
+\begin{itemize}
+\item
+  Modeling and simulation activities can be described in a succinct
+  workflow model, (see ``Workflow Model'').
+\item
+  An architecture for such a workflow system can satisfy the model of
+  workflows in an extensible way, (see ``Software Architecture'').
+\item
+  Such a system is applicable to a suite of problems in energy science,
+  including virtual battery simulations, additive manufacturing and
+  other areas, (see ``Illlustrative Examples'').
+\end{itemize}
 
-It is not clear that one of these solutions is better than the others.
-Practical requirements will ultimately dictate which way projects go.
-This work considers a middle ground solution and presents the Eclipse
-Integrated Computational Environment (ICE) as proof that it is possible
-to create such a system. Specifically, we show * an architecture for
-such a workflow system that satisfies the model of workflows presented
-below in an extensible way. * that such a system can be cross-platform
-for workstations and simultaneously deployable on the web. * that smart
-design decisions enable not only authoring code for simulation software,
-but also make it possible for the system to extend itself, thereby
-enabling heavy customization.
-
-\textbf{FIXME! Needs to transition smoothly!}
+This section concludes with an introduction of the workflow model addressed by
+ICE. Section \ref{software-description} presents the details of the software
+from an architecture perspective while section \ref{illustrative-examples}
+provides a set of comprehensive examples. Finally, this paper concludes with a
+presentation of the impact, (section \ref{impact}), and sample code,
+(section \ref{sample-code-tutorials-and-other-resources}).
 
@@
 
-Computational scientists perform a variety of tasks with respect to
-modeling and simulation that can be abstracted into a lightweight
-theoretical framework broadly based on five high-level
-\emph{activities}: creating input, executing jobs, analyzing results,
-managing data, and modifying code. The same computational scientist
-would most likely find these activities difficult for all codes with
-which they lack experience, whereas with their own codes or those with
-which they are most familiar these tasks may be so easy that they are
+Computational scientists perform a variety of tasks in modeling and
+simulation that can be abstracted into a lightweight theoretical
+framework based broadly on five high-level \emph{activities}: (1)
+creating input, (2) executing jobs, (3) analyzing results, (4) managing
+data, and (5) modifying code. Those same computational scientist would
+most likely find these activities difficult for all codes with which
+they lack experience, whereas with their own codes---or those with which
+they are most familiar---these tasks may be so simple that they are
 taken for granted. Any particular combination of these activities across
-one or more scientific software packages or codes results in a unique
+one or more scientific software package or code results in a unique
 \emph{workflow}. Such a workflow is normally, but not always, requested
@@
 collection of codes is to string the activities together: the user's
-workflow is to create the input, launch the job, perform some analysis
-and manage their data, possibly modifying their code in the process.
-There are many other combinations though, such as re-running jobs with
-conditions or modifications or analyzing someone else's data. (See
-footnote 1.)
+workflow is to create the input, launch the job, perform some analysis,
+and manage the data---possibly modifying the code in the process. There
+are many other combinations however, including re-running jobs with
+conditions or modifications or analyzing someone else's data (See
+footnote 1).\footnote{The
+authors have identified many different combinations of these activities that
+define workflow ``classes.'' When possible, every effort is made to give the
+classes funny names such as ``The Re-Run'' or ``The Graduate Student.''}
 
@@
 or state of a system that will be simulated. This could include creating
-an input file or file(s), but could also include external calls to a
-process to configure a running program. In most situations a
-computational scientist will modify existing input or create new input
-from a template. ``Input'' generally includes runtime parameters for the
-simulation framework (tolerances, etc.); configuration options (data
-locations, output locations, module configurations, etc.); material
-properties for the materials that will be simulated; and a
-discretization of the simulation space (mesh, grid, particle
-distribution, etc.). The collection of all required input can be quite
-large and may go by many names such as ``input set,'' ``input package,''
-``problem,'' or, simply, ``input.'' Often the set of input files will be
-described in a ``main'' input file that acts as a kind of manifest,
-describing and providing links to all necessary information for the
-given problem.
+an input file(s) or making calls to an external process to configure a
+running program. In most situations, a computational scientist will
+modify existing input or create new input from a template. ``Input''
+generally includes runtime parameters for the simulation framework
+(e.g., tolerances); configuration options (e.g., data locations, output
+locations, module configurations); properties of the materials to be
+simulated; and a discretization of the simulation space (e.g., mesh,
+grid, particle distribution). The collection of all required input can
+be quite large and may go by many names, including ``input set,''
+``input package,'' ``problem,'' or, simply, ``input.'' Often, the set of
+input files will be described in a ``main'' input file that acts as a
+kind of manifest, describing and providing links to all necessary
+information for a given problem.
 
-In this work, it should be assumed unless otherwise noted that ``input''
-refers to the entire set of input, not a single file.
+In this work, it should be assumed---unless otherwise noted---that
+``input'' refers to the entire set of input, not to a single file.
 
-\textbf{Executing jobs} or ``running the workflow'' in this context is
-the process of performing some calculation based on the input with a
-simulation code or framework. Modeling and simulation codes are normally
-run locally for small jobs or development. Large simulations typically
-require equally large hardware resources that are utilized remotely
+\textbf{Executing jobs}, or ``running the workflow'' in this context, is
+the process of performing calculations using a simulation code or
+framework based on known variables---the input. Models and simulation
+codes are typically run locally for small jobs or for development. Large
+simulations, on the other hand, typically require a large amount of
+hardware resources; these resources are usually off site (i.e.,
+physically unavailable to the user) and are accessed remotely remotely
 through Secure Shell (SSH) connections or similar protocols. Remote
 execution requires moving the input in advance of the execution and
-copying or moving the output to the user's machine, if possible and
-desirable. (In many cases the output cannot be moved because it is too
-large.)
+copying or moving the output to the user's machine. In many cases,
+though, the output is too large to move to the user's local machine.
 
-Local and remote jobs are often monitored in one or more ways to
-ascertain the status of job. This can include simply checking whether or
-not execution has finished or monitoring the output of individual
+Local and remote jobs are often monitored to ascertain a job's status.
+This monitoring may be a simple check as to whether or not the execution
+has completed, or it may involve monitoring the output of individual
 quantities to examine the calculation state. The latter is often used to
 detect calculation errors that will result in incorrect results. If such
-results are found, the job is typically cancelled (``killed'') to save
-compute resources and re-run later.
+problems are found, the job is typically cancelled (``killed'') to save
+compute resources and is then re-run later.
 
-In this work, it should be assumed unless otherwise noted that
+In this work, it should be assumed---unless otherwise noted---that
 ``executing a job'' includes monitoring that job in one or more ways,
@@
 example, post-processing results and visualizing the new data with
-dedicated visualization tools. For many types of scientific computing
+dedicated visualization tools. For many types of scientific computing,
 this includes viewing the results of a simulation on a mesh or grid and
@@
 cases may include analyzing results in preparation for follow
-simulations or performing feature extraction, classification or
+simulations or performing feature extraction, classification, or
 activities for machine learning and data mining.
@@
 different because the activity changes focus to satisfy the needs of a
-human operator. Simple data reduction where the exact reduction is known
-certainly qualifies as executing a job, but analysis of modeling and
-simulation results is far from simple data reduction. It is generally a
-far more interactive process for computational scientists.
+human operator. Simple data reduction, where the exact reduction is
+known, certainly qualifies as executing a job; however, analysis of
+model and simulation results is far from simple data reduction, and is
+generally far more interactive for computational scientists.
 
-\textbf{Managing data} includes moving, copying, storing, sharing or
+\textbf{Managing data} includes moving, copying, storing, sharing, or
 otherwise interacting with data for or from simulations. This activity
-is the most pervasive of all the activities because each of the others
-requires interacting with data in some way. In many cases though, data
-is still managed its own purposes, without performing a simulation,
-generating new input, or analysing results. Examples include archiving
+is the most pervasive because each of the other activities requires
+interacting with data in some way. In many cases, though, data is still
+managed for its own purposes, without performing a simulation,
+generating new input, or analyzing results. Examples include archiving
 data, packaging data for publications, and updating values manually
@@
 such as with the computational fluid dynamics code Nek5000,
-{[}Nek5000{]}; or to issue special re-build instructions. Many
-computational scientists consider ``their workflow'' to be re-running
+\cite{the_nek5000_team_nek5000_2014}, or to issue special re-build instructions.
+Many computational scientists consider ``their workflow'' to be re-running
 software after modifications for purely exploratory purposes. This may
-be required if the model the author is manipulating can not be
-configured as part of the input directly but can be easily manipulated
+be required if the model that the author is manipulating cannot be
+configured directly as part of the input but can be easily manipulated
 by hand.
@@
 efforts in workflow science because it defines workflows in terms of
-activities. Others in the literature define a workflow as a collection
-of computing processes. For example, Yu and Buyya define grid workflows
-as ``a collection of tasks that are processed on distributed resources
-in a wel-defined order to accomplish a specific goal,'' {[}Yu, 2005{]}.
-Others such as Pizzi et al. subscribe to similar definitions, {[}Pizzi,
-2015{]}. This ``process'' view is acceptable where the workflow is
-static and does not require additional human input or ``human in the
-loop'' behavior after the all the initial human input is provided. That
-is, a ``process-oriented'' definition is acceptable where all human
-input is provided in advance. However, workflows within ICE are fully
-interactive with regular call-backs to humans. It is simpler to discuss
-``activities'' than it is to create a distinction between ``human
-processes'' and ``computer processes.'' Focusing on ``activities'' over
-processes (human or computer) also has the benefit of removing concrete
-elements such as hardware properties or software details that distract
-from details of workflows and WMSes per se. That is, considerations such
-as memory usage and raw performance are important, but questions about
-the abstract workflow or what the WMS should do are far more important.
+activities. Other workflow models in the literature define a workflow as
+a collection of computing processes. For example, Yu and Buyya define
+grid workflows as ``a collection of tasks that are processed on
+distributed resources in a well-defined order to accomplish a specific
+goal,'' \cite{yu_taxonomy_2005}. Others, such as Pizzi et al., subscribe to
+similar definitions, \cite{pizzi_aiida:_2016}. This ``process'' view is
+acceptable where the workflow is static and does not require additional
+human input or ``human in the loop'' behavior after the all the initial
+human input is provided. That is, a ``process-oriented'' definition is
+acceptable where all human input is provided in advance. However,
+workflows within ICE are fully interactive with regular call-backs to
+humans. It is simpler to discuss ``activities'' than it is to create a
+distinction between ``human processes'' and ``computer processes.''
+Focusing on ``activities'' over processes (human or computer) also has
+the benefit of removing concrete elements such as hardware properties or
+software details that distract from details of workflows and WMSes. That
+is, considerations such as memory usage and raw performance are
+important, but questions about the abstract workflow or what the WMS
+should do are far more important.
 
@@
 Directed Acyclic Graphs, (DAGS) - as is common with grid workflow tools,
-{[}Yu, 2005{]}. Instead, ICE's design is inspired by Representational
-State Transfer (REST), {[}Fielding, 2000{]}.
+\cite{yu_taxonomy_2005}. Instead, ICE's design is inspired by Representational
+State Transfer (REST), \cite{fielding_architectural_2000}.
 
@@
 an \emph{Action Factory} and obtained at runtime. Table 1. describes the
-differences between Items, Actions, and Forms. (See footnote 2.)
+differences between Items, Actions, and Forms.\footnote{An upcoming update to the API will see the formal introduction of
+IWorkflow, IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's
+API language closer to other systems. This must be done with care to
+satisfy backwards compatibility requirements on the present API.}
 
@@
 
-\begin{longtable}[c]{@{}lll@{}}
-\toprule
-Class & Class Description & Object Description\tabularnewline
-\midrule
-\endhead
+\begin{table*}[t]
+\begin{tabularx}{\textwidth}{|l|X|l|}
+\hline
+Class & Class Description & Object Description\tabularnewline\hline
 Item & Java class with code to execute an abstract workflow. Provides a
-Form. & Concrete workflow executor.\tabularnewline
+Form. & Concrete workflow executor.\tabularnewline\hline
 Form & Description and template of the data needed for the Item to
-process the workflow. & User-modified workflow data.\tabularnewline
+process the workflow. & User-modified workflow data.\tabularnewline\hline
 Action & Java class for executing a specific task in the workflow. Used
-by Items. & Concrete workflow task executor.\tabularnewline
-\bottomrule
-\end{longtable}
+by Items. & Concrete workflow task executor.\tabularnewline\hline
+\end{tabularx}
+\caption{Class Descriptions for Items, Forms and Actions}
+\end{table*}
 
@@
 ICE handles persistence using a \emph{persistence provider}. The only
-default persistence provider uses JAX-RS, {[}Burke, 2009{]}, to write
+default persistence provider uses JAX-RS, \cite{burke_restful_2010}, to write
 Forms to XML. In principle other persistence providers could replace the
@@
 
-ICE is an Eclipse Rich Client Platform (RCP) application, {[}McAffer 2,
-2010{]}. It has a plugin architecture based on Equinox, the reference
-implementation of the Open Service Gateway Initiative (OSGi) framework
-specification, {[}McAffer, 2010{]}. It uses over 1200 additional
+ICE is an Eclipse Rich Client Platform (RCP) application,
+\cite{mcaffer_eclipse_2010}. It has a plugin architecture based on Equinox, the
+reference implementation of the Open Service Gateway Initiative (OSGi) framework specification, \cite{mcaffer_osgi_2010}. It uses over 1200 additional
 packages from the Eclipse ecosystem to provide services such as language
@@
 resources that are managed with the Eclipse Parallel Tools Platform,
-{[}Tibbitts, 2009{]}.
+\cite{tibbitts_integrated_2009}.
 
@@
 management system. ICE includes the Eclipse Advanced Scripting
-Environment, {[}Pontesegger, 2017{]}, (EASE), for scripting because it
+Environment, \cite{pontesegger_eclipse_2015}, (EASE), for scripting because it
 provides a native way to script Eclipse RCP projects in Javascript,
@@
 separate visualization project, the Eclipse Advanced Visualization
-Project, EAVP, {[}EAVP, 2009{]}.
+Project, EAVP, \cite{billings_eclipse_2015}.
 
@@
 as part of their research into safety and performance characteristics of
-lithium ion batteries, {[}Pannala, 2015{]}. VIBE provides ICE to users
-as part of its distribution. New workflows were added to ICE to create
+lithium ion batteries, \cite{pannala_multiscale_2015}. VIBE provides ICE to
+users as part of its distribution. New workflows were added to ICE to create
 multiple types of input, configure the simulation software, and launch
@@
 \includegraphics[width=\textwidth]{images/vibe_20151016.png}
-\caption{vibe}
+\caption{ICE workbench for VIBE analysis.}
 \end{figure}
@@
 The MOOSE Framework is a powerful, easy to use multiphysics framework
-developed at the Idaho National Laboratory, {[}Gaston, 2009{]}. ICE
+developed at the Idaho National Laboratory, \cite{gaston_moose:_2009}. ICE
 provides workflow tools for MOOSE as well as specialized class
@@
 shows an example of the ICE workbench for a simple structural mechanics
-problem solved with the MOOSE framework, {[}McCaskey, 2016{]}.
+problem solved with the MOOSE framework, \cite{mccaskey_scientific_2015}.
 
@@
 \includegraphics[width=\textwidth]{images/ice-moose.png}
-\caption{moose}
+\caption{ICE workbench for MOOSE workflows.}
 \end{figure}
@@
 \includegraphics[width=\textwidth]{images/ice-bjm.png}
-\caption{bjm}
+\caption{ICE workbench for binder jet modeling.}
 \end{figure}
@@
 ICE includes a small utility for simulating neutron reflectivity and
-comparing the results to data, {[}Billings, 2015{]}. This was developed
+comparing the results to data, \cite{billings_brand_2015}. This was developed
 in collaboration with colleagues at the Spallation Neutron Source to
@@
 \includegraphics[width=\textwidth]{images/reflectivity-screenshot.png}
-\caption{reflectivity}
+\caption{ICE workbench for neutron reflectivity.}
 \end{figure}
@@
 interaction with the simulator, but also to process large sets of
-quadratic binary optimimzation problems, {[}Humble, 2014{]}. Figure 5
+quadratic binary optimimzation problems, \cite{humble_integrated_2014}. Figure 5
 shows the workbench for this project.
@@
 \includegraphics[width=\textwidth]{images/jaded.png}
-\caption{qc}
+\caption{ICE workbench in JADE for quantum computing simulations.}
 \end{figure}
@@
 eXtreme-scale ACCelerator (XACC) programming framework,
-{[}ORNL-QCI/XACC, 2016{]}. XACC is a programming framework for
+\cite{mccaskey_ornl-qci/xacc_2016}. XACC is a programming framework for
 extreme-scale, post-exascale accelerator architectures that integrates
@@
 projects for nuclear energy, but readers are referred to the work in
-{[}Billings, 2015{]} for an extreme example of the level of
+\cite{billings_domain-specific_2015} for an extreme example of the level of
 customization that is possible in ICE. Support for the ``Reactor
@@
 large workflow management systems, such as that Mandal et al.,
-{[}Mandal, 2007{]}, but the end goal of gaining the greatest advantage
-by using the best capabilities from multiple systems remains elusive.
+\cite{mandal_integrating_2007}, but the end goal of gaining the greatest
+advantage by using the best capabilities from multiple systems remains elusive.
 ICE's unique perspective on workflows and its well-defined API make it
@@
 allows it to connect to other workflow environments, such as Triquetrum,
-quite easily, {[}Brooks 1, 2015{]}. Triquetrum, (like Kepler in
-{[}Mandal, 2007{]}), is a Ptolemy-based workflow engine, {[}Brooks 2,
-2015{]}. Several of the authors of this paper are using it to
-investigate these issues.
+quite easily, \cite{brooks_introducing_2016}. Triquetrum, (like Kepler in
+\cite{mandal_integrating_2007}), is a Ptolemy-based workflow engine,
+\cite{brooks_triquetrum:_2015}. Several of the authors of this paper are using
+it to investigate these issues.
 
@@
 visualizations and the Eclipse January project for scientific data
-structures, {[}Graham, 2016{]}. ICE was also one of the founding
+structures, \cite{graham_eclipse_2016}. ICE was also one of the founding
 projects of the Eclipse Science Working Group.
+
+Eclipse ICE is an open source project and the authors welcome and encourage
+engagement and contributions from readers. Interested parties my inquire by
+contacting the corresponding author or visiting the website.
 
@@
 The quintessential resource for information on ICE is the projects web
-page, {[}ICE, 2016{]}. The ``Resources'' menu includes links to detailed
-tutorials and documentation of multiple types. Examples of how to create
+page, \cite{billings_eclipse_2016}. The ``Resources'' menu includes links to
+detailed tutorials and documentation of multiple types. Examples of how to create
 new workflow Items are available at
-https://github.com/eclipse/ice/tree/master/org.eclipse.ice.demo.
+\url{https://github.com/eclipse/ice/tree/master/org.eclipse.ice.demo}.
 Examples of how to use the scripting engine (in this case for neutron
 reflectivity) are available at
-https://github.com/eclipse/ice/tree/master/examples. ICE includes an
+\url{https://github.com/eclipse/ice/tree/master/examples}. ICE includes an
 extensive test suite of unit, integration, and UI tests and these are
@@
 
---------- \textbar{}
-:-----------------------------------------------------------------:
-\textbar{} :-------------------------------------------------------- :
-\textbar{}\\C1 \textbar{} Current Code Version \textbar{} `next'
-\textbar{}\\C2 \textbar{} Permanent link to code/repository used for
-this code version \textbar{} https://github.com/eclipse/ice/tree/next
-\textbar{}\\C3 \textbar{} Legal Code License \textbar{} Eclipse Public
-License 1.0 \textbar{}\\C4 \textbar{} Code versioning system use
-\textbar{} Git \textbar{}\\C5 \textbar{} Software code languages, tools,
-and services used \textbar{} Java, OSGi, Eclipse Rich Client Platform,
-and Maven \textbar{}\\C6 \textbar{} Compilation requirements, operating
-environments \& dependencies \textbar{} Java 1.8 or greater, Maven, and
-an internet connection for dependencies \textbar{}\\C7 \textbar{} If
-available Link to developer documentation/manual \textbar{}
-https://wiki.eclipse.org/ICE \textbar{}\\C8 \textbar{} Support email for
-questions \textbar{} ice-dev@eclipse.org \textbar{}
+See Table \ref{codeTable}.
+
+\begin{table*}[!htbp]
+\begin{tabularx}{\textwidth}{|l|X|X|}
+\hline
+C1 & Current Code Version & `next'\tabularnewline\hline
+C2 & Permanent link to code/repository used for this code version &
+\url{https://github.com/eclipse/ice/tree/next}
+\tabularnewline\hline
+C3 & Legal Code License & Eclipse Public License 1.0 \tabularnewline\hline
+C4 & Code versioning system use & Git \tabularnewline\hline
+C5 & Software code languages, tools, and services used & Java, OSGi, Eclipse Rich Client Platform,
+and Maven \tabularnewline\hline
+C6 & Compilation requirements, operating environments \& dependencies & Java 1.8 or greater, Maven, and
+an internet connection for dependencies \tabularnewline\hline 
+C7 & If available Link to developer documentation/manual &
+\url{https://wiki.eclipse.org/ICE} \tabularnewline\hline 
+C8 & Support email for questions & ice-dev@eclipse.org \tabularnewline\hline
+\end{tabularx}
+\caption{Current Code Version}
+\label{codeTable}
+\end{table*}
 
@@
 
---------- \textbar{}
-:-----------------------------------------------------------------:
-\textbar{} :-------------------------------------------------------- :
-\textbar{}\\S1 \textbar{} Current Code Version \textbar{} 2.2.1
-\textbar{}\\S2 \textbar{} Permanent link to executables of this version
-\textbar{}
-http://www.eclipse.org/downloads/download.php?file=/ice/builds/2.2.1/
-\textbar{}\\S3 \textbar{} Legal Software License \textbar{} Eclipse
-Public License 1.0 \textbar{}\\S4 \textbar{} Computing
-platforms/Operating Systems \textbar{} Windows (32/64-bit), Mac OS/X,
-Linux (32/64-bit) \textbar{}\\S5 \textbar{} Installation requirements \&
-dependencies \textbar{} Java 1.8 or greater \textbar{}\\S6 \textbar{} If
-available, link to user manual - if formally published include a
-reference to the publication in the reference list \textbar{}
-https://wiki.eclipse.org/ICE \textbar{}\\S7 \textbar{} Support email for
-questions \textbar{} ice-users@eclipse.org \textbar{}
+See Table \ref{execTable}.
 
-\section{References}\label{references}
-
-Yu, Jia, and Rajkumar Buyya. ``A Taxonomy of Workflow Management Systems
-for Grid Computing.'' Journal of Grid Computing 3.3--4 (2005): 171--200.
-link.springer.com. Web.
-
-Billings, Jay J. et al. ``Designing a Component-Based Architecture for
-the Modeling and Simulation of Nuclear Fuels and Reactors.'' Proceedings
-of the 2009 Workshop on Component-Based High Performance Computing. New
-York, NY, USA: ACM, 2009. 6:1--6:4. ACM Digital Library. Web. 25 May
-2016. CBHPC '09.
-
-Pizzi, Giovanni et al. ``AiiDA: Automated Interactive Infrastructure and
-Database for Computational Science.'' Computational Materials Science
-111 (2016): 218--230. ScienceDirect. Web.
-
-The Nek5000 Team. ``Nek5000 \textbar{} A Spectral Element Code for
-CFD.'' Nek5000 Website. 22 Oct. 2014. Web. 29 Dec. 2016.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  McAffer, Jeff, Paul VanderLei, and Simon Archer. OSGi and Equinox.
-  Boston: Addison-Wesley, 2010. Print.
-\item
-  McAffer, Jeff, Jean-Michel Lemieux, and Chris Aniszczyk. Eclipse Rich
-  Client Platform Second Edition. Boston: Addison-Wesley, 2010. Print.
-\end{enumerate}
-
-Gaston, Derek et al. ``MOOSE: A Parallel Computational Framework for
-Coupled Systems of Nonlinear Equations.'' Nuclear Engineering and Design
-239.10 (2009): n. pag. Print.
-
-Fielding, Roy Thomas. ``Architectural Styles and the Design of
-Network-Based Software Architectures.'' University of California,
-Irvine, 2000. Print.
-
-Burke, Bill. RESTful Java with JAX-RS. California: O-Reilly, 2010.
-Print.
-
-Pontesegger, Christian. ``Eclipse Advanced Scripting Environment.''
-N.p., n.d. Web. 1 Jan. 2017.
-
-Billings, Jay Jay. ``Eclipse ICE.'' Project Website. Eclipse ICE. N.p.,
-21 Oct. 2016. Web. 1 Jan. 2017.
-
-Tibbitts, Beth R., Gregory R. Watson, and Craig E. Rasmussen. ``An
-Integrated Approach to Improving the Parallel Application Development
-Process.'' 2009 IEEE International Symposium on Parallel \& Distributed
-Processing (IPDPS). Los Alamitos, CA, USA: IEEE Computer Society, 2009.
-1--8. IEEE Computer Society. Web.
-
-Billings, Jay Jay. ``Eclipse Advanced Visualization Project.'' Text.
-projects.eclipse.org. N.p., 16 Dec. 2015. Web. 1 Jan. 2017.
-
-Billings, Jay Jay et al. ``A Domain-Specific Analysis System for
-Examining Nuclear Reactor Simulation Data for Light-Water and
-Sodium-Cooled Fast Reactors.'' Annals of Nuclear Energy 85 (2015):
-856--868. ScienceDirect. Web.
-
-Billings, Jay Jay. ``The Brand New Neutron Reflectivity Simulator in
-Eclipse ICE and What It Took to Make It.'' EclipseCon Europe 2015.
-Ludwigsburg Germany: Eclipse Foundation, 2015. Web. 25 May 2016.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Brooks, Christopher. ``Triquetrum: Models of Computation for
-  Workflows.'' EclipseCon NA 2016. N.p., 4 Dec. 2015. Web. 1 Jan. 2017.
-\item
-  Brooks, Christopher, and Jay Jay Billings. ``Introducing Triquetrum, A
-  Possible Future for Kepler and Ptolemy II.'' Procedia Computer Science
-  80 (2016): 2449--2454. ScienceDirect. Web. International Conference on
-  Computational Science 2016, ICCS 2016, 6-8 June 2016, San Diego,
-  California, USA.
-\end{enumerate}
-
-Humble, T. S. et al. ``An Integrated Programming and Development
-Environment for Adiabatic Quantum Optimization.'' Computational Science
-\& Discovery 7.1 (2014): 015006. Institute of Physics. Web.
-
-McCaskey. ``Scientific Simulation with Eclipse - From Zero Code to
-Running on Lots of Cores in 10 Minutes.'' EclipseCon NA 2016. Reston VA:
-Eclipse Foundation, 2015. Web. 26 May 2016.
-
-Pannala, S. et al. ``Multiscale Modeling and Characterization for
-Performance and Safety of Lithium-Ion Batteries.'' Journal of Applied
-Physics 118.7 (2015): 072017. scitation.aip.org. Web.
-
-``ORNL-QCI/Xacc.'' GitHub. N.p., n.d. Web. 1 Jan. 2017.
-
-Mandal, Nandita et al. ``Integrating Existing Scientific Workflow
-Systems: The Kepler/Pegasus Example.'' Proceedings of the 2Nd Workshop
-on Workflows in Support of Large-Scale Science. New York, NY, USA: ACM,
-2007. 21--28. ACM Digital Library. Web. 20 Dec. 2016. WORKS '07.
-
-Graham, Jonah. ``Eclipse January.'' Text. projects.eclipse.org. N.p., 6
-Apr. 2016. Web. 1 Jan. 2017.
-
-\section{Footnotes}\label{footnotes}
-
-1: The authors have identified many different combinations of these
-activities that define workflow ``classes.'' When possible, every effort
-is made to give the classes funny names such as ``The Re-Run'' or ``The
-Graduate Student.''
-
-2: An upcoming update to the API will see the formal introduction of
-IWorkflow, IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's
-API language closer to other systems. This must be done with care to
-satisfy backwards compatibility requirements on the present API.
+\begin{table*}[!htbp]
+\begin{tabularx}{\textwidth}{|l|X|X|}
+\hline
+S1 & Current Code Version & 2.2.1 \tabularnewline\hline
+S2 & ermanent link to executables of this version &
+\url{https://www.eclipse.org/downloads/download.php?file=/ice/builds/2.2.1/}
+ \tabularnewline\hline 
+S3 & Legal Software License & Eclipse Public License 1.0 \tabularnewline\hline
+S4 & Computing platforms/Operating Systems & Windows (32/64-bit), Mac OS/X,
+Linux (32/64-bit) \tabularnewline\hline 
+S5 & Installation requirements \& dependencies & Java 1.8 or
+greater \tabularnewline\hline
+S6 & If available, link to user manual - if formally published include a
+reference to the publication in the reference list &
+\url{https://wiki.eclipse.org/ICE} \tabularnewline\hline 
+S7 & Support email for questions & ice-users@eclipse.org \tabularnewline\hline
+\end{tabularx}
+\caption{Current Executable Software}
+\label{execTable}
+\end{table*}

### 2017-04-25 src/comments.tex
Addressed comments by Jordan and Dasha.
Signed-off-by: Jay Jay Billings<billingsjj@ornl.gov>

Jordan Deyton:

1 - abstract - "feedback driven way w*h*ere solutions"
1 - keywords didn't render correctly?
3 - 2.0.1. (1st paragraph) - "Those same computational scientist*s*"
4 - Executing jobs (1st paragraph) - "remotely remotely"
4 - Analyzing results (1st paragraph) - "in preparation for follow*ing* simulations"
5 - 3.1 (second paragraph) - "since it often changes *at* run time"
6 - (second paragraph) - "section ??"
6 - (just before last paragraph) - the caption for table 1 is shown here
7 - 3.1.2 (1st paragraph) - "By conventional"
8 - 3.2 (2nd paragraph) - "ICE originally *?* a significant amount"
10 - 4.3 (1st paragraph) - "an ICE-based workbench for perform*ing* simulations"
13 - (3rd paragraph) - "Other tools create*d* with ICE"
13 - (3rd paragraph) - "was a*s* simple as"
14 - 7 - "and described how its has been"

Dasha Gorin:

Abstract:
"Computational scientists typically interact with simulation software in a feedback driven way where solutions and workflows are developed iteratively and simultaneously."

Also on page 11, section 4.5 "Quantum Computing":
As quantum computing grows, so too does the need for sophisticated software...

Bottom of page 13:
"Interested parties may inquire by contacting the corresponding author or visiting the website."

Hari:

I hope you are doing well! Overall the paper looks good. Thanks for including me on it!

For grammar: I would just read through the text to correct some minor spelling and grammar issues. Minor stuff like the following sentence: "ICE originally a significant amount of visualization support"

For the story: Are you planning a general software infrastructure paper?

The highlights and use cases make a solid argument, but the tone of the paper comes off a little reserved.

For instance,  "The impact of software tools such as ICE are hard to quantify. However, there are several places where ICE has significantly assisted its development team and others."

I personally like being realistic and a bit humble that ICE isn't being touted as the best thing since sliced bread without enough proven track record, which a lot of software papers tend to do.

At the same time this strategy might have the opposite effect where reviewers don't think it's good enough because the authors aren't excited about their work. Maybe rewriting this or moving it later or to end of the section would be prudent. Then the text would suggest: "Look at the cool and useful stuff ICE is already capable of, but this is just the beginning and ICE has an exciting future ahead of it"

### 2017-04-25 src/content.tex
Addressed comments by Jordan and Dasha.
Signed-off-by: Jay Jay Billings<billingsjj@ornl.gov>

@@
 creating input, (2) executing jobs, (3) analyzing results, (4) managing
-data, and (5) modifying code. Those same computational scientist would
+data, and (5) modifying code. Those same computational scientists would
 most likely find these activities difficult for all codes with which
@@
 hardware resources; these resources are usually off site (i.e.,
-physically unavailable to the user) and are accessed remotely remotely
+physically unavailable to the user) and are accessed remotely
 through Secure Shell (SSH) connections or similar protocols. Remote
@@
 extracting publication quality images or movies from that data. Other
-cases may include analyzing results in preparation for follow
+cases may include analyzing results in preparation for follow on
 simulations or performing feature extraction, classification, or
@@
 Users initiate requests to create, edit, update or delete workflows from
-the \emph{ICE Client} (the workbench). The list of available workflow
+the \emph{ICE Client} (the workbench). The list of available workflows
 that can be created is provided dynamically to the \emph{ICE Client} by
-the \emph{ICE Core}, which acts as a kind of server. This information is
-provided dynamically since it often changes as run time based on the
+the \emph{ICE Core}, which acts as a server. This information is
+provided dynamically since it often changes at run time based on the
 configuration of available workflow components in the registry and on
@@
 satisfy backwards compatibility requirements on the present API.}
-
-Table 1: Class Descriptions for Items, Forms and Actions
 
@@
 Likewise, if output is small enough, ICE will automatically move it back
-to local directory. By conventional, all paths in ICE's Forms are
+to local directory. By convention, all paths in ICE's Forms are
 relative to the workspace root path. Workspace directories are specified
@@
 \subsubsection{Extending the Framework to Add Custom
-Workflows}\label{extending-the-framework-to-add-custom-workflows}
+Workflows}\label{framework}
 
@@
 sophisticated user environment for computational science projects (see
-``Impact'' below) and as a visualization tool. ICE originally a
+``Impact'' below) and as a visualization tool. The ICE source code originally contained a
 significant amount of visualization support, but at the request of users
@@
 warpage and deformation due to sintering in the design phase of the
-part. Figure 3 shows an ICE-based workbench for perform simulations of
+part. Figure 3 shows an ICE-based workbench for performing simulations of
 this process with visualizations of the pre- and post-simulation
@@
 
-As quantum computing grows, so to does the need for sophisticated
+As quantum computing grows, so too does the need for sophisticated
 software that can utilize quantum hardware or perform calculations on
@@
 deploy new simulation environments for problems, such as the binder jet
-modeler and reflectivity tools mentioned earlier. Other tools create
+modeler and reflectivity tools mentioned earlier. Other tools created
 with ICE may not radically invent something new, but they tend to
@@
 development activities because of the tools that ICE provides or learned
-new technologies because access to new tooling was a simple as
+new technologies because access to new tooling was as simple as
 installing more plugins through the Eclipse Marketplace.
@@
 Eclipse ICE is an open source project and the authors welcome and encourage
-engagement and contributions from readers. Interested parties my inquire by
+engagement and contributions from readers. Interested parties may inquire by
 contacting the corresponding author or visiting the website.
@@
 grid-based workflow management systems. This work presented the Eclipse
-Integrated Computational Environment (ICE) and described how its has
+Integrated Computational Environment (ICE) and described how it has
 been used to address interdisciplinary problems in modeling and

### 2017-04-25 src/main.tex
First full draft of the article.
Merged manually from github.com/jayjaybillings/thesis. Includes edits
from Sam Crawford and the most recent copy of the article and
bibliography.

Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>
Modified to post to Arxiv as a preprint.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>
Addressed comments by Jordan and Dasha.
Signed-off-by: Jay Jay Billings<billingsjj@ornl.gov>

@@
 \documentclass{elsart}
+%% For Arxiv.org
+\pdfoutput=1
 
@@
 \usepackage{booktabs}
+\usepackage[hyphens]{url}
 
@@
 management systems. Computational scientists typically interact with
-simulation software in a feedback driven way were solutions and
+simulation software in a feedback driven way where solutions and
 workflows are developed iteratively and simultaneously. This work
@@
 areas are presented as well as its impact on the community.
-
-%---------------FIXME! Table reference!
-%\begin{table*}[t]
-%\begin{tabularx}{\textwidth}{|l|X|l|}
-%\hline
-%Class & Class Description & Object Description\tabularnewline\hline
-%Item & Java class with code to execute an abstract workflow. Provides a
-%Form. & Concrete workflow executor.\tabularnewline\hline
-%Form & Description and template of the data needed for the Item to
-%process the workflow. & User-modified workflow data.\tabularnewline\hline
-%Action & Java class for executing a specific task in the workflow. Used
-%by Items. & Concrete workflow task executor.\tabularnewline\hline
-%\end{tabularx}
-%\caption{Class Descriptions for Items, Forms and Actions}
-%\end{table*}
 

### 2017-05-23 src/content.tex
Touched up the conclusions to address some of Sam's suggestions. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 greatly from experimentalists or those who primarily interact with
-grid-based workflow management systems. This work presented the Eclipse
-Integrated Computational Environment (ICE) and described how it has
-been used to address interdisciplinary problems in modeling and
-simulation for energy science. One interesting avenue for future
-exploration is coupling or integrating ICE with other workflow tools
-such as Aiida, Triquetrum, Kepler and Pegasus. It remains as abundantly
-clear now as it was in Mandal's 2007 paper that the best of all workflow
-management tools will be needed to address high-performance computing
-problems at the exascale and beyond.
+grid-based workflow management systems, which has driven the creation of
+additional workflow management systems to meet those needs. This work 
+presented the Eclipse Integrated Computational Environment (ICE) and 
+described how it has been used to address interdisciplinary problems in 
+modeling and simulation for energy science. Of particular note is the
+difference in architecture between a workflow management system focused
+on modeling and simulation compared to those focused on grids. ICE's broad
+applicability across a number of topics in energy science suggests that
+there are opportunities for these systems in general. Finally, one 
+interesting avenue for future exploration is coupling or integrating ICE 
+with other workflow tools such as Aiida, Triquetrum, Kepler and Pegasus,
+which would make it possible to combine the best of grid and modeling and
+simulation workflows to address greater challenges.
 

### 2017-05-23 src/main.tex
Fixed messed up superscripts in affiliations. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 
-\address{$^1$Computer Science and Mathematics Division, Oak Ridge National
+\address{$^{1}$Computer Science and Mathematics Division, Oak Ridge National
 Laboratory, Oak Ridge, TN 37830, USA}
-\address{$^2$The Bredesen Center for Interdisciplinary Research and Graduate
+\address{$^{2}$The Bredesen Center for Interdisciplinary Research and Graduate
 Education, University of Tennessee, 444 Greve Hall, 821 Volunteer
   Blvd. Knoxville, TN 37996-3394}
-\address{$^3$University of Washington, Seattle, WA 98105}
-\address{$^4$General Electric Company, 3200 North Grandview Blvd Waukesha, WI
+\address{$^{3}$University of Washington, Seattle, WA 98105}
+\address{$^{4}$General Electric Company, 3200 North Grandview Blvd Waukesha, WI
 53188-1678}
-\address{$^5$Georgia Institute of Technology North Avenue, Atlanta, GA 30332}
-\address{$^6$Kichwa Coders Ltd. 1 Plomer Green Avenue Downley, High Wycombe
+\address{$^{5}$Georgia Institute of Technology North Avenue, Atlanta, GA 30332}
+\address{$^{6}$Kichwa Coders Ltd. 1 Plomer Green Avenue Downley, High Wycombe
 HP13 5LN United Kingdom}
-\address{$^7$Northwestern University 633 Clark Street Evanston, IL 60208}
-\address{$^8$Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley,
+\address{$^{7}$Northwestern University 633 Clark Street Evanston, IL 60208}
+\address{$^{8}$Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley,
 CA 94720}
-\address{$^9$Department of Computer Science, and Department of Biological
+\address{$^{9}$Department of Computer Science, and Department of Biological
 Sciences, Purdue University, West Lafayette, IN 47906} 
-\address{$^10$Acato Information Management, LLC 114 Union Valley Rd. Oak Ridge,
+\address{$^{10}$Acato Information Management, LLC 114 Union Valley Rd. Oak Ridge,
 TN 37830}
-\address{$^11$Colorado State University Fort Collins, CO 80523}
+\address{$^{11}$Colorado State University Fort Collins, CO 80523}
 

### 2017-05-30 src/content.tex
Pushing changes from Sam's edits. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

--- 2017-04-25 src/content.tex
@@
 
-In previous work, Billings et. al., discovered through requirements
-gathering interviews that many of the difficulties using
-high-performance modeling and simulation software fall broadly into five
-distinct categories, \cite{billings_designing_2009}. These activities,
-detailed in section \ref{workflow-model}, include (1) creating input,
+In previous work, Billings et al. interviewed simulation and modeling 
+software users to compile a list of requirements for implementing and 
+using these kinds of applications. In the process, they discovered 
+that many of the difficulties inherent in using
+high-performance modeling and simulation software fall into five
+distinct categories \cite{billings_designing_2009}. These activities,
+detailed in Section \ref{workflow-model}, include (1) creating input,
 (2) executing jobs, (3) analyzing results, (4) managing data, and (5)
@@
 
-Efforts to address these five issues have previously resulted in general
-purpose scientific workflow tools like Kepler, 
-\cite{ludascher_scientific_2006}, or myopic tools that only satisfy a single
-set of requirements for a single piece of software or platform. These
-are opposing extremes, but a middle-of-the-road solution is also
+Previous efforts to address these five issues have resulted in general
+purpose scientific workflow tools like Kepler \cite{ludascher_scientific_2006} 
+or myopic tools that only satisfy a single
+set of requirements for a single piece of software or a single platform. These
+are opposite extremes, but a middle-of-the-road solution is also
 possible. A workflow engine could be developed that limits its scope to
@@
 minor additional development, a rich application programming interface
-(API) could be exposed so that highly-customized solutions could still
+(API) could be exposed so that highly customized solutions could still
 be made based on this limited workflow engine.
@@
   Modeling and simulation activities can be described in a succinct
-  workflow model, (see ``Workflow Model'').
+  workflow model (see ``Workflow Model'').
 \item
   An architecture for such a workflow system can satisfy the model of
-  workflows in an extensible way, (see ``Software Architecture'').
+  workflows in an extensible way (see ``Software Architecture'').
 \item
   Such a system is applicable to a suite of problems in energy science,
-  including virtual battery simulations, additive manufacturing and
-  other areas, (see ``Illlustrative Examples'').
+  including virtual battery simulations and additive manufacturing, 
+  among others (see ``Illlustrative Examples'').
 \end{itemize}
@@
 This section concludes with an introduction of the workflow model addressed by
-ICE. Section \ref{software-description} presents the details of the software
-from an architecture perspective while section \ref{illustrative-examples}
-provides a set of comprehensive examples. Finally, this paper concludes with a
-presentation of the impact, (section \ref{impact}), and sample code,
-(section \ref{sample-code-tutorials-and-other-resources}).
+ICE. Section \ref{software-description} details the software
+from an architectural perspective, while Section \ref{illustrative-examples}
+provides a set of comprehensive examples. A
+presentation of the impact is included in Section \ref{impact}, and sample 
+code is provided in Section \ref{sample-code-tutorials-and-other-resources}.
 
@@
 simulation that can be abstracted into a lightweight theoretical
-framework based broadly on five high-level \emph{activities}: (1)
+framework based broadly on five high-level activities: (1)
 creating input, (2) executing jobs, (3) analyzing results, (4) managing
@@
 one or more scientific software package or code results in a unique
-\emph{workflow}. Such a workflow is normally, but not always, requested
-by a human user and orchestrated by a \emph{Workflow Management System
-(WMS)}.
+workflow. Such a workflow is normally, but not always, requested
+by a human user and orchestrated by a workflow management system.
 
 The most obvious workflow for any individual simulation code or
-collection of codes is to string the activities together: the user's
+collection of codes is to string the activities together, where the user's
 workflow is to create the input, launch the job, perform some analysis,
-and manage the data---possibly modifying the code in the process. There
-are many other combinations however, including re-running jobs with
-conditions or modifications or analyzing someone else's data (See
-footnote 1).\footnote{The
-authors have identified many different combinations of these activities that
+and manage the data---possibly modifying the code in the process. However, 
+there are many other combinations, including re-running jobs with
+conditions or modifications or analyzing someone else's data.\footnote{The
+authors have identified many unique combinations that
 define workflow ``classes.'' When possible, every effort is made to give the
-classes funny names such as ``The Re-Run'' or ``The Graduate Student.''}
+classes colloquial names such as ``The Re-Run'' or ``The Graduate Student.''}
 
@@
 input files will be described in a ``main'' input file that acts as a
-kind of manifest, describing and providing links to all necessary
+kind of manifest to describe---and provide links to---all necessary
 information for a given problem.
@@
 this includes viewing the results of a simulation on a mesh or grid and
-extracting publication quality images or movies from that data. Other
-cases may include analyzing results in preparation for follow on
+extracting publication-quality images or movies from that data. Other
+cases may include analyzing results in preparation for follow-on
 simulations or performing feature extraction, classification, or
@@
 known, certainly qualifies as executing a job; however, analysis of
-model and simulation results is far from simple data reduction, and is
+model and simulation results is far from simple data reduction and is
 generally far more interactive for computational scientists.
@@
 goal,'' \cite{yu_taxonomy_2005}. Others, such as Pizzi et al., subscribe to
-similar definitions, \cite{pizzi_aiida:_2016}. This ``process'' view is
+similar definitions \cite{pizzi_aiida:_2016}. This ``process'' view is
 acceptable where the workflow is static and does not require additional
@@
 the benefit of removing concrete elements such as hardware properties or
-software details that distract from details of workflows and WMSes. That
-is, considerations such as memory usage and raw performance are
-important, but questions about the abstract workflow or what the WMS
-should do are far more important.
+software details that distract from details of workflows and workflow 
+management systems. That is, considerations such as memory usage and 
+raw performance are important, but questions about the abstract workflow 
+or what the workflow management system should do are far more important.
 
@@
 
-Workflows and tasks in ICE are not explicitly treated as trees -
-Directed Acyclic Graphs, (DAGS) - as is common with grid workflow tools,
-\cite{yu_taxonomy_2005}. Instead, ICE's design is inspired by Representational
-State Transfer (REST), \cite{fielding_architectural_2000}.
+Workflows and tasks in ICE are not explicitly treated as trees, or
+directed acyclic graphs (DAGS), as is common with grid workflow tools
+\cite{yu_taxonomy_2005}. Instead, ICE's design is inspired by representational
+state transfer (REST) \cite{fielding_architectural_2000}.
 
-Users initiate requests to create, edit, update or delete workflows from
-the \emph{ICE Client} (the workbench). The list of available workflows
-that can be created is provided dynamically to the \emph{ICE Client} by
-the \emph{ICE Core}, which acts as a server. This information is
-provided dynamically since it often changes at run time based on the
-configuration of available workflow components in the registry and on
+Users initiate requests to create, edit, update, or delete workflows from
+the ``ICE Client'' (the workbench). The list of available workflows
+that can be created is provided dynamically to the ICE Client by
+the ``ICE Core,'' which acts as a server. This information is
+provided dynamically because the information often changes at run time based on 
+both the configuration of available workflow components in the registry and on
 persisted workflows that users have saved in their workspace.
-Information about workflows are provided from the Core to the Client
-through \emph{stateless Forms} that describe the workflow and provide
+Information about workflows is provided to the Client by the Core
+through stateless ``Forms'' that describe the workflow and provide
 all the necessary information to understand \emph{what} should process
-the workflow, (but not \emph{how} it should be processed). Once users
+the workflow (but not \emph{how} it should be processed). Once users
 modify the description of the workflow in the Form to provide their
 specific details, the Client dispatches a request to the Core to modify
-or process the workflow. The Core then uses the information in the Form
+or process the workflow. The Core then uses the information from the Form
 to perform a service lookup for \emph{what} should process the workflow.
 
-Workflows in ICE are encoded in and processed by \emph{Items} and each
+Workflows in ICE are encoded in and processed by ``Items'' and each
 workflow type is a subclass of Item. Items are registered dynamically
-through a service registry in ICE, (see section \ref{framework}), and
+through a service registry in ICE (see Section \ref{framework}) and
 provide the Forms for the ICE Core and Client. Since ICE's design is
@@
 
-Individual components of workflows, i.e. - workflow ``tasks'' or
-``nodes'' - are either encoded directly in the workflow's subclass of
-Item or provided as \emph{Actions} that are dynamically registered with
-an \emph{Action Factory} and obtained at runtime. Table 1. describes the
-differences between Items, Actions, and Forms.\footnote{An upcoming update to the API will see the formal introduction of
+Individual components of workflows (i.e., workflow ``tasks'' or
+``nodes'') are either encoded directly in the workflow's subclass of
+Item or provided as ``Actions'' that are dynamically registered with
+an ``Action Factory'' and obtained at runtime. Table 1 describes the
+differences between Items, Actions, and Forms.\footnote{An upcoming 
+update to the API will include the formal introduction of
 IWorkflow, IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's
@@
 \end{tabularx}
-\caption{Class Descriptions for Items, Forms and Actions}
+\caption{Class Descriptions for Items, Forms, and Actions}
 \end{table*}
@@
 headless web server with a remote service interface and a web
-Application Programming Interface (API). The web API is also used as the
-primary means of providing real-time feedback and monitoring support in
-ICE.
+API. The web API is also used as the primary means of providing real-time 
+feedback and monitoring support in ICE.
 
@@
 created, it enters the ``Form Ready'' state to indicate that it could,
-in theory, be processed after a user reviews it. After that review it
-enters the ``Ready to Process'' state before and the ``Processed'' state
-after it is processed. There are several additional states for errors.
+in theory, be processed after a user reviews it. After that review, it
+enters the ``Ready to Process'' state before it is processed and 
+the ``Processed'' state after it is processed. There are several additional 
+states for errors.
 
 This design is very important. First, it means that all workflows in
-ICE, regardless of their actual details and function, can only behave in
-a specific set of known, predictable ways. This greatly simplifies the
-way that the Core manages and interacts with Items. Second, it
-explicitly delineates which workflows can be executed from those that
-must still receive some configuration because it formalizes state and
-error checks. Finally, it allows developers implementing Items and
-Actions to specify by contract what is required before proceeding to the
+ICE, regardless of their actual details and functions, can only behave in
+a specific set of known and predictable ways, and this predictability 
+simplifies the way the Core manages and interacts with Items. Second, by
+formalizing state and error checks, it explicitly delineates which workflows 
+can be executed from those that must receive additional configuration. 
+Finally, it allows developers implementing Items and
+Actions to specify, by contract, what is required before proceeding to the
 next task, processing the workflow, or declaring a successful execution.
@@
 
-ICE persists permanent copies of Forms to disk when workflows are
-created and modified in a special directory called a \emph{workspace}.
-Workspaces can contain projects, folders and files, including data,
-code, input and output. ICE automatically manages local and remote (or
+When workflows are created and modified, ICE saves permanent copies of 
+Forms to disk in a special directory called a ``workspace.''
+Workspaces can contain projects, folders, and files; including data,
+code, input, and output. ICE automatically manages local and remote (or
 even local \emph{to} remote) transfers of data files when executing
@@
 the workflow and available in the project directory of the workspace.
-Likewise, if output is small enough, ICE will automatically move it back
+Likewise, if the output is small enough, ICE will automatically move it back
 to local directory. By convention, all paths in ICE's Forms are
@@
 
-ICE handles persistence using a \emph{persistence provider}. The only
-default persistence provider uses JAX-RS, \cite{burke_restful_2010}, to write
-Forms to XML. In principle other persistence providers could replace the
-XML-based provider since it is registered as a dynamic service, and in
-the past a JAX-P based provider has been used.
+ICE handles persistence using a ``persistence provider.'' The
+default persistence provider uses JAX-RS to write Forms to 
+XML~\cite{burke_restful_2010}. In principle, other persistence providers 
+could replace the XML-based provider since it is registered as a dynamic 
+service, and a JAX-P based provider has been used in the past.
 
@@
 
-ICE is an Eclipse Rich Client Platform (RCP) application,
-\cite{mcaffer_eclipse_2010}. It has a plugin architecture based on Equinox, the
-reference implementation of the Open Service Gateway Initiative (OSGi) framework specification, \cite{mcaffer_osgi_2010}. It uses over 1200 additional
-packages from the Eclipse ecosystem to provide services such as language
-support and visualization to users. Each unique element of ICE described
-in this work, including the client, core, all Items, data structures and
-many others are provided as plugins to Equinox. Most plugins are
-dynamically managed and provided as services that can be obtained from a
-service registry. All file I/O in ICE, with only a few exceptions,
-interacts with the RCP's Resources plugin. This includes remote
-resources that are managed with the Eclipse Parallel Tools Platform,
+ICE is an Eclipse Rich Client Platform (RCP) application
+\cite{mcaffer_eclipse_2010}, and has a plugin architecture based on 
+Equinox, which is the reference implementation of the Open Service Gateway Initiative (OSGi) 
+framework specification \cite{mcaffer_osgi_2010}. ICE uses over 1,200 additional
+packages from the Eclipse ecosystem to provide services like language
+support and visualization. Each unique element of ICE described
+in this work---including the Client, Core, Items, and data structures---are 
+provided as plugins to Equinox. Most plugins are managed
+dynamically and provided as services that can be obtained through a
+service registry. Most file I/O in ICE, with only a few exceptions,
+interacts with the RCP's resources plugin. This also includes remote
+resources that are managed with the Eclipse Parallel Tools Platform
 \cite{tibbitts_integrated_2009}.
 
-It is not possible to graphically create new Items in ICE. Users can
-only use the workflow Items provided with their version of ICE unless
-they provide their own plugin to the framework. This can seem like an
-onerous task to the novice user especially if they do not know Java, but
+It is not possible to create new Items in ICE graphically, and---unless 
+they provide their own plugin to the framework---users can
+only use the workflow Items provided by their version of ICE. This can seem like an
+onerous task to the novice user, especially if they do not know Java, but
 this design was chosen because it is, in the opinion of the authors, a
-far more sophisticated and sustainable way to create workflows than
-through wiring diagram.
+far more sophisticated and sustainable way to create workflows than, for example,
+using a wiring diagram.
 
-ICE provides built-in development tools to auto-generate ``stubs'' of
+ICE provides built-in development tools to automatically generate ``stubs'' of
 plugins that can then be installed into the framework. This
@@
 know how to interact with the framework. Furthermore, ICE provides a
-rich API, documentation, tutorials, and tools to further simply the
+rich API, documentation, tutorials, and tools to further simplify the
 process.
 
-There are many situations where graphically configuring workflows is
+There are many situations where configuring workflows graphically is
 unacceptable, such as when a very large number of workflows will be
@@
 management system. ICE includes the Eclipse Advanced Scripting
-Environment, \cite{pontesegger_eclipse_2015}, (EASE), for scripting because it
-provides a native way to script Eclipse RCP projects in Javascript,
+Environment (EASE)~\cite{pontesegger_eclipse_2015} for scripting because it
+provides a way to script Eclipse RCP projects natively in Javascript,
 Jython, and Python. This also makes it possible to extend the
@@
 Outside of the development team, ICE is commonly deployed as a
-sophisticated user environment for computational science projects (see
-``Impact'' below) and as a visualization tool. The ICE source code originally contained a
+sophisticated user environment for computational science projects 
+(see Section \ref{impact}) and as a visualization tool. The ICE source code originally contained a
 significant amount of visualization support, but at the request of users
-in the community that support was ``spun off'' in early 2016 as a
-separate visualization project, the Eclipse Advanced Visualization
-Project, EAVP, \cite{billings_eclipse_2015}.
+in the community that support was ``spun off'' in early 2016 as the 
+Eclipse Advanced Visualization Project (EAVP)~\cite{billings_eclipse_2015}.
 
@@
 The role that ICE plays as a workflow tool is best illustrated by the
-various ways that it has been deployed.
+various ways in which it has been deployed, as shown in the following 
+examples.
 
@@
 as part of their research into safety and performance characteristics of
-lithium ion batteries, \cite{pannala_multiscale_2015}. VIBE provides ICE to
-users as part of its distribution. New workflows were added to ICE to create
-multiple types of input, configure the simulation software, and launch
-simulations of virtual batteries. Interactive 3D visualizations of the
-results were embedded in the launcher so that users would quickly find
-their results. Figure 1 shows the results from a temperature
-distribution of a prismatic cell battery simulated during discharge.
+lithium ion batteries \cite{pannala_multiscale_2015}. VIBE includes ICE
+as part of its distribution, and new workflows were added to ICE to enable users
+to add multiple types of input, configure the simulation software, and launch
+simulations of virtual batteries. Interactive 3-D visualizations of the
+results were embedded in the launcher so that users can quickly find
+their results. Figure 1 shows a (simulated) prismatic-cell battery's temperature
+distribution during discharge.
 
@@
 VIBE 1.0 is available as a virtual machine in which the simulation
-software and ICE are provided side by side. More recent efforts for VIBE
-1.1 by the VIBE development team include providing the simulation
+software and ICE are provided side by side. The VIBE team's more recent 
+efforts for VIBE~1.1 include providing the simulation
 software in Docker containers so that users can download the latest,
@@
 
-The MOOSE Framework is a powerful, easy to use multiphysics framework
-developed at the Idaho National Laboratory, \cite{gaston_moose:_2009}. ICE
+The MOOSE Framework is a powerful, easy-to-use multiphysics framework
+developed at Idaho National Laboratory \cite{gaston_moose:_2009}. ICE
 provides workflow tools for MOOSE as well as specialized class
 generation utilities for developing custom MOOSE kernels. Many of the
-MOOSE tools in ICE were developed closely with the MOOSE team to closely
-reproduce various aspects of MOOSE's user interface, Peacock. Figure 2
-shows an example of the ICE workbench for a simple structural mechanics
-problem solved with the MOOSE framework, \cite{mccaskey_scientific_2015}.
+MOOSE tools in ICE were developed closely with the MOOSE team to
+reproduce various aspects of MOOSE's user interface, known as ``Peacock.'' 
+Figure 2 shows an example of the ICE workbench for a simple structural mechanics
+problem solved using the MOOSE framework \cite{mccaskey_scientific_2015}.
 
@@
 
-There are over three hundred MOOSE-based applications and it is very
+There are over three hundred MOOSE-based applications, and it is very
 easy to create new MOOSE applications. The ICE development team uses ICE
-and MOOSE to quickly solve energy science problems with high-performance
-computing resources and deploy domain specific workbenches. ICE includes
-support for automatically downloading and building MOOSE from its GitHub
-project, which then makes it possible to immediately begin developing
-complex multiphysics applications using the Eclipse C Development Tools,
-which are pre-installed in ICE to facilitate this interaction. Once the
-new MOOSE-based application is built, it will automatically work with
+and MOOSE to quickly solve energy science problems with HPC resources 
+and to deploy domain-specific workbenches. ICE includes
+support for automatically downloading and building MOOSE from MOOSE's GitHub
+repository. This integration enables users to immediately begin developing
+complex multiphysics applications using the pre-installed Eclipse C Development 
+Tools. Once the new MOOSE-based application is built, it will automatically work with
 the MOOSE workflow tools in ICE, although developers can also create
@@
 significantly increases part strength by decreasing the part porosity
-and eliminating voids. The downside of this process is that it causes
-the part to shrink and warp. An ideal near-net-shape process that
-combined binder jetting with solid-state sintering would thus consider
-warpage and deformation due to sintering in the design phase of the
-part. Figure 3 shows an ICE-based workbench for performing simulations of
+and eliminating voids. However, this process does cause the resulting
+product to shrink and warp from its original layout. An ideal, near-net-shape, 
+process combines binder jetting with solid-state sintering and accounts
+for warpage and deformation in the part's design phase. 
+Figure 3 shows an ICE-based workbench for performing simulations of
 this process with visualizations of the pre- and post-simulation
@@
 (which was written in ICE as described above) for simulating the
-deformation of the cantilevers.
+deformation of the cantilevers. The full application for this work 
+is expected to be released near the end of 2017.
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 
-The full application for this work is expected to be released near the
-end of 2017.
-
 \subsection{Neutron Reflectivity}\label{neutron-reflectivity}
 
-ICE includes a small utility for simulating neutron reflectivity and
-comparing the results to data, \cite{billings_brand_2015}. This was developed
-in collaboration with colleagues at the Spallation Neutron Source to
-replace an older utility written in Visual Basic and distributed via
-Excel macros. The newer utility in ICE is capable of processing a single
-workflow and is shown in figure 4.
+ICE also includes a small utility for simulating neutron reflectivity and
+comparing the results to other data \cite{billings_brand_2015}. This 
+utility was developed in collaboration with a team at ORNL's Spallation Neutron 
+Source to replace an older utility that was originally written in Visual Basic and 
+distributed via Excel macros. The new utility, developed in ICE and 
+shown in Figure 4, is capable of processing a single workflow.
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 
-As quantum computing grows, so too does the need for sophisticated
+As quantum computing grows, the need for sophisticated
 software that can utilize quantum hardware or perform calculations on
-simulated quantum hardware. Humble et al. created a simulator for
+simulated quantum hardware becomes more pressing. Humble et al. created a simulator for
 adiabatic quantum computers where workflows were added to ICE to support
-interaction with the simulator, but also to process large sets of
-quadratic binary optimimzation problems, \cite{humble_integrated_2014}. Figure 5
+interaction with the simulator and to process large sets of
+quadratic binary optimization problems \cite{humble_integrated_2014}. Figure 5
 shows the workbench for this project.
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 ICE also supports other quantum computing projects, including the
-eXtreme-scale ACCelerator (XACC) programming framework,
+eXtreme-scale ACCelerator (XACC) effort
 \cite{mccaskey_ornl-qci/xacc_2016}. XACC is a programming framework for
-extreme-scale, post-exascale accelerator architectures that integrates
-alongside existing conventional applications.
+extreme-scale, post-exascale accelerator architectures that can be
+integrated alongside existing, conventional applications.
 
@@
 There are many examples of ICE's role in modeling and simulation
-projects for nuclear energy, but readers are referred to the work in
-\cite{billings_domain-specific_2015} for an extreme example of the level of
-customization that is possible in ICE. Support for the ``Reactor
+projects for nuclear energy, but for an example of the level of
+customization that is possible in ICE, readers are referred to the work outlined in
+\cite{billings_domain-specific_2015}. Support for the ``Reactor
 Analyzer'' was dropped in ICE 2.1.8, but it demonstrated ICE's ability
@@
 
-The impact of software tools such as ICE are hard to quantify. However,
-there are several places where ICE has significantly assisted its
+The impact of software tools like ICE is difficult to quantify. However,
+there are several examples of when ICE has significantly assisted its
 development team and others.
@@
 One pressing area of interest and impact is that of interoperability
-between workflow systems. There is significant prior art in combining
-large workflow management systems, such as that Mandal et al.,
-\cite{mandal_integrating_2007}, but the end goal of gaining the greatest
+between workflow systems. There have been significant prior efforts in combining
+large workflow management systems (e.g., Mandal et al.
+\cite{mandal_integrating_2007}), but the end goal of gaining the greatest
 advantage by using the best capabilities from multiple systems remains elusive.
@@
 allows it to connect to other workflow environments, such as Triquetrum,
-quite easily, \cite{brooks_introducing_2016}. Triquetrum, (like Kepler in
-\cite{mandal_integrating_2007}), is a Ptolemy-based workflow engine,
+quite easily \cite{brooks_introducing_2016}. Triquetrum, like Kepler in
+\cite{mandal_integrating_2007}, is a Ptolemy-based workflow engine
 \cite{brooks_triquetrum:_2015}. Several of the authors of this paper are using
@@
 
-It is widely known that tools that make researchers more productive tend
+It is widely known that tools that enable researchers to be more productive tend
 to improve the pursuit of existing research. The high extensibility of
@@
 have made it possible for researchers on the development team to quickly
-deploy new simulation environments for problems, such as the binder jet
-modeler and reflectivity tools mentioned earlier. Other tools created
-with ICE may not radically invent something new, but they tend to
-streamline interactions with those tools. Many ICE users (and certainly
-the development team!) have experienced improvements in software
-development activities because of the tools that ICE provides or learned
+deploy new simulation environments for their research problems (e.g., the binder jet
+modeler and reflectivity tools mentioned earlier). Other tools created
+with ICE may not invent something radically new, but they tend to
+streamline interactions with those tools. Many ICE users, and certainly
+the development team, have experienced improvements in their software
+development efforts because of the tools that ICE provides or have learned
 new technologies because access to new tooling was as simple as
@@
 
-A new cloud based development tool based on ICE is under development by
-RNET LLC out of Dayton, Ohio in response to an SBIR award from the U.S.
-Department of Energy. This web based version of ICE will continue ICE's
-support for nuclear energy and integrate with cloud services such as
-Amazon Web Services and Oak Ridge National Laboratory's Compute and Data
-Environment for Science (CADES). Additionally, while ICE has not led to
-the development of ``spin-off'' companies, ICE source code has been used
-in two spin-off projects: EAVP (mentioned earlier) for advanced
-visualizations and the Eclipse January project for scientific data
-structures, \cite{graham_eclipse_2016}. ICE was also one of the founding
+A new cloud-based development tool based on ICE is under development by
+RNET Technologies, Inc. out of Dayton, Ohio in response to a Small Business Innovation 
+Research award from the US Department of Energy. This web-based version of 
+ICE will continue ICE's support for nuclear energy and will integrate with cloud 
+computing solutions like Amazon Web Services and ORNL's Compute and Data
+Environment for Science (CADES). Additionally, while ICE has not directly led to
+any ``spin-off'' companies, ICE source code has been used
+in two spin-off projects: (1) EAVP (mentioned earlier) for advanced
+visualizations and (2) the Eclipse January project for scientific data
+structures \cite{graham_eclipse_2016}. ICE was also one of the founding
 projects of the Eclipse Science Working Group.
 
-Eclipse ICE is an open source project and the authors welcome and encourage
-engagement and contributions from readers. Interested parties may inquire by
-contacting the corresponding author or visiting the website.
+Eclipse ICE is an open-source project, and the authors welcome and encourage
+engagement and contributions from users. Interested parties may inquire by
+contacting the corresponding author or visiting the ICE website.
 
-\section{Sample Code, Tutorials and Other
+\section{Sample Code, Tutorials, and Other
 Resources}\label{sample-code-tutorials-and-other-resources}
 
-The quintessential resource for information on ICE is the projects web
-page, \cite{billings_eclipse_2016}. The ``Resources'' menu includes links to
-detailed tutorials and documentation of multiple types. Examples of how to create
+The primary resource for information on ICE is the project's 
+website~\cite{billings_eclipse_2016}. The ``Resources'' menu includes links to
+detailed tutorials and user documentation. Examples of how to create
 new workflow Items are available at
 \url{https://github.com/eclipse/ice/tree/master/org.eclipse.ice.demo}.
-Examples of how to use the scripting engine (in this case for neutron
-reflectivity) are available at
-\url{https://github.com/eclipse/ice/tree/master/examples}. ICE includes an
-extensive test suite of unit, integration, and UI tests and these are
+Examples of how to use the scripting engine are available at
+\url{https://github.com/eclipse/ice/tree/master/examples}. ICE also includes an
+extensive suite of unit, integration, and UI tests, which are
 also excellent examples of how to work with the platform.
@@
 
-Workflows for computational scientists in modeling and simulation differ
-greatly from experimentalists or those who primarily interact with
-grid-based workflow management systems. This work presented the Eclipse
-Integrated Computational Environment (ICE) and described how it has
-been used to address interdisciplinary problems in modeling and
-simulation for energy science. One interesting avenue for future
-exploration is coupling or integrating ICE with other workflow tools
-such as Aiida, Triquetrum, Kepler and Pegasus. It remains as abundantly
-clear now as it was in Mandal's 2007 paper that the best of all workflow
-management tools will be needed to address high-performance computing
-problems at the exascale and beyond.
+Modeling and simulation workflows for computational scientists differ
+greatly from those of experimentalists or those who primarily interact with
+grid-based workflow management systems. The Eclipse ICE effort described here 
+has been used to address interdisciplinary problems in 
+modeling and simulation for energy science. Of particular interest are the
+differences in architecture between a workflow management system focused
+on modeling and simulation compared to those focused on grids. ICE's broad
+applicability across many topics in energy science suggests that
+there are opportunities for these systems in general. Finally, one 
+interesting avenue of future exploration is coupling or integrating ICE 
+with other workflow tools such as Aiida, Triquetrum, Kepler, and Pegasus,
+which would make it possible to combine the best of grid and modeling and
+simulation workflows to address greater challenges.
 
-\section*{Acknowledgements}\label{acknowledgements}
-\addcontentsline{toc}{section}{Acknowledgements}
+\section*{Acknowledgments}\label{acknowledgments}
+\addcontentsline{toc}{section}{Acknowledgments}
 
 The authors are grateful for the assistance and support of the following
-people and institutions without which this work would not have been
+people and institutions without whom this work would not have been
 possible. This includes many people who directly contributed to the
@@
 Lyon, Tony McCrary, John M. Hetrick III, Elizabeth Piersall, Neeti
-Pokhriyal, Adrian Sanchez, Claire Saunders, Nick Stanish, Matthew Wang,
-Scott Wittenberg. The support of both the NEAMS and CASL programs is
+Pokhriyal, Adrian Sanchez, Claire Saunders, Nick Stanish, Matthew Wang, and
+Scott Wittenberg. The support of both the NEAMS and CASL programs is also
 greatly appreciated. The authors would like to acknowledge the special
 contribution of the Eclipse Foundation, the Eclipse Community, the
-Eclipse Science Working Group and our many colleagues who use and
-contribute to open source projects in the Eclipse ecosystem.
+Eclipse Science Working Group, and our many colleagues who use and
+contribute to open-source projects in the Eclipse ecosystem.
 
 Finally, the development team is especially grateful to Barney Maccabe,
-David Pointer and John Turner of Oak Ridge National Laboratory for their
+David Pointer, and John Turner of ORNL for their
 endless support and advocacy for this work.
@@
 the Oak Ridge Institute for Science and Education (ORISE). This work was
-also supported in part by the Oak Ridge National Laboratory Director's
+also supported in part by the ORNL Director's
 Research and Development Fund. ORNL is managed by UT-Battelle, LLC, for
@@
 
-\section*{Current code version}\label{current-code-version}
+\section*{Current Code Version}\label{current-code-version}
 \addcontentsline{toc}{section}{Current code version}
@@
 
-\begin{table*}[!htbp]
+\begin{table}[H]
 \begin{tabularx}{\textwidth}{|l|X|X|}
 \hline
-C1 & Current Code Version & `next'\tabularnewline\hline
+C1 & Current code version & `next'\tabularnewline\hline
 C2 & Permanent link to code/repository used for this code version &
@@
 \tabularnewline\hline
-C3 & Legal Code License & Eclipse Public License 1.0 \tabularnewline\hline
-C4 & Code versioning system use & Git \tabularnewline\hline
-C5 & Software code languages, tools, and services used & Java, OSGi, Eclipse Rich Client Platform,
+C3 & Legal code license & Eclipse public license 1.0 \tabularnewline\hline
+C4 & Code versioning system used & Git \tabularnewline\hline
+C5 & Software code languages, tools, and services used & Java, OSGi, Eclipse RCP,
 and Maven \tabularnewline\hline
-C6 & Compilation requirements, operating environments \& dependencies & Java 1.8 or greater, Maven, and
+C6 & Compilation requirements, operating environments and dependencies & Java 1.8 or greater, Maven, and
 an internet connection for dependencies \tabularnewline\hline 
-C7 & If available Link to developer documentation/manual &
+C7 & If available, link to developer documentation/manual &
 \url{https://wiki.eclipse.org/ICE} \tabularnewline\hline 
@@
 \label{codeTable}
-\end{table*}
+\end{table}
 
-\section*{Current executable software
-version}\label{current-executable-software-version}
-\addcontentsline{toc}{section}{Current executable software version}
+\section*{Current Executable Software
+Version}\label{current-executable-software-version}
+\addcontentsline{toc}{section}{Current Executable Software Version}
 
@@
 
-\begin{table*}[!htbp]
+\begin{table}[H]
 \begin{tabularx}{\textwidth}{|l|X|X|}
 \hline
-S1 & Current Code Version & 2.2.1 \tabularnewline\hline
-S2 & ermanent link to executables of this version &
+S1 & Current code version & 2.2.1 \tabularnewline\hline
+S2 & Permanent link to executables of this version &
 \url{https://www.eclipse.org/downloads/download.php?file=/ice/builds/2.2.1/}
  \tabularnewline\hline 
-S3 & Legal Software License & Eclipse Public License 1.0 \tabularnewline\hline
-S4 & Computing platforms/Operating Systems & Windows (32/64-bit), Mac OS/X,
+S3 & Legal software license & Eclipse public license 1.0 \tabularnewline\hline
+S4 & Computing platforms/operating systems & Windows (32/64-bit), Mac OS/X,
 Linux (32/64-bit) \tabularnewline\hline 
-S5 & Installation requirements \& dependencies & Java 1.8 or
+S5 & Installation requirements and dependencies & Java 1.8 or
 greater \tabularnewline\hline
-S6 & If available, link to user manual - if formally published include a
+S6 & If available, link to user manual. If formally published, include a
 reference to the publication in the reference list &
@@
 \label{execTable}
-\end{table*}
+\end{table}

### 2017-05-30 src/main.tex
Fixed keywords. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>
Pushing changes from Sam's edits. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 \usepackage{booktabs}
+\usepackage{float}
 \usepackage[hyphens]{url}
@@
 management systems. Computational scientists typically interact with
-simulation software in a feedback driven way where solutions and
+simulation software in a feedback-driven way where solutions and
 workflows are developed iteratively and simultaneously. This work
@@
 Examples of the Environment's applicability to problems in energy
-science, general multiphysics simulations, quantum computing and other
-areas are presented as well as its impact on the community.
+science, general multiphysics simulations, quantum computing, and other
+areas are presented along with its impact on the community at large.
 
@@
 \begin{keyword}
+workflows
 \sep 
+workflow management
 \sep
 supercomputing
+\sep
+usability
+\sep
+eclipse
 

### 2017-05-30 src/content.tex
Synced additional changes from Sam. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 
-In previous work, Billings et al. interviewed simulation and modeling 
-software users to compile a list of requirements for implementing and 
+In previous work, Billings et al. interviewed modeling and simulation subject matter experts to compile a list of requirements for implementing and 
 using these kinds of applications. In the process, they discovered 
@@
 
-This section concludes with an introduction of the workflow model addressed by
-ICE. Section \ref{software-description} details the software
+This section concludes with an introduction of the ICE workflow model. Section \ref{software-description} details the software
 from an architectural perspective, while Section \ref{illustrative-examples}
@@
 IWorkflow, IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's
-API language closer to other systems. This must be done with care to
-satisfy backwards compatibility requirements on the present API.}
+API language closer to other systems. This must be done carefully to
+preserve backwards compatibility with the present API.}
 
@@
 simplifies the way the Core manages and interacts with Items. Second, by
-formalizing state and error checks, it explicitly delineates which workflows 
+formalizing state and error checks, ICE explicitly delineates which workflows 
 can be executed from those that must receive additional configuration. 
@@
 \includegraphics[width=\textwidth]{images/jaded.png}
-\caption{ICE workbench in JADE for quantum computing simulations.}
+\caption{ICE workbench in the Jade Adiabatic Development Environment (JADE) for quantum computing simulations.}
 \end{figure}
@@
 with other workflow tools such as Aiida, Triquetrum, Kepler, and Pegasus,
-which would make it possible to combine the best of grid and modeling and
+which would make it possible to combine the best of grid and modeling workflows and
 simulation workflows to address greater challenges.
@@
 Pokhriyal, Adrian Sanchez, Claire Saunders, Nick Stanish, Matthew Wang, and
-Scott Wittenberg. The support of both the NEAMS and CASL programs is also
+Scott Wittenberg. The support of both the Nucleare Energy Advanced Modeling and Simulation (NEAMS) and Consortium for Simulation of Light-water Reactors (CASL) programs is also
 greatly appreciated. The authors would like to acknowledge the special

### 2017-06-11 src/content.tex
Added changes suggested by Geoffroy Vallee and Norbert Podhorski after internal ORNL review. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
   including virtual battery simulations and additive manufacturing, 
-  among others (see ``Illlustrative Examples'').
+  among others (see ``Illustrative Examples'').
 \end{itemize}
@@
 acceptable where the workflow is static and does not require additional
-human input or ``human in the loop'' behavior after the all the initial
+human input or ``human in the loop'' behavior after all the initial
 human input is provided. That is, a ``process-oriented'' definition is
@@
 
-VIBE 1.0 is available as a virtual machine in which the simulation
+VIBE 1.0 is available as a virtual machine (for convenient deployment) in which the simulation
 software and ICE are provided side by side. The VIBE team's more recent 
@@
 and MOOSE to quickly solve energy science problems with HPC resources 
-and to deploy domain-specific workbenches. ICE includes
-support for automatically downloading and building MOOSE from MOOSE's GitHub
+and to deploy domain-specific workbenches.
+ICE provides features for automatic installation, configuration and optimization of scientific development environments.
+In the context of MOOSE, ICE includes support for automatically downloading and building MOOSE from MOOSE's GitHub
 repository. This integration enables users to immediately begin developing
@@
 extensive suite of unit, integration, and UI tests, which are
-also excellent examples of how to work with the platform.
+also excellent examples of how to work with the platform. Tutorial and demonstration videos are available on YouTube at \url{https://goo.gl/nxCzRD}.
 

### 2018-07-10 src/content.tex
Fixed typos and errors in the references. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 
-Previous efforts to address these five issues have resulted in general
-purpose scientific workflow tools like Kepler \cite{ludascher_scientific_2006} 
-or myopic tools that only satisfy a single
+Previous efforts to address these five issues have resulted in general-purpose scientific workflow tools like Kepler \cite{ludascher_scientific_2006} 
+or myopic tools that satisfy only a single
 set of requirements for a single piece of software or a single platform. These
@@
 \item
-  Modeling and simulation activities can be described in a succinct
-  workflow model (see ``Workflow Model'').
+  modeling and simulation activities can be described in a succinct
+  workflow model (see ``Workflow Model'');
 \item
-  An architecture for such a workflow system can satisfy the model of
-  workflows in an extensible way (see ``Software Architecture'').
+  an architecture for such a workflow system can satisfy the model of
+  workflows in an extensible way (see ``Software Architecture''); and 
 \item
-  Such a system is applicable to a suite of problems in energy science,
+  such a system is applicable to a suite of problems in energy science,
   including virtual battery simulations and additive manufacturing, 
@@
 
-This section concludes with an introduction of the ICE workflow model. Section \ref{software-description} details the software
-from an architectural perspective, while Section \ref{illustrative-examples}
+This section concludes with an introduction to the ICE workflow model. Section \ref{software-description} details the software
+from an architectural perspective, and Section \ref{illustrative-examples}
 provides a set of comprehensive examples. A
-presentation of the impact is included in Section \ref{impact}, and sample 
-code is provided in Section \ref{sample-code-tutorials-and-other-resources}.
+presentation of the impact is included in Section \ref{impact}, and details on obtaining sample 
+code are provided in Section \ref{sample-code-tutorials-and-other-resources}.
 
@@
 modify existing input or create new input from a template. ``Input''
-generally includes runtime parameters for the simulation framework
+generally includes run time parameters for the simulation framework
 (e.g., tolerances); configuration options (e.g., data locations, output
@@
 the process of performing calculations using a simulation code or
-framework based on known variables---the input. Models and simulation
-codes are typically run locally for small jobs or for development. Large
+framework based on known variables from the input. These are typically run locally for small jobs or for development. Large
 simulations, on the other hand, typically require a large amount of
-hardware resources; these resources are usually off site (i.e.,
+hardware resources. These resources are usually off-site (i.e.,
 physically unavailable to the user) and are accessed remotely
@@
 Local and remote jobs are often monitored to ascertain a job's status.
-This monitoring may be a simple check as to whether or not the execution
-has completed, or it may involve monitoring the output of individual
+This monitoring could be a simple check as to whether or not the execution
+has completed, or it could involve monitoring the output of individual
 quantities to examine the calculation state. The latter is often used to
@@
 data in one or more prescribed ways and producing artifacts with
-scientific significance from the transformed data. This may include, for
-example, post-processing results and visualizing the new data with
+scientific significance from the transformed data. This could include, for
+example, postprocessing results and visualizing the new data with
 dedicated visualization tools. For many types of scientific computing,
@@
 extracting publication-quality images or movies from that data. Other
-cases may include analyzing results in preparation for follow-on
+cases might include analyzing results in preparation for follow-on
 simulations or performing feature extraction, classification, or
@@
 
-While this has many similarities to executing a job, it is distinctly
+Although this is similar to executing a job, it is distinctly
 different because the activity changes focus to satisfy the needs of a
@@
 known, certainly qualifies as executing a job; however, analysis of
-model and simulation results is far from simple data reduction and is
+modeling and simulation results is far from simple data reduction and is
 generally far more interactive for computational scientists.
@@
 generating new input, or analyzing results. Examples include archiving
-data, packaging data for publications, and updating values manually
-(often in light of new information from publications).
+data, packaging data for publications, and updating values manually or through scripts (often in light of new information from publications).
 
@@
 scientific computing workflow. However, modeling and simulation use
-cases often require users to explicitly modify code before execution,
-such as with the computational fluid dynamics code Nek5000,
-\cite{the_nek5000_team_nek5000_2014}, or to issue special re-build instructions.
+cases often require users to explicitly modify code before execution or to issue special re-build instructions.
+This is true, for example, with the computational fluid dynamics code Nek5000 which requires modification of code before compilation and special build instructions using the \textit{makenek} shell script,
+\cite{the_nek5000_team_nek5000_2014},
 Many computational scientists consider ``their workflow'' to be re-running
-software after modifications for purely exploratory purposes. This may
-be required if the model that the author is manipulating cannot be
-configured directly as part of the input but can be easily manipulated
-by hand.
+software after modifications for purely exploratory purposes. This might
+be required if the model that the author is modifying cannot be
+configured directly as part of the input but can be easily accomplished by manipulating the source code.
 
@@
 human input or ``human in the loop'' behavior after all the initial
-human input is provided. That is, a ``process-oriented'' definition is
-acceptable where all human input is provided in advance. However,
-workflows within ICE are fully interactive with regular call-backs to
-humans. It is simpler to discuss ``activities'' than it is to create a
+human input is provided. However, workflows within ICE are fully interactive with regular callbacks to humans. It is simpler to discuss ``activities'' than it is to create a
 distinction between ``human processes'' and ``computer processes.''
 Focusing on ``activities'' over processes (human or computer) also has
-the benefit of removing concrete elements such as hardware properties or
-software details that distract from details of workflows and workflow 
+the benefit of removing concrete elements such as hardware or software properties that distract from details of workflows and workflow 
 management systems. That is, considerations such as memory usage and 
 raw performance are important, but questions about the abstract workflow 
-or what the workflow management system should do are far more important.
+or what the workflow management system should do are far more important in this context.
 
@@
 
-ICE was specifically created to address the workflow model described
-above, which is to say that it was created specifically to address
-hands-on workflows for computational scientists. Users download and
-execute ICE locally and it orchestrates workflows locally or remotely as
+ICE was specifically created to address hands-on workflows for computational scientists, as in section \ref{illustrative-examples}. Users download and
+execute ICE locally, and ICE in turn orchestrates local or remote workflows as
 required. It provides a comprehensive workbench for modeling and
@@
 the ``ICE Core,'' which acts as a server. This information is
-provided dynamically because the information often changes at run time based on 
+provided dynamically because it often changes at run time based on 
 both the configuration of available workflow components in the registry and on
@@
 specific details, the Client dispatches a request to the Core to modify
-or process the workflow. The Core then uses the information from the Form
-to perform a service lookup for \emph{what} should process the workflow.
+and/or process the workflow. The Core then uses the information from the Form
+to perform a service lookup to identify the correct service to process the workflow.
 
-Workflows in ICE are encoded in and processed by ``Items'' and each
-workflow type is a subclass of Item. Items are registered dynamically
+Workflows in ICE are encoded in and processed by services called ``Items,'' and each
+workflow type is a subclass of an Item base class. Items are registered dynamically
 through a service registry in ICE (see Section \ref{framework}) and
@@
 Item or provided as ``Actions'' that are dynamically registered with
-an ``Action Factory'' and obtained at runtime. Table 1 describes the
+an ``Action Factory'' and obtained at run time. Table 1 describes the
 differences between Items, Actions, and Forms.\footnote{An upcoming 
@@
 IWorkflow, IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's
-API language closer to other systems. This must be done carefully to
+API language closer to other systems. However, this must be done carefully to
 preserve backwards compatibility with the present API.}
@@
 Forms to disk in a special directory called a ``workspace.''
-Workspaces can contain projects, folders, and files; including data,
+Workspaces can contain projects, folders, and files, including data,
 code, input, and output. ICE automatically manages local and remote (or
@@
 Likewise, if the output is small enough, ICE will automatically move it back
-to local directory. By convention, all paths in ICE's Forms are
+to the local directory. By convention, all paths in ICE's Forms are
 relative to the workspace root path. Workspace directories are specified
-by the user.
+by the user and are fully functional Eclipse workspaces.
 
@@
 could replace the XML-based provider since it is registered as a dynamic 
-service, and a JAX-P based provider has been used in the past.
+service and a JAX-P based provider has been used in the past.
 
@@
 ICE is an Eclipse Rich Client Platform (RCP) application
-\cite{mcaffer_eclipse_2010}, and has a plugin architecture based on 
+\cite{mcaffer_eclipse_2010} and has a plugin architecture based on 
 Equinox, which is the reference implementation of the Open Service Gateway Initiative (OSGi) 
-framework specification \cite{mcaffer_osgi_2010}. ICE uses over 1,200 additional
+framework specification \cite{mcaffer_osgi_2010}. ICE uses more than 1,200 additional
 packages from the Eclipse ecosystem to provide services like language
@@
 they provide their own plugin to the framework---users can
-only use the workflow Items provided by their version of ICE. This can seem like an
-onerous task to the novice user, especially if they do not know Java, but
+use only the workflow Items provided by their version of ICE. This extension method can seem like an onerous task to the novice user, especially if they do not know Java, but
 this design was chosen because it is, in the opinion of the authors, a
@@
 
-ICE provides built-in development tools to automatically generate ``stubs'' of
-plugins that can then be installed into the framework. This
+ICE provides built-in development tools to automatically generate empty but ready to compile classes, (``stubs''), of
+plugins that can then be installed into the framework as services. This
 ``self-hosting'' makes it possible for new users to create complex,
@@
 know how to interact with the framework. Furthermore, ICE provides a
-rich API, documentation, tutorials, and tools to further simplify the
-process.
+rich API that that exposes all workflow management functionality, documentation, tutorials, and tools to further simplify the process.
 
@@
 unacceptable, such as when a very large number of workflows will be
-executed or the type of information required is very fine-grained. In
+executed or the type of information required is very fine grained. In
 these cases, it is often necessary to provide scripts to the workflow
@@
 
-\subsection{Software Functionalities}\label{software-functionalities}
+\subsection{Functionality}\label{software-functionalities}
 
@@
 workflow management system for computational scientists in support of
-the activities described above. In practice, it is most often used as a
+the activities described previously. In practice, it is most often used as a
 combination of workflow management system and development environment
@@
 to add multiple types of input, configure the simulation software, and launch
-simulations of virtual batteries. Interactive 3-D visualizations of the
+simulations of virtual batteries. Interactive 3D visualizations of the
 results were embedded in the launcher so that users can quickly find
@@
 
-There are over three hundred MOOSE-based applications, and it is very
-easy to create new MOOSE applications. The ICE development team uses ICE
+There are more than 300 MOOSE-based applications, and it is very
+easy to create new ones. The ICE development team uses ICE
 and MOOSE to quickly solve energy science problems with HPC resources 
 and to deploy domain-specific workbenches.
-ICE provides features for automatic installation, configuration and optimization of scientific development environments.
+ICE provides features for automatic installation, configuration, and optimization of scientific development environments.
 In the context of MOOSE, ICE includes support for automatically downloading and building MOOSE from MOOSE's GitHub
 repository. This integration enables users to immediately begin developing
-complex multiphysics applications using the pre-installed Eclipse C Development 
+complex multiphysics applications using the preinstalled Eclipse C Development 
 Tools. Once the new MOOSE-based application is built, it will automatically work with
@@
 product to shrink and warp from its original layout. An ideal, near-net-shape, 
-process combines binder jetting with solid-state sintering and accounts
+process would combine binder jetting with solid-state sintering and accounts
 for warpage and deformation in the part's design phase. 
@@
 deformation in this type of geometry is bending or drooping of the
-cantilevers, and ICE currently calls a custom MOOSE-based application
-(which was written in ICE as described above) for simulating the
-deformation of the cantilevers. The full application for this work 
-is expected to be released near the end of 2017.
+cantilevers due to sintering and thermal creep.
 
@@
 ICE also includes a small utility for simulating neutron reflectivity and
-comparing the results to other data \cite{billings_brand_2015}. This 
+comparing the results with other data \cite{billings_brand_2015}. This 
 utility was developed in collaboration with a team at ORNL's Spallation Neutron 
 Source to replace an older utility that was originally written in Visual Basic and 
-distributed via Excel macros. The new utility, developed in ICE and 
-shown in Figure 4, is capable of processing a single workflow.
+distributed via Excel macros. The new utility, developed in ICE is shown.
 
@@
 As quantum computing grows, the need for sophisticated
-software that can utilize quantum hardware or perform calculations on
+software that can use quantum hardware or perform calculations on
 simulated quantum hardware becomes more pressing. Humble et al. created a simulator for
 adiabatic quantum computers where workflows were added to ICE to support
-interaction with the simulator and to process large sets of
+interactions with the simulator and to process large sets of
 quadratic binary optimization problems \cite{humble_integrated_2014}. Figure 5
@@
 
-ICE also supports other quantum computing projects, including the
-eXtreme-scale ACCelerator (XACC) effort
-\cite{mccaskey_ornl-qci/xacc_2016}. XACC is a programming framework for
-extreme-scale, post-exascale accelerator architectures that can be
-integrated alongside existing, conventional applications.
+%ICE also supports other quantum computing projects, including the
+%eXtreme-scale ACCelerator (XACC) effort
+%\cite{mccaskey_ornl-qci/xacc_2016}. XACC is a programming framework for
+%extreme-scale, post-exascale accelerator architectures that can be
+%integrated alongside existing, conventional applications.
 
@@
 \cite{billings_domain-specific_2015}. Support for the ``Reactor
-Analyzer'' was dropped in ICE 2.1.8, but it demonstrated ICE's ability
-to integrate many different nuclear energy tools for complex analysis.
+Analyzer'' was dropped in ICE 2.1.8, but it demonstrated ICE's capability
+to integrate many different nuclear energy tools for complex analyses.
 
@@
 \cite{mandal_integrating_2007}), but the end goal of gaining the greatest
-advantage by using the best capabilities from multiple systems remains elusive.
+advantage by using the best capabilities from multiple systems remains unrealized.
 ICE's unique perspective on workflows and its well-defined API make it
@@
 \cite{mandal_integrating_2007}, is a Ptolemy-based workflow engine
-\cite{brooks_triquetrum:_2015}. Several of the authors of this paper are using
-it to investigate these issues.
+\cite{brooks_triquetrum:_2015}.
 
 It is widely known that tools that enable researchers to be more productive tend
-to improve the pursuit of existing research. The high extensibility of
+to improve the pursuit of new research. The high extensibility of
 ICE and the tools that it combines from the larger Eclipse ecosystem
 have made it possible for researchers on the development team to quickly
-deploy new simulation environments for their research problems (e.g., the binder jet
-modeler and reflectivity tools mentioned earlier). Other tools created
-with ICE may not invent something radically new, but they tend to
+deploy new simulation environments for their research problems. Other tools created
+with ICE might not invent something radically new, but they tend to
 streamline interactions with those tools. Many ICE users, and certainly
@@
 sources such as the VIBE mailing list, ICE's own mailing lists, and
-website download statistics suggest that ICE has been used by over 350
-people at one time or another and currently has about twenty
+website download statistics suggest that ICE has been used by more than 350
+people at one time or another and currently has about 20
 ``superusers,'' including the development team.
@@
 A new cloud-based development tool based on ICE is under development by
-RNET Technologies, Inc. out of Dayton, Ohio in response to a Small Business Innovation 
+RNET Technologies, Inc., out of Dayton, Ohio, in response to a Small Business Innovation 
 Research award from the US Department of Energy. This web-based version of 
@@
 
-The primary resource for information on ICE is the project's 
+The primary resource for information on ICE is the project 
 website~\cite{billings_eclipse_2016}. The ``Resources'' menu includes links to
@@
 differences in architecture between a workflow management system focused
-on modeling and simulation compared to those focused on grids. ICE's broad
+on modeling and simulation compared with those focused on grids. ICE's broad
 applicability across many topics in energy science suggests that
@@
 project, either in its early days as ``NiCE'' or once it moved to
-Eclipse, including: Ronald Allen, Andrew Belt, Tim Bohn, David E.
-Bernholdt, Erica Grant, Mike Guidry, Forest Hull, Eric J. Lingerfelt,
-Sebastien Jourdain, JiSoo Kim, Allison Koenecke, Fangzhou Lin, Greg
-Lyon, Tony McCrary, John M. Hetrick III, Elizabeth Piersall, Neeti
+Eclipse, including Ronald Allen, Andrew Belt, David E.
+Bernholdt, Tim Bohn, Erica Grant, Mike Guidry, John M. Hetrick III, Forest Hull, 
+Sebastien Jourdain, JiSoo Kim, Allison Koenecke, Fangzhou Lin, Eric J. Lingerfelt, Greg
+Lyon, Tony McCrary, Elizabeth Piersall, Neeti
 Pokhriyal, Adrian Sanchez, Claire Saunders, Nick Stanish, Matthew Wang, and
-Scott Wittenberg. The support of both the Nucleare Energy Advanced Modeling and Simulation (NEAMS) and Consortium for Simulation of Light-water Reactors (CASL) programs is also
+Scott Wittenberg. The support of both the Nuclear Energy Advanced Modeling and Simulation (NEAMS) and Consortium for Simulation of Light-water Reactors (CASL) programs is also
 greatly appreciated. The authors would like to acknowledge the special

### 2018-07-12 src/review-response-20180712.tex
Addressed all reviews and finished grammatical edits. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

Dear Dr. Sobie,

Thank you very much for providing the reviewer's responses. Please find below a list of the issues that we have addressed and comments on the reviewer's responses. We found these reviews to be highly constructive and made every effort to address the reviews as thoroughly as possible.

We have resubmitted the manuscript and hope that you will reconsider it for publication in Software X.

Best,
Jay Jay Billings
ORNL

-----
Reviewer #1

>> It seems that comparison to other models could be improved and the authors could have listed features that provided by ICE that are either missing in other workflow models or are efficient compare, other models. Perhaps this section can be re-named as background or related work. Also, it was a little surprise that authors did not mention provenance which is one of the import features expected or desired by the scientific community.

We have expanded this section and addressed unique features and the comparison of ICE to other workflow engines with activities-based workflow models.

>> 
>> To summarize, the review,  the work seems interesting and useful to the community. The writing could be improved, below is the list of suggestions:
>> 
>> 1) A figure of some sort on complete architecture is extremely desired.

We have added four pictures and expanded the software architecture section to better describe ICE's architecture.

>> 
>> 2) Some of the references need to be looked up carefully. For instance reference 23 and 24 seem incomplete and less useful for a reader. See below:
>> 
>> [24] Jay Jay Billings. Eclipse ICE, October 2016.
>>

Five erroneous web citations were addressed.

>> 3) Renaming
>> Comparison to other models seems incomplete. Perhaps it could be renamed to something better such as "related work."
>>

Done.

>> 4) It is not very clear exactly how ICE integrate code from other languages. A reference to EASE was given but no other detail was provided.

We have added text to clarify that this is done by simple scripts in Javascript and Python through a built in shell, through workflow items, and in extreme cases through the Java Native Interface.

>> -----
>> Reviewer #2: This manuscript describes the Eclipse Integrated Computational Environment (ICE, https://www.eclipse.org/ice/), a scientific workbench and workflow environment for the execution and analysis of computational simulations. ICE adopts an alternative approach to typical workflow systems, which consists of defining analysis and computational processes into activities, as well as the support for workflow steering. Overall, the system has a proof community and relies in a well-established IDE (Eclipse), which increases its adoption by the community. This manuscript provides general concepts of the ICE system and illustrative examples, however lacks detailed information about the system architecture and execution environments. Additionally, related work is not comprehensive.

>> Detailed comments:
>> - Related work should be carefully revised, and include popular workflow system such as Swift, Pegasus, Makeflow, Taverna, Askalon, Nextflow, etc. (only Kepler is shown as an example). The manuscript claims that ICE follows the five categories described in the motivation section, however it is not the only workflow system that follows this classification.

The purpose of this work is not to extensively compare ICE to other workflow engines,

We do not believe that a detailed, n-by-n comparison of workflow systems is valuable in the context of a software publication on ICE, but we agree that it is important to illustrate the differences a little better. To that end, the text now discusses Chiron, Taverna, Aiida, and Fireworks. We have also added a reference to other work by the authors that describes the differences between modeling and simulation workflows and grid workflows in more detail.

>> The same issue appears again in Section 2.0.2 (section number should be revised too), where the presented model is claimed to significantly differ from similar efforts in workflow science. This is not accurate, there are several workflow systems that follows the activities model, such as Moteur, Taverna, and Chiron. It is crucial to distinguish ICE's contributions from these systems.

Taverna and Chiron are now discussed in the related work section. The exact differences between their Activities and ICE's are presented.

>> Last, interactive analysis of workflow executions is claimed as a novelty of this work; however workflow steering has been investigated by over a decade and support in systems such as Chiron and SciCumulus. How ICE differs from them?

Our paper only points out that ICE can perform this work and does not, as far as we can tell, claim that ICE uniquely provides this capability.

>> 
>> - Section 3, software description needs to be substantially improved. It misses an overview architecture (a figure would be extremely helpful) that shows how ICE components interact/leverage Eclipse components. This is one of the main contributions of this paper and should be better articulated.

We have addressed this point by adding new diagrams and more text describing the architecture of ICE. We have also added more information on the relationship to Eclipse Equinox, RCP, and PTP, etc. and cleaned up the sections that describe Eclipse across the document.

>> Several definitions are looseness:
>> + How the Items model differs from Taverna's model with Web Services?

Taverna's web services are now discussed specifically in the related work section, but since they are not similar to ICE's Items the relationship is not addressed. Shim services are now discussed briefly as well.

>> + There is a mention that ICE API will be evolved to make the API language closer to other systems. Which systems and how?

This is a generic statement about the names of classes and methods in other systems compared to the language used to describe these in ICE. For example, Item's in ICE are typically called tasks in Kepler-based systems such as Triquetrum.

The footnote has been changed to reflect this by adding "such as Triquetrum" after "other system" to provide an example.

>> + What defines a small output (so it will be automatically transferred)?

50MB. This has been updated in the text.

>> + Why is it more sophisticated? What can be achieved here? It is important to enumerate the advantages.

We have updated the text in this section to more clearly reflect our thinking on language-based workflows in ICE.

>> + What is a 'stubs' of plugins? How will it then interact with the framework? Which capabilities are used to enable them with ICE?

Updated the text to define stubs, strengthen the related statement on installation, and to describe the role of the OSGi in this process.

>> + Which operations are available via the APIs? It is mentioned that it has a rich API, but no detailed information is provided.

Detailed information is provided in the API documentation, which is cited in the final section. However, we strengthened this sentence by adding text that all workflow management functions are exposed by the API.

>> 
>> - IMHO, one of the main contributions and novelty of the paper is the combination of the Eclipse IDE with the workflow development/execution capabilities. However, it is not discussed in detail how a user may benefit from this integration.

This point has been addressed by creating a section specifically on the relationship to Eclipse out of content from the old framework extension section and new information on the benefits of self-hosting.

>> 
>> - The examples section would significantly benefit of more information about how the workflows are executed.

All workflows in ICE are executed as described in the executing jobs sub section.

>> 
>> - Also, there are mentions that ICE can run locally and in HPC platforms, but no information is provided on how the system actually executes the workflows. There is a quick mention to SSH connections, but nowadays there are other methods to remotely submit jobs for execution, such as Globus GRAM, Bosco, etc. The manuscript needs a proper workflow execution section which describes the different methods how the workflows can be executed.

The executing jobs section completely covers how workflows are executed in ICE. We have modified it to state that Globus GRAM, etc. are not supported. We have also provided some text to clarify that executing jobs is not the same as executing a workflow.

>> 
>> In summary, I see much potential in the proposed workflow tool, however a thoroughly characterization and description of the architectural components and their capabilities is key to demonstrate the novelty and impact of the discussed system.

We are very grateful for this thorough review of the paper. We believe that we have addressed this review just as thoroughly with the significant updates provided in this revised manuscript.

Also tightened up text significantly.

>> 
>> ******************************************
>> Please note that the editorial process varies considerably from journal to journal. To view the submission-to-publication lifecycle, click here: http://help.elsevier.com/app/answers/detail/p/7923/a_id/160
>> 
>> For further assistance, please visit our customer support site at http://help.elsevier.com/app/answers/list/p/7923. Here you can search for solutions on a range of topics, find answers to frequently asked questions and learn more about EES via interactive tutorials. You will also find our 24/7 support contact details should you need any further assistance from one of our customer support representatives.

### 2018-07-12 src/content.tex
Addressed all reviews and finished grammatical edits. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 that it is possible to create such a system. Specifically, the work
-described here shows that:
+described here shows that
 
@@
 
-\subsubsection{Workflow Model}\label{workflow-model}
+\subsection{Workflow Model}\label{workflow-model}
 
@@
 
+Local jobs in ICE are executed using standard Java system calls.
+Remote jobs are launched only through SSH connections on remote machines.
+This includes direct SSH command execution on clusters and proxy connections through a pilot service on large Leadership-class supercomputers.
+Services such as Globus GRAM and Bosco are not supported, but the SSH command execution includes extensive support for numerous batch and queuing systems.
+The Eclipse Parallel Tools Platform (PTP) is used to create all remote SSH connections, regardless of the target machine \cite{tibbitts_integrated_2009}.
+
 In this work, it should be assumed---unless otherwise noted---that
@@
 possibly including real-time updates to visualizations.
+It is also important to note that executing a job is not the same as executing a workflow.
+Executing jobs specifically refers to launching simulations, whereas executing a workflow could be something different such as generating input or post-processing results.
+This is an important distinction because ICE's workflows are all executed locally, but simulations and work may be distributed remotely depending on the implementation of the workflow plugin.
 
@@
 scientific significance from the transformed data. This could include, for
-example, postprocessing results and visualizing the new data with
+example, post-processing results and visualizing the new data with
 dedicated visualization tools. For many types of scientific computing,
@@
 cases often require users to explicitly modify code before execution or to issue special re-build instructions.
-This is true, for example, with the computational fluid dynamics code Nek5000 which requires modification of code before compilation and special build instructions using the \textit{makenek} shell script,
-\cite{the_nek5000_team_nek5000_2014},
+This is true, for example, with the computational fluid dynamics code Nek5000, which requires modification of code before compilation and special build instructions using the \textit{makenek} shell script
+\cite{the_nek5000_team_nek5000_2014}.
 Many computational scientists consider ``their workflow'' to be re-running
@@
 
-\subsubsection{Comparison to Other
-Models}\label{comparison-to-other-models}
+\subsection{Related Work}\label{comparison-to-other-models}
 
-This model of workflows differs significantly from those of similar
-efforts in workflow science because it defines workflows in terms of
-activities. Other workflow models in the literature define a workflow as
+ICE's model of workflows differs significantly from many other
+efforts in workflow science because it defines workflows in terms of high-level activities that are meant to guide workflow implementers and users.
+Many other workflow models in the literature define a workflow as
 a collection of computing processes. For example, Yu and Buyya define
@@
 distributed resources in a well-defined order to accomplish a specific
-goal,'' \cite{yu_taxonomy_2005}. Others, such as Pizzi et al., subscribe to
+goal'' \cite{yu_taxonomy_2005}. Others, such as Pizzi et al., subscribe to
 similar definitions \cite{pizzi_aiida:_2016}. This ``process'' view is
@@
 human input or ``human in the loop'' behavior after all the initial
-human input is provided. However, workflows within ICE are fully interactive with regular callbacks to humans. It is simpler to discuss ``activities'' than it is to create a
-distinction between ``human processes'' and ``computer processes.''
+human input is provided.
+However, workflows within ICE are fully interactive with regular callbacks to humans.
+It is simpler to discuss ``activities'' than it is to create a distinction between ``human processes'' and ``computer processes.''
 Focusing on ``activities'' over processes (human or computer) also has
@@
 
+There are other workflow engines that have their own concepts of activities, with various similarities and differences compared to ICE's model.
+For example, Taverna has a concept of activities \cite{wolstencroft_taverna_2013}.
+Activities in Taverna are defined as invocable activities within a workflow, which is closely related to a lower-level class in ICE called Actions (see \ref{item}).
+On the other hand, ICE's activities loosely describe what can be done conceptually and the workflows that are implemented provide the Actions that carry out these activities.
+
+ICE and Taverna can both natively execute Java code, but ICE 2.0 cannot natively invoke Web Service Definition Language (WSDL) web services.
+ICE uses regular Java-based libraries to interact with web services, such as Jersey, and requires that developers write the code to do this directly.
+Shim services in Taverna are provided in ICE as separate services in the framework, but are otherwise very similar.
+
+Chiron, an algebraic workflow engine, has a concept of activities that is closer to ICE's than Taverna's, but still very strongly related to implementation \cite{ogasawara_chiron_2014}.
+Activities in Chiron are combinations of the program or expression to execute, plus the input schema, plus the output schema.
+This is a close match to the design of the Item class in ICE.
+ICE's Items (see Section \ref{item}) implement the high-level activities, such as launching a job or creating a model.
+The major difference between Chiron's activities and ICE's Items appears to be scope.
+A Chiron activity such as Map or Reduce would normally be implemented as an Action in ICE, whereas an Item in ICE may be tasked with executing multiple Actions to enact a workflow.
+
+One significant difference between ICE and many other systems is that it uses a language-based approach to defining workflows, but with a standard language, Java, as opposed to a custom workflow definition language.
+Pizzi et al.
+do this with Aiida and Python, and the Fireworks Workflow Engine also uses Python.
+The advantage of this approach is that compilation is not a problem.
+ICE also differs from other workflow engines because it is specifically focused on modeling and simulation instead of grid workflows.
+Grid workflows are almost always defined as workflows based on trees without humans in the loop, but modeling and simulation workflows are much more interactive and undirected \cite{billings_toward_2017}.
+
 \section{Software Description}\label{software-description}
 
-ICE was specifically created to address hands-on workflows for computational scientists, as in section \ref{illustrative-examples}. Users download and
+ICE was specifically created to address hands-on workflows for computational scientists, as in Section \ref{illustrative-examples}. Users download and
 execute ICE locally, and ICE in turn orchestrates local or remote workflows as
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\textwidth]{src/images/ICE-arch-1.jpg}
+\caption{High-level architecture of ICE showing the relationships and rough division of responsibility between the five primary components of ICE.
+The ICE Core is responsible for the workflow management and delegations instructions and data to the Item and Data Structures, respectively.
+User input is received from the client or through headless interactions, while persistence of large amounts of data is delegated to a persistence service.}
+\label{highlevel-arch}
+\end{figure}
+
 Workflows and tasks in ICE are not explicitly treated as trees, or
@@
 \cite{yu_taxonomy_2005}. Instead, ICE's design is inspired by representational
-state transfer (REST) \cite{fielding_architectural_2000}.
+state transfer (REST) and the workflow engine is implemented as services in an Eclipse Rich Client Platform (RCP) application
+\cite{fielding_architectural_2000} \cite{mcaffer_eclipse_2010}.
 
-Users initiate requests to create, edit, update, or delete workflows from
-the ``ICE Client'' (the workbench). The list of available workflows
+Figure \ref{highlevel-arch} shows the five primary components of ICE and their relationships to each other.
+Users initiate requests to create, edit, update, or delete workflows from the ``ICE Client'' (the workbench) or through headless interactions using web or language programming interfaces.
+The list of available workflows
 that can be created is provided dynamically to the ICE Client by
-the ``ICE Core,'' which acts as a server. This information is
+the ``ICE Core,'' which acts as a server and is the primary component responsible for workflow orchestration. Workflow information is
 provided dynamically because it often changes at run time based on 
@@
 persisted workflows that users have saved in their workspace.
-Information about workflows is provided to the Client by the Core
-through stateless ``Forms'' that describe the workflow and provide
+Workflow task enactment and execution is performed by services called ``Items.'' Information about workflows is provided to the Client by the Core
+through common data structures rooted in a stateless ``Form'' tree. Forms describe the workflow and provide
 all the necessary information to understand \emph{what} should process
@@
 and/or process the workflow. The Core then uses the information from the Form
-to perform a service lookup to identify the correct service to process the workflow.
+to perform a service lookup to identify the correct Item to process the workflow.
 
-Workflows in ICE are encoded in and processed by services called ``Items,'' and each
-workflow type is a subclass of an Item base class. Items are registered dynamically
+\subsubsection{ICE Core}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\textwidth]{src/images/ICE-arch-2.jpg}
+\caption{The architecture of the ICE Core and its dependencies.
+The ICE Core class handles communications between workflow Items and common data structures, but delegates construction of workflow Items to builders.}
+\label{core-arch}
+\end{figure}
+
+The primary purpose of the ICE Core is to orchestrate workflows and services for the platform.
+Figure \ref{core-arch} shows the primary classes that interact with the ICE Core.
+It is the ``core'' control component of ICE where all other component interactions converge.
+It is the middle tier of ICE's architecture and brokers communications between Items and Clients (graphical or not) by sharing Forms that contain workflow data.
+The ICE Core class delegates construction and management of Items to the Item Manager.
+
+The Item Manager acts as a container and factory for Items created by the ICE Core.
+Items are constructed using the Builder pattern, with concrete construction handled by realizations of the ItemBuilder interface.
+
+ICE 2.0 includes a graphical client based on the Eclipse Workbench, which is common for Eclipse applications.
+The workflow management capabilities of the core can be accessed through languages and a web-based programming interface as well (see Section \ref{framework}).
+
+\subsubsection{Items}
+\label{item}
+\label{item-states}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\textwidth]{src/images/ICE-arch-3.jpg}
+\caption{The class hierarchy of ICE Items showing the relationships between the Item, its subclasses, and services that it uses.
+Vibe Launcher and MOOSE Launcher are examples of special Job Launch Items for executing jobs, and their applications are discussed in section \ref{illustrative-examples}.}
+\label{item-arch}
+\end{figure}
+
+Each workflow Item in ICE is an independent service, and each
+workflow type is a subclass of the Item base class or another Item subclass. Items are registered dynamically
 through a service registry in ICE (see Section \ref{framework}) and
-provide the Forms for the ICE Core and Client. Since ICE's design is
+provide collections of workflow data, Forms, for the ICE Core and Client. Since ICE's design is
 highly object oriented, it is easiest to think of the Item class as a
@@
 the class) as a concrete workflow with all required execution details
-provided by its Form.
+specified in its Form.
 
+Figure \ref{item-arch} shows the class hierarchy of the Item class and its collaborators.
 Individual components of workflows (i.e., workflow ``tasks'' or
@@
 Item or provided as ``Actions'' that are dynamically registered with
-an ``Action Factory'' and obtained at run time. Table 1 describes the
-differences between Items, Actions, and Forms.\footnote{An upcoming 
+an ``Action Factory'' and obtained at run time.
+Common data structures that are shared across Items, the Client, and the Core are provided by the data structures component.
+Table 1 describes the differences between Items, Actions, and Forms.\footnote{An upcoming
 update to the API will include the formal introduction of
 IWorkflow, IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's
-API language closer to other systems. However, this must be done carefully to
-preserve backwards compatibility with the present API.}
+API language closer to other systems such as Triquetrum. However, this must be done carefully to preserve backwards compatibility.}
 
@@
 
-In addition to running as a desktop workbench, ICE can be run as a
-headless web server with a remote service interface and a web
-API. The web API is also used as the primary means of providing real-time 
-feedback and monitoring support in ICE.
-
-\subsubsection{Item States}\label{item-states}
+Commonly used subclasses of Item include the Model and Job Launcher classes, which can be  used to create workflow plugins for input generation and workflow execution, respectively.
+Composite Items are special Items that are built of compositions of other Items.
+Composite Items are commonly used for workflow Items that can be executed in parallel or to tightly couple different workflow tasks for resource and performance management.
 
@@
 Finally, it allows developers implementing Items and
-Actions to specify, by contract, what is required before proceeding to the
+Actions to specify by contract what is required before proceeding to the
 next task, processing the workflow, or declaring a successful execution.
+
+\subsubsection{Data Structures}
+
+ICE contains a collection of common data structures that are useful for representing data needed modeling and simulation workflows.
+Figure \ref{data-arch} shows some of these classes and their relationship.
+All data structures (and Items) in ICE are uniquely identifiable and behave in predictable ways: they receive and dispatch updates, can be visited to determine type information, etc.
+\textit{Components} in the data sense, not the class sense, represent a special data structure that forms a child of a Form.
+Forms themselves are components and hierarchically aggregate other components.
+
+The name ``Component'' in the context of ICE's data structures refers to a unique and reusable collection of data, not a class or component in the object oriented sense.
+Components that hold data do very little of their own work but strongly scope the interfacial contract of their clients.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\textwidth]{src/images/ICE-arch-4.jpg}
+\caption{Common data structures and their relationships in ICE.}
+\label{data-arch}
+\end{figure}
 
@@
 the workflow and available in the project directory of the workspace.
-Likewise, if the output is small enough, ICE will automatically move it back
+Likewise, if the output is small enough (less than 50 megabytes), ICE will automatically move it back
 to the local directory. By convention, all paths in ICE's Forms are
@@
 
-\subsubsection{Extending the Framework to Add Custom
-Workflows}\label{framework}
+\subsubsection{Relationship to Other Eclipse Technologies}\label{framework}
 
@@
 Equinox, which is the reference implementation of the Open Service Gateway Initiative (OSGi)
-framework specification \cite{mcaffer_osgi_2010}. ICE uses more than 1,200 additional
-packages from the Eclipse ecosystem to provide services like language
+framework specification \cite{mcaffer_osgi_2010}.
+It is most appropriate to think of Eclipse ICE as an alternative flavor of any other Eclipse development environment because like those environments it is just a collection of Eclipse plugins with a well-defined purpose and brand.
+ICE uses more than 1,200 additional packages from the Eclipse ecosystem to provide services like language
 support and visualization. Each unique element of ICE described
-in this work---including the Client, Core, Items, and data structures---are 
+in this work---including the Client, Core, Items, and data structures---is 
 provided as plugins to Equinox. Most plugins are managed
-dynamically and provided as services that can be obtained through a
-service registry. Most file I/O in ICE, with only a few exceptions,
-interacts with the RCP's resources plugin. This also includes remote
-resources that are managed with the Eclipse Parallel Tools Platform
-\cite{tibbitts_integrated_2009}.
+dynamically and provided as services that can be obtained as dynamic OSGi Declarative Services. File I/O in ICE, with only a few exceptions,
+interacts with the RCP's Resources plugin and the standard Eclipse Workspace. This also includes remote resources that are managed with Eclipse PTP.
 
-It is not possible to create new Items in ICE graphically, and---unless 
-they provide their own plugin to the framework---users can
-use only the workflow Items provided by their version of ICE. This extension method can seem like an onerous task to the novice user, especially if they do not know Java, but
-this design was chosen because it is, in the opinion of the authors, a
-far more sophisticated and sustainable way to create workflows than, for example,
-using a wiring diagram.
+ICE plugins are created used normal Eclipse development tools and installed into either the running instance of ICE or published in a newly built version.
+In either case, the running platform of ICE can only use the plugins that are actually installed and at least a small amount of code must be written in Java for each plugin.
+This extension method may seem odd to the novice user or developer, especially if they do not know Java very well, but
+this design was chosen because it is an easy, fast, and precise way to create workflows.
 
-ICE provides built-in development tools to automatically generate empty but ready to compile classes, (``stubs''), of
-plugins that can then be installed into the framework as services. This
+ICE provides built-in development tools to automatically generate empty but ready to compile classes (``stubs'') of plugins that can then be installed into the framework as services.
+These tools are based on other code generation tools in the Eclipse platform.
+This
 ``self-hosting'' makes it possible for new users to create complex,
 sophisticated workflows very quickly because they are not required to
-know how to interact with the framework. Furthermore, ICE provides a
-rich API that that exposes all workflow management functionality, documentation, tutorials, and tools to further simplify the process.
+know how to interact with the framework. Development of new workflows is streamlined because ICE provides a
+rich API that exposes all workflow management functionality, documentation, tutorials, and tools to further simplify the process.
+These are shared through the self-hosted environment by code completion tools, help menus, and documentation overlays.
+The close proximity of the workflow environment with the development platform for modeling and simulation codes is also beneficial because, as a self-hosted entity, workflows can be co-developed with the code.
 
-There are many situations where configuring workflows graphically is
+ICE can be run as a headless web server with a remote service interface and a web
+API. The web API is also used as the primary means of providing real-time 
+feedback and monitoring support in ICE, and it is published as an OSGi service as well. These services can also be consumed as OSGi Remote Services.
+
+There are many situations where configuring workflows graphically or serially is
 unacceptable, such as when a very large number of workflows will be
@@
 environment by adding Items in these languages.
+Specifically, scripts in Javascript and Python are written and executed in simple shell that is part of the workbench.
+Calling other languages, such as C or Fortran, is typically accomplished by adding workflow Items for the executables in these languages and performing local workflow job launches.
+C languages routines have been called from ICE through the Java Native Interface (JNI), but this is not a technique that is widely used with the platform because of its complexity.
 
@@
 significant amount of visualization support, but at the request of users
-in the community that support was ``spun off'' in early 2016 as the 
+in the community, that support was ``spun off'' in early 2016 as the 
 Eclipse Advanced Visualization Project (EAVP)~\cite{billings_eclipse_2015}.
@@
 results were embedded in the launcher so that users can quickly find
-their results. Figure 1 shows a (simulated) prismatic-cell battery's temperature
+their results. Figure \ref{vibe} shows a (simulated) prismatic-cell battery's temperature
 distribution during discharge.
@@
 \caption{ICE workbench for VIBE analysis.}
+\label{vibe}
 \end{figure}
@@
 reproduce various aspects of MOOSE's user interface, known as ``Peacock.'' 
-Figure 2 shows an example of the ICE workbench for a simple structural mechanics
+Figure \ref{moose} shows an example of the ICE workbench for a simple structural mechanics
 problem solved using the MOOSE framework \cite{mccaskey_scientific_2015}.
@@
 \caption{ICE workbench for MOOSE workflows.}
+\label{moose}
 \end{figure}
@@
 and eliminating voids. However, this process does cause the resulting
-product to shrink and warp from its original layout. An ideal, near-net-shape, 
-process would combine binder jetting with solid-state sintering and accounts
+product to shrink and warp from its original layout. An ideal near-net-shape 
+process would combine binder jetting with solid-state sintering and account
 for warpage and deformation in the part's design phase. 
-Figure 3 shows an ICE-based workbench for performing simulations of
+Figure \ref{binder} shows an ICE-based workbench for performing simulations of
 this process with visualizations of the pre- and post-simulation
@@
 \caption{ICE workbench for binder jet modeling.}
+\label{binder}
 \end{figure}
@@
 utility was developed in collaboration with a team at ORNL's Spallation Neutron 
-Source to replace an older utility that was originally written in Visual Basic and 
-distributed via Excel macros. The new utility, developed in ICE is shown.
+Source to replace an older utility that was originally written in Visual Basic and distributed via Excel macros. The new utility, developed in ICE, is shown in Figure \ref{reflectivity}.
 
@@
 \caption{ICE workbench for neutron reflectivity.}
+\label{reflectivity}
 \end{figure}
@@
 interactions with the simulator and to process large sets of
-quadratic binary optimization problems \cite{humble_integrated_2014}. Figure 5
-shows the workbench for this project.
+quadratic binary optimization problems \cite{humble_integrated_2014}. Figure \ref{jade} shows the workbench for this project.
 
@@
 \caption{ICE workbench in the Jade Adiabatic Development Environment (JADE) for quantum computing simulations.}
+\label{jade}
 \end{figure}
@@
 Pokhriyal, Adrian Sanchez, Claire Saunders, Nick Stanish, Matthew Wang, and
-Scott Wittenberg. The support of both the Nuclear Energy Advanced Modeling and Simulation (NEAMS) and Consortium for Simulation of Light-water Reactors (CASL) programs is also
+Scott Wittenberg. The support of both the Nuclear Energy Advanced Modeling and Simulation (NEAMS) and Consortium for Simulation of Light Water Reactors (CASL) programs is also
 greatly appreciated. The authors would like to acknowledge the special
@@
 Nuclear Energy (DOE-NE) and Energy Efficiency and Renewable Energy
-(DOE-EERE), and by the ORNL Undergraduate Research Participation
+(DOE-EERE) and by the ORNL Undergraduate Research Participation
 Program, which is sponsored by ORNL and administered jointly by ORNL and

### 2018-07-12 src/main.tex
Fixed typos and errors in the references. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>
Addressed all reviews and finished grammatical edits. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 \address{$^{5}$Georgia Institute of Technology North Avenue, Atlanta, GA 30332}
-\address{$^{6}$Kichwa Coders Ltd. 1 Plomer Green Avenue Downley, High Wycombe
+\address{$^{6}$Kichwa Coders Ltd., 1 Plomer Green Avenue Downley, High Wycombe
 HP13 5LN United Kingdom}
-\address{$^{7}$Northwestern University 633 Clark Street Evanston, IL 60208}
+\address{$^{7}$Northwestern University, 633 Clark Street Evanston, IL 60208}
 \address{$^{8}$Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley,
 CA 94720}
-\address{$^{9}$Department of Computer Science, and Department of Biological
+\address{$^{9}$Department of Computer Science and Department of Biological
 Sciences, Purdue University, West Lafayette, IN 47906} 
-\address{$^{10}$Acato Information Management, LLC 114 Union Valley Rd. Oak Ridge,
+\address{$^{10}$Acato Information Management, LLC, 114 Union Valley Rd., Oak Ridge,
 TN 37830}
-\address{$^{11}$Colorado State University Fort Collins, CO 80523}
+\address{$^{11}$Colorado State University, Fort Collins, CO 80523}
 
@@
 Problems in modeling and simulation require significantly different
-workflow management technologies than standard grid-based workflow
+workflow management technologies from standard grid-based workflow
 management systems. Computational scientists typically interact with
@@
 workflows are developed iteratively and simultaneously. This work
-describes common activities in workflows and how combinations of these
+describes common modeling and simulation activities in workflows and how combinations of these
 activities form unique workflows. It presents the Eclipse Integrated
@@
 
-This manuscript has been authored by UT-Battelle, LLC under Contract No.
-DEAC05-00OR22725 with the U.S. Department of Energy. The United States
-Government retains and the publisher, by accepting the article for
-publication, acknowledges that the United States Government retains a
-nonexclusive, paid-up, irrevocable, world-wide license to publish or
-reproduce the published form of this manuscript, or allow others to do
-so, for United States Government purposes. The Department of Energy will
-provide public access to these results of federally sponsored research
-in accordance with the DOE Public Access Plan
-(http://energy.gov/downloads/doe-public-access-plan ).
+This manuscript has been authored by UT-Battelle, LLC, under contract DE-AC05-00OR22725 with the US Department of Energy (DOE).
+The US government retains and the publisher, by accepting the article for publication, acknowledges that the US government retains a nonexclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this manuscript, or allow others to do so, for US government purposes.
+DOE will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).
 

### 2018-07-12 src/review-response-20180712.tex
Added review responses. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 We found these reviews to be highly constructive and made every effort to address the reviews as thoroughly as possible.
+We believe that the result is a significantly stronger narrative.
 
@@
 Reviewer #1
-
->> It seems that comparison to other models could be improved and the authors could have listed features that provided by ICE that are either missing in other workflow models or are efficient compare, other models.
-Perhaps this section can be re-named as background or related work.
-Also, it was a little surprise that authors did not mention provenance which is one of the import features expected or desired by the scientific community.
-
-We have expanded this section and addressed unique features and the comparison of ICE to other workflow engines with activities-based workflow models.
-
->> 
->> To summarize, the review,  the work seems interesting and useful to the community. The writing could be improved, below is the list of suggestions:
->> 
 >> 1) A figure of some sort on complete architecture is extremely desired.
@@
 
->> 
 >> 2) Some of the references need to be looked up carefully. For instance reference 23 and 24 seem incomplete and less useful for a reader. See below:
@@
 >> [24] Jay Jay Billings. Eclipse ICE, October 2016.
->>
 
@@
 
->> 3) Renaming
->> Comparison to other models seems incomplete. Perhaps it could be renamed to something better such as "related work."
->>
+>> 3) Renaming Comparison to other models seems incomplete. Perhaps it could be renamed to something better such as "related work."
 
-Done.
+We have expanded this section and addressed unique features and the comparison of ICE to other workflow engines with activities-based workflow models.
 
@@
 
->> -----
->> Reviewer #2: This manuscript describes the Eclipse Integrated Computational Environment (ICE, https://www.eclipse.org/ice/), a scientific workbench and workflow environment for the execution and analysis of computational simulations.
-ICE adopts an alternative approach to typical workflow systems, which consists of defining analysis and computational processes into activities, as well as the support for workflow steering.
-Overall, the system has a proof community and relies in a well-established IDE (Eclipse), which increases its adoption by the community.
-This manuscript provides general concepts of the ICE system and illustrative examples, however lacks detailed information about the system architecture and execution environments.
-Additionally, related work is not comprehensive.
+-----
+Reviewer #2:
 
->> Detailed comments:
->> - Related work should be carefully revised, and include popular workflow system such as Swift, Pegasus, Makeflow, Taverna, Askalon, Nextflow, etc.
+>> 1) Related work should be carefully revised, and include popular workflow system such as Swift, Pegasus, Makeflow, Taverna, Askalon, Nextflow, etc.
 (only Kepler is shown as an example).
 The manuscript claims that ICE follows the five categories described in the motivation section, however it is not the only workflow system that follows this classification.
-
-The purpose of this work is not to extensively compare ICE to other workflow engines,
 
@@
 
->> The same issue appears again in Section 2.0.2 (section number should be revised too), where the presented model is claimed to significantly differ from similar efforts in workflow science.
+>> 1.b) The same issue appears again in Section 2.0.2 (section number should be revised too), where the presented model is claimed to significantly differ from similar efforts in workflow science.
 This is not accurate, there are several workflow systems that follows the activities model, such as Moteur, Taverna, and Chiron.
@@
 
->> Last, interactive analysis of workflow executions is claimed as a novelty of this work; however workflow steering has been investigated by over a decade and support in systems such as Chiron and SciCumulus.
+>> 2) Last, interactive analysis of workflow executions is claimed as a novelty of this work; however workflow steering has been investigated by over a decade and support in systems such as Chiron and SciCumulus.
 How ICE differs from them?
@@
 Our paper only points out that ICE can perform this work and does not, as far as we can tell, claim that ICE uniquely provides this capability.
+We did not address anything related to this point, but would be happy to do so with more direction if necessary.
 
->> 
->> - Section 3, software description needs to be substantially improved.
+>> 3) Section 3, software description needs to be substantially improved.
 It misses an overview architecture (a figure would be extremely helpful) that shows how ICE components interact/leverage Eclipse components.
@@
 
->> Several definitions are looseness:
->> + How the Items model differs from Taverna's model with Web Services?
+>> 4) How the Items model differs from Taverna's model with Web Services?
 
@@
 
->> + There is a mention that ICE API will be evolved to make the API language closer to other systems. Which systems and how?
+>> 5) There is a mention that ICE API will be evolved to make the API language closer to other systems. Which systems and how?
 
@@
 
->> + What defines a small output (so it will be automatically transferred)?
+>> 6) What defines a small output (so it will be automatically transferred)?
 
@@
 
->> + Why is it more sophisticated? What can be achieved here? It is important to enumerate the advantages.
+>> 7) Why is it more sophisticated? What can be achieved here? It is important to enumerate the advantages.
 
-We have updated the text in this section to more clearly reflect our thinking on language-based workflows in ICE.
+We have updated the text in this section to more clearly and fairly reflect our thinking on language-based workflows in ICE.
 
->> + What is a 'stubs' of plugins? How will it then interact with the framework? Which capabilities are used to enable them with ICE?
+>> 8) What is a 'stubs' of plugins? How will it then interact with the framework? Which capabilities are used to enable them with ICE?
 
-Updated the text to define stubs, strengthen the related statement on installation, and to describe the role of the OSGi in this process.
+We have updated the text to define stubs, strengthen the related statement on installation, and to describe the role of the OSGi in this process.
 
->> + Which operations are available via the APIs? It is mentioned that it has a rich API, but no detailed information is provided.
+>> 9) Which operations are available via the APIs? It is mentioned that it has a rich API, but no detailed information is provided.
 
@@
 
->> 
->> - IMHO, one of the main contributions and novelty of the paper is the combination of the Eclipse IDE with the workflow development/execution capabilities.
+>> 10) IMHO, one of the main contributions and novelty of the paper is the combination of the Eclipse IDE with the workflow development/execution capabilities.
 However, it is not discussed in detail how a user may benefit from this integration.
 
-This point has been addressed by creating a section specifically on the relationship to Eclipse out of content from the old framework extension section and new information on the benefits of self-hosting.
+This point has been addressed by creating a section specifically on the relationship to Eclipse by merging content from the old framework extension section and new information on the benefits of self-hosting.
 
->> 
->> - The examples section would significantly benefit of more information about how the workflows are executed.
+>> 11) The examples section would significantly benefit of more information about how the workflows are executed.
 
-All workflows in ICE are executed as described in the executing jobs sub section.
+We added a paragraph describing how workflows are executed in ICE at the end of the executing jobs section.
+The main purpose of this paragraph was to illustrate the differences between executing jobs and executing workflows because they are significantly different.
 
->> 
->> - Also, there are mentions that ICE can run locally and in HPC platforms, but no information is provided on how the system actually executes the workflows.
+>> 12) Also, there are mentions that ICE can run locally and in HPC platforms, but no information is provided on how the system actually executes the workflows.
 There is a quick mention to SSH connections, but nowadays there are other methods to remotely submit jobs for execution, such as Globus GRAM, Bosco, etc.
@@
 
->> 
->> In summary, I see much potential in the proposed workflow tool, however a thoroughly characterization and description of the architectural components and their capabilities is key to demonstrate the novelty and impact of the discussed system.
+>> 13) In summary, I see much potential in the proposed workflow tool, however a thoroughly characterization and description of the architectural components and their capabilities is key to demonstrate the novelty and impact of the discussed system.
 
-We are very grateful for this thorough review of the paper. We believe that we have addressed this review just as thoroughly with the significant updates provided in this revised manuscript.
-
-Also tightened up text significantly.
-
->> 
->> ******************************************
->> Please note that the editorial process varies considerably from journal to journal.
-To view the submission-to-publication lifecycle, click here: http://help.elsevier.com/app/answers/detail/p/7923/a_id/160
->> 
->> For further assistance, please visit our customer support site at http://help.elsevier.com/app/answers/list/p/7923.
-Here you can search for solutions on a range of topics, find answers to frequently asked questions and learn more about EES via interactive tutorials.
-You will also find our 24/7 support contact details should you need any further assistance from one of our customer support representatives.
+We are very grateful for this thorough review of the paper.
+We believe that we have addressed this review just as thoroughly with the significant updates provided in this revised manuscript, especially the new content on the architecture and the relationship to other Eclipse technologies.

### 2018-07-13 src/content.tex
Addressed editor's comments. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 
-Computational scientists perform a variety of tasks in modeling and
-simulation that can be abstracted into a lightweight theoretical
-framework based broadly on five high-level activities: (1)
-creating input, (2) executing jobs, (3) analyzing results, (4) managing
-data, and (5) modifying code. Those same computational scientists would
+ICE's workflow model is based on making it easier for scientists to create input, launch jobs, analyze results, manage data, and modify code. Many scientists would
 most likely find these activities difficult for all codes with which
@@
 modeling and simulation results is far from simple data reduction and is
-generally far more interactive for computational scientists.
+generally far more interactive for scientists.
 
@@
 \cite{the_nek5000_team_nek5000_2014}.
-Many computational scientists consider ``their workflow'' to be re-running
+Many scientists consider ``their workflow'' to be re-running
 software after modifications for purely exploratory purposes. This might
@@
 
-ICE was specifically created to address hands-on workflows for computational scientists, as in Section \ref{illustrative-examples}. Users download and
+ICE was specifically created to address hands-on workflows for scientists, as in Section \ref{illustrative-examples}. Users download and
 execute ICE locally, and ICE in turn orchestrates local or remote workflows as
@@
 The most important function of ICE is to serve as an easily extended
-workflow management system for computational scientists in support of
+workflow management system for scientists in support of
 the activities described previously. In practice, it is most often used as a
@@
 
-Modeling and simulation workflows for computational scientists differ
+Modeling and simulation workflows for scientists differ
 greatly from those of experimentalists or those who primarily interact with

### 2018-07-13 src/main.tex
Fixed a typo in the abstract. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>
Addressed editor's comments. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 workflows are developed iteratively and simultaneously. This work
-describes common modeling and simulation activities in workflows and how combinations of these
-activities form unique workflows. It presents the Eclipse Integrated
+describes common modeling and simulation activities and how combinations of these
+activities form unique workflows. We present the Eclipse Integrated
 Computational Environment as a workflow management system and
@@
 
-\section{Notice of Copyright}\label{notice-of-copyright}
+\section*{Notice of Copyright}
 

### 2019-06-23 src/content.tex
Modified content to fit thesis format.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 \centering
-\includegraphics[width=\textwidth]{src/images/ICE-arch-1.jpg}
+\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-1.jpg}
 \caption{High-level architecture of ICE showing the relationships and rough division of responsibility between the five primary components of ICE.
@@
 \centering
-\includegraphics[width=\textwidth]{src/images/ICE-arch-2.jpg}
+\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-2.jpg}
 \caption{The architecture of the ICE Core and its dependencies.
@@
 \centering
-\includegraphics[width=\textwidth]{src/images/ICE-arch-3.jpg}
+\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-3.jpg}
 \caption{The class hierarchy of ICE Items showing the relationships between the Item, its subclasses, and services that it uses.
@@
 \centering
-\includegraphics[width=\textwidth]{src/images/ICE-arch-4.jpg}
+\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-4.jpg}
 \caption{Common data structures and their relationships in ICE.}
@@
 \centering
-\includegraphics[width=\textwidth]{images/vibe_20151016.png}
+\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/vibe_20151016.png}
 \caption{ICE workbench for VIBE analysis.}
@@
 \centering
-\includegraphics[width=\textwidth]{images/ice-moose.png}
+\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ice-moose.png}
 \caption{ICE workbench for MOOSE workflows.}
@@
 \centering
-\includegraphics[width=\textwidth]{images/ice-bjm.png}
+\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ice-bjm.png}
 \caption{ICE workbench for binder jet modeling.}
@@
 \centering
-\includegraphics[width=\textwidth]{images/reflectivity-screenshot.png}
+\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/reflectivity-screenshot.png}
 \caption{ICE workbench for neutron reflectivity.}
@@
 \centering
-\includegraphics[width=\textwidth]{images/jaded.png}
+\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/jaded.png}
 \caption{ICE workbench in the Jade Adiabatic Development Environment (JADE) for quantum computing simulations.}

### 2019-07-23 src/content.tex
Addressed comments from Charlie.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 
-In previous work, Billings et al. interviewed modeling and simulation subject matter experts to compile a list of requirements for implementing and 
-using these kinds of applications. In the process, they discovered 
-that many of the difficulties inherent in using
-high-performance modeling and simulation software fall into five
-distinct categories \cite{billings_designing_2009}. These activities,
-detailed in Section \ref{workflow-model}, include (1) creating input,
-(2) executing jobs, (3) analyzing results, (4) managing data, and (5)
-modifying code. There are many tools that address these problems
+In previous work, Billings et al. interviewed modeling and simulation subject
+matter experts to compile a list of requirements for implementing and using
+these kinds of applications. In the process, they discovered that many of the
+difficulties inherent in using high-performance modeling and simulation
+software fall into five distinct categories \cite{billings_designing_2009}.
+These activities, detailed in Section \ref{workflow-model}, include (1)
+creating input, (2) executing jobs, (3) analyzing results, (4) managing data,
+and (5) modifying code. There are many tools that address these problems
 individually, but the same research found that the excess number and
@@
 
-Previous efforts to address these five issues have resulted in general-purpose scientific workflow tools like Kepler \cite{ludascher_scientific_2006} 
-or myopic tools that satisfy only a single
-set of requirements for a single piece of software or a single platform. These
-are opposite extremes, but a middle-of-the-road solution is also
-possible. A workflow engine could be developed that limits its scope to
-high-performance computing (HPC) and to the set of possible workflows
-associated with the five previously mentioned activities. With only
-minor additional development, a rich application programming interface
-(API) could be exposed so that highly customized solutions could still
-be made based on this limited workflow engine.
+Previous efforts to address these five issues have resulted in general-purpose
+scientific workflow tools like Kepler \cite{ludascher_scientific_2006} or
+myopic tools that satisfy only a single set of requirements for a single piece
+of software or a single platform. These are opposite extremes, but a
+middle-of-the-road solution is also possible. A workflow engine could be
+developed that limits its scope to high-performance computing (HPC) and to the
+set of possible workflows associated with the five previously mentioned
+activities. With only minor additional development, a rich application
+programming interface (API) could be exposed so that highly customized
+solutions could still be made based on this limited workflow engine.
 
@@
   modeling and simulation activities can be described in a succinct
-  workflow model (see ``Workflow Model'');
+  workflow model (see \S \ref{workflow-model}),
 \item
   an architecture for such a workflow system can satisfy the model of
-  workflows in an extensible way (see ``Software Architecture''); and 
+  workflows in an extensible way (see \S \ref{software-architecture}), and 
 \item
@@
   including virtual battery simulations and additive manufacturing, 
-  among others (see ``Illustrative Examples'').
+  among others (see \S \ref{illustrative-examples}).
 \end{itemize}
@@
 
-ICE's workflow model is based on making it easier for scientists to create input, launch jobs, analyze results, manage data, and modify code. Many scientists would
-most likely find these activities difficult for all codes with which
-they lack experience, whereas with their own codes---or those with which
-they are most familiar---these tasks may be so simple that they are
-taken for granted. Any particular combination of these activities across
-one or more scientific software package or code results in a unique
-workflow. Such a workflow is normally, but not always, requested
-by a human user and orchestrated by a workflow management system.
+ICE's workflow model is based on making it easier for scientists to create
+input, launch jobs, analyze results, manage data, and modify code. Many
+scientists would most likely find these activities difficult for all codes with
+which they lack experience, whereas with their own codes---or those with which
+they are most familiar---these tasks may be so simple that they are taken for
+granted. Any particular combination of these activities across one or more
+scientific software package or code results in a unique workflow. Such a
+workflow is normally, but not always, requested by a human user and
+orchestrated by a workflow management system.
 
@@
 grid, particle distribution). The collection of all required input can
-be quite large and may go by many names, including ``input set,''
+be quite large and can go by many names, including ``input set,''
 ``input package,'' ``problem,'' or, simply, ``input.'' Often, the set of
@@
 
-Local jobs in ICE are executed using standard Java system calls.
-Remote jobs are launched only through SSH connections on remote machines.
-This includes direct SSH command execution on clusters and proxy connections through a pilot service on large Leadership-class supercomputers.
-Services such as Globus GRAM and Bosco are not supported, but the SSH command execution includes extensive support for numerous batch and queuing systems.
-The Eclipse Parallel Tools Platform (PTP) is used to create all remote SSH connections, regardless of the target machine \cite{tibbitts_integrated_2009}.
+Local jobs in ICE are executed using standard Java system calls. Remote jobs
+are launched only through SSH connections on remote machines. This includes
+direct SSH command execution on clusters and proxy connections through a pilot
+service on large leadership-class supercomputers. Services such as Globus GRAM
+and Bosco are not supported, but the SSH command execution includes extensive
+support for numerous batch and queuing systems. The Eclipse Parallel Tools
+Platform (PTP) is used to create all remote SSH connections, regardless of the
+target machine \cite{tibbitts_integrated_2009}.
 
@@
 ``executing a job'' includes monitoring that job in one or more ways,
-possibly including real-time updates to visualizations.
-It is also important to note that executing a job is not the same as executing a workflow.
-Executing jobs specifically refers to launching simulations, whereas executing a workflow could be something different such as generating input or post-processing results.
-This is an important distinction because ICE's workflows are all executed locally, but simulations and work may be distributed remotely depending on the implementation of the workflow plugin.
+possibly including real-time updates to visualizations. It is also important to
+note that executing a job is not the same as executing a workflow. Executing
+jobs specifically refers to launching simulations, whereas executing a workflow
+could be something different such as generating input or postprocessing
+results. This is an important distinction because ICE's workflows are all
+executed locally, but simulations and work can be distributed remotely
+depending on the implementation of the workflow plugin.
 
@@
 scientific significance from the transformed data. This could include, for
-example, post-processing results and visualizing the new data with
+example, postprocessing results and visualizing the new data with
 dedicated visualization tools. For many types of scientific computing,
@@
 generating new input, or analyzing results. Examples include archiving
-data, packaging data for publications, and updating values manually or through scripts (often in light of new information from publications).
+data, packaging data for publications, and updating values manually or through
+scripts (often in light of new information from publications).
 
@@
 scientific computing workflow. However, modeling and simulation use
-cases often require users to explicitly modify code before execution or to issue special re-build instructions.
-This is true, for example, with the computational fluid dynamics code Nek5000, which requires modification of code before compilation and special build instructions using the \textit{makenek} shell script
-\cite{the_nek5000_team_nek5000_2014}.
+cases often require users to explicitly modify code before execution or to
+issue special build instructions. This is true, for example, with the
+computational fluid dynamics code Nek5000, which requires modification of code
+before compilation and special build instructions using the \textit{makenek}
+shell script \cite{the_nek5000_team_nek5000_2014}.
 Many scientists consider ``their workflow'' to be re-running
 software after modifications for purely exploratory purposes. This might
-be required if the model that the author is modifying cannot be
-configured directly as part of the input but can be easily accomplished by manipulating the source code.
+be required if the model the author is modifying cannot be
+configured directly as part of the input but can be easily accomplished by
+manipulating the source code.
 
@@
 ICE's model of workflows differs significantly from many other
-efforts in workflow science because it defines workflows in terms of high-level activities that are meant to guide workflow implementers and users.
-Many other workflow models in the literature define a workflow as
-a collection of computing processes. For example, Yu and Buyya define
-grid workflows as ``a collection of tasks that are processed on
-distributed resources in a well-defined order to accomplish a specific
-goal'' \cite{yu_taxonomy_2005}. Others, such as Pizzi et al., subscribe to
-similar definitions \cite{pizzi_aiida:_2016}. This ``process'' view is
-acceptable where the workflow is static and does not require additional
-human input or ``human in the loop'' behavior after all the initial
-human input is provided.
-However, workflows within ICE are fully interactive with regular callbacks to humans.
-It is simpler to discuss ``activities'' than it is to create a distinction between ``human processes'' and ``computer processes.''
-Focusing on ``activities'' over processes (human or computer) also has
-the benefit of removing concrete elements such as hardware or software properties that distract from details of workflows and workflow 
-management systems. That is, considerations such as memory usage and 
-raw performance are important, but questions about the abstract workflow 
-or what the workflow management system should do are far more important in this context.
+efforts in workflow science because it defines workflows in terms of high-level
+activities that are meant to guide workflow implementers and users. Many other
+workflow models in the literature define a workflow as a collection of
+computing processes. For example, Yu and Buyya define grid workflows as ``a
+collection of tasks that are processed on distributed resources in a
+well-defined order to accomplish a specific goal'' \cite{yu_taxonomy_2005}.
+Others, such as Pizzi et al., subscribe to similar definitions
+\cite{pizzi_aiida:_2016}. This ``process'' view is acceptable where the
+workflow is static and does not require additional human input or ``human in
+the loop'' behavior after all the initial human input is provided. However,
+workflows within ICE are fully interactive with regular callbacks to humans. It
+is simpler to discuss ``activities'' than it is to create a distinction between
+``human processes'' and ``computer processes.'' Focusing on activities over
+processes (human or computer) also has the benefit of removing concrete
+elements such as hardware or software properties that distract from details of
+workflows and workflow management systems. That is, considerations such as
+memory usage and raw performance are important, but questions about the
+abstract workflow or what the workflow management system should do are far more
+important in this context.
 
-There are other workflow engines that have their own concepts of activities, with various similarities and differences compared to ICE's model.
-For example, Taverna has a concept of activities \cite{wolstencroft_taverna_2013}.
-Activities in Taverna are defined as invocable activities within a workflow, which is closely related to a lower-level class in ICE called Actions (see \ref{item}).
-On the other hand, ICE's activities loosely describe what can be done conceptually and the workflows that are implemented provide the Actions that carry out these activities.
+There are other workflow engines that have their own concepts of activities,
+with various similarities and differences compared with ICE's model. For
+example, Taverna has a concept of activities \cite{wolstencroft_taverna_2013}.
+Activities in Taverna are defined as invocable activities within a workflow,
+which is closely related to a lower-level class in ICE called Actions (see \S
+\ref{item}). On the other hand, ICE's activities loosely describe what can be
+done conceptually and the workflows that are implemented provide the Actions
+that carry out these activities.
 
-ICE and Taverna can both natively execute Java code, but ICE 2.0 cannot natively invoke Web Service Definition Language (WSDL) web services.
-ICE uses regular Java-based libraries to interact with web services, such as Jersey, and requires that developers write the code to do this directly.
-Shim services in Taverna are provided in ICE as separate services in the framework, but are otherwise very similar.
+ICE and Taverna can both natively execute Java code, but ICE 2.0 cannot
+natively invoke Web Service Definition Language (WSDL) web services. ICE uses
+regular Java-based libraries to interact with web services, such as Jersey, and
+requires that developers write the code to do this directly. Shim services in
+Taverna are provided in ICE as separate services in the framework but are
+otherwise very similar.
 
-Chiron, an algebraic workflow engine, has a concept of activities that is closer to ICE's than Taverna's, but still very strongly related to implementation \cite{ogasawara_chiron_2014}.
-Activities in Chiron are combinations of the program or expression to execute, plus the input schema, plus the output schema.
-This is a close match to the design of the Item class in ICE.
-ICE's Items (see Section \ref{item}) implement the high-level activities, such as launching a job or creating a model.
-The major difference between Chiron's activities and ICE's Items appears to be scope.
-A Chiron activity such as Map or Reduce would normally be implemented as an Action in ICE, whereas an Item in ICE may be tasked with executing multiple Actions to enact a workflow.
+Chiron, an algebraic workflow engine, has a concept of activities that is
+closer to ICE's than Taverna's but still very strongly related to
+implementation \cite{ogasawara_chiron_2014}. Activities in Chiron are
+combinations of the program or expression to execute, plus the input schema,
+plus the output schema. This is a close match to the design of the Item class
+in ICE. ICE's Items (see Section \ref{item}) implement the high-level
+activities, such as launching a job or creating a model. The major difference
+between Chiron's activities and ICE's Items appears to be scope. A Chiron
+activity such as Map or Reduce would normally be implemented as an Action in
+ICE, whereas an Item in ICE can be tasked with executing multiple Actions to
+enact a workflow.
 
-One significant difference between ICE and many other systems is that it uses a language-based approach to defining workflows, but with a standard language, Java, as opposed to a custom workflow definition language.
-Pizzi et al.
-do this with Aiida and Python, and the Fireworks Workflow Engine also uses Python.
-The advantage of this approach is that compilation is not a problem.
-ICE also differs from other workflow engines because it is specifically focused on modeling and simulation instead of grid workflows.
-Grid workflows are almost always defined as workflows based on trees without humans in the loop, but modeling and simulation workflows are much more interactive and undirected \cite{billings_toward_2017}.
+One significant difference between ICE and many other systems is that it uses a
+language-based approach to defining workflows but with a standard language,
+Java, as opposed to a custom workflow definition language. Pizzi et al. do this
+with Aiida and Python, and the Fireworks Workflow Engine also uses Python. The
+advantage of this approach is that compilation is not a problem. ICE also
+differs from other workflow engines because it is specifically focused on
+modeling and simulation instead of grid workflows. Grid workflows are almost
+always defined as workflows based on trees without humans in the loop, but
+modeling and simulation workflows are much more interactive and undirected
+\cite{billings_toward_2017}.
 
@@
 
-ICE was specifically created to address hands-on workflows for scientists, as in Section \ref{illustrative-examples}. Users download and
-execute ICE locally, and ICE in turn orchestrates local or remote workflows as
-required. It provides a comprehensive workbench for modeling and
-simulation that includes tools for workflows, visualization, data
-management, and software development.
+ICE was specifically created to address hands-on workflows for scientists, as
+described in \S \ref{illustrative-examples}. Users download and execute ICE
+locally, and ICE in turn orchestrates local or remote workflows as required. It
+provides a comprehensive workbench for modeling and simulation that includes
+tools for workflows, visualization, data management, and software development.
 
@@
 
-\begin{figure}[htbp]
-\centering
+\begin{figure}[htbp] \centering
 \baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-1.jpg}
-\caption{High-level architecture of ICE showing the relationships and rough division of responsibility between the five primary components of ICE.
-The ICE Core is responsible for the workflow management and delegations instructions and data to the Item and Data Structures, respectively.
-User input is received from the client or through headless interactions, while persistence of large amounts of data is delegated to a persistence service.}
+\caption{High-level architecture of ICE showing the relationships and rough
+division of responsibility between the five primary components of ICE. The ICE
+Core is responsible for the workflow management and delegations instructions
+and data to the Item and data structures, respectively. User input is received
+from the client or through headless interactions, while persistence of large
+amounts of data is delegated to a persistence service. The ``1'' and ``*''
+represent the cardinality of the aggregation relationship.}
 \label{highlevel-arch}
@@
 
-Workflows and tasks in ICE are not explicitly treated as trees, or
+Workflows and tasks in ICE are not explicitly treated as trees or
 directed acyclic graphs (DAGS), as is common with grid workflow tools
 \cite{yu_taxonomy_2005}. Instead, ICE's design is inspired by representational
-state transfer (REST) and the workflow engine is implemented as services in an Eclipse Rich Client Platform (RCP) application
+state transfer (REST), and the workflow engine is implemented as services in an
+Eclipse Rich Client Platform (RCP) application
 \cite{fielding_architectural_2000} \cite{mcaffer_eclipse_2010}.
 
-Figure \ref{highlevel-arch} shows the five primary components of ICE and their relationships to each other.
-Users initiate requests to create, edit, update, or delete workflows from the ``ICE Client'' (the workbench) or through headless interactions using web or language programming interfaces.
-The list of available workflows
-that can be created is provided dynamically to the ICE Client by
-the ``ICE Core,'' which acts as a server and is the primary component responsible for workflow orchestration. Workflow information is
-provided dynamically because it often changes at run time based on 
-both the configuration of available workflow components in the registry and on
-persisted workflows that users have saved in their workspace.
-Workflow task enactment and execution is performed by services called ``Items.'' Information about workflows is provided to the Client by the Core
-through common data structures rooted in a stateless ``Form'' tree. Forms describe the workflow and provide
-all the necessary information to understand \emph{what} should process
-the workflow (but not \emph{how} it should be processed). Once users
-modify the description of the workflow in the Form to provide their
-specific details, the Client dispatches a request to the Core to modify
-and/or process the workflow. The Core then uses the information from the Form
-to perform a service lookup to identify the correct Item to process the workflow.
+Figure \ref{highlevel-arch} shows the five primary components of ICE and their
+relationships to each other. Users initiate requests to create, edit, update, or
+delete workflows from the ``ICE Client'' (the workbench) or through headless
+interactions using web or language programming interfaces. The list of available
+workflows that can be created is provided dynamically to the ICE Client by the
+``ICE Core,'' which acts as a server and is the primary component responsible
+for workflow orchestration. Workflow information is provided dynamically because
+it often changes at run time based on both the configuration of available
+workflow components in the registry and on persisted workflows users have
+saved in their workspace. Workflow task enactment and execution is performed by
+services called ``Items.'' Information about workflows is provided to the Client
+by the Core through common data structures rooted in a stateless ``Form'' tree.
+Forms describe the workflow and provide all the necessary information to
+understand \emph{what} should process the workflow (but not \emph{how} it should
+be processed). Once users modify the description of the workflow in the Form to
+provide their specific details, the Client dispatches a request to the Core to
+modify and/or process the workflow. The Core then uses the information from the
+Form to perform a service lookup to identify the correct Item to process the
+workflow.
 
@@
 \baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-2.jpg}
-\caption{The architecture of the ICE Core and its dependencies.
-The ICE Core class handles communications between workflow Items and common data structures, but delegates construction of workflow Items to builders.}
+\caption{Architecture of the ICE Core and its dependencies. The ICE Core class
+handles communications between workflow Items and common data structures but
+delegates construction of workflow Items to builders.}
 \label{core-arch}
@@
 
-The primary purpose of the ICE Core is to orchestrate workflows and services for the platform.
-Figure \ref{core-arch} shows the primary classes that interact with the ICE Core.
-It is the ``core'' control component of ICE where all other component interactions converge.
-It is the middle tier of ICE's architecture and brokers communications between Items and Clients (graphical or not) by sharing Forms that contain workflow data.
-The ICE Core class delegates construction and management of Items to the Item Manager.
+The primary purpose of the ICE Core is to orchestrate workflows and services for
+the platform. Figure \ref{core-arch} shows the primary classes that interact
+with the ICE Core. It is the ``core'' control component of ICE where all other
+component interactions converge. It is the middle tier of ICE's architecture and
+brokers communications between Items and Clients (graphical or not) by sharing
+Forms that contain workflow data. The ICE Core class delegates construction and
+management of Items to the Item Manager.
 
-The Item Manager acts as a container and factory for Items created by the ICE Core.
-Items are constructed using the Builder pattern, with concrete construction handled by realizations of the ItemBuilder interface.
+The Item Manager acts as a container and factory for Items created by the ICE
+Core. Items are constructed using the Builder pattern, with concrete
+construction handled by realizations of the ItemBuilder interface.
 
-ICE 2.0 includes a graphical client based on the Eclipse Workbench, which is common for Eclipse applications.
-The workflow management capabilities of the core can be accessed through languages and a web-based programming interface as well (see Section \ref{framework}).
+ICE 2.0 includes a graphical client based on the Eclipse Workbench, which is
+common for Eclipse applications. The workflow management capabilities of the
+core can be accessed through languages and a web-based programming interface as
+well (see Section \ref{framework}).
 
@@
 \baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-3.jpg}
-\caption{The class hierarchy of ICE Items showing the relationships between the Item, its subclasses, and services that it uses.
-Vibe Launcher and MOOSE Launcher are examples of special Job Launch Items for executing jobs, and their applications are discussed in section \ref{illustrative-examples}.}
+\caption{The class hierarchy of ICE Items showing the relationships between the
+Item, its subclasses, and services that it uses. Vibe Launcher and MOOSE
+Launcher are examples of special Job Launch Items for executing jobs, and their
+applications are discussed in \S \ref{illustrative-examples}.}
 \label{item-arch}
@@
 
-Each workflow Item in ICE is an independent service, and each
-workflow type is a subclass of the Item base class or another Item subclass. Items are registered dynamically
-through a service registry in ICE (see Section \ref{framework}) and
-provide collections of workflow data, Forms, for the ICE Core and Client. Since ICE's design is
-highly object oriented, it is easiest to think of the Item class as a
-description of an abstract workflow and an Item object (an instance of
-the class) as a concrete workflow with all required execution details
-specified in its Form.
+Each workflow Item in ICE is an independent service, and each workflow type is a
+subclass of the Item base class or another Item subclass. Items are registered
+dynamically through a service registry in ICE (see Section \ref{framework}) and
+provide collections of workflow data ---Forms--- for the ICE Core and Client.
+Since ICE's design is highly object oriented, it is easiest to think of the Item class
+as a description of an abstract workflow and an Item object (an instance of the
+class) as a concrete workflow with all required execution details specified in
+its Form.
 
-Figure \ref{item-arch} shows the class hierarchy of the Item class and its collaborators.
-Individual components of workflows (i.e., workflow ``tasks'' or
-``nodes'') are either encoded directly in the workflow's subclass of
-Item or provided as ``Actions'' that are dynamically registered with
-an ``Action Factory'' and obtained at run time.
-Common data structures that are shared across Items, the Client, and the Core are provided by the data structures component.
-Table 1 describes the differences between Items, Actions, and Forms.\footnote{An upcoming
-update to the API will include the formal introduction of
-IWorkflow, IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's
-API language closer to other systems such as Triquetrum. However, this must be done carefully to preserve backwards compatibility.}
+Figure \ref{item-arch} shows the class hierarchy of the Item class and its
+collaborators.
+Individual components of workflows (i.e., workflow ``tasks'' or ``nodes'') are
+either encoded directly in the workflow's subclass of Item or provided as
+``Actions'' that are dynamically registered with an ``Action Factory'' and
+obtained at run time. Common data structures that are shared across Items, the
+Client, and the Core are provided by the data structures component. Table 1
+describes the differences between Items, Actions, and Forms.\footnote{An
+upcoming update to the API will include the formal introduction of IWorkflow,
+IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's API language closer
+to other systems such as Triquetrum. However, this must be done carefully to
+preserve backwards compatibility.}
 
@@
 \end{tabularx}
-\caption{Class Descriptions for Items, Forms, and Actions}
+\caption{Class descriptions for Items, Forms, and Actions.}
 \end{table*}
 
-Commonly used subclasses of Item include the Model and Job Launcher classes, which can be  used to create workflow plugins for input generation and workflow execution, respectively.
-Composite Items are special Items that are built of compositions of other Items.
-Composite Items are commonly used for workflow Items that can be executed in parallel or to tightly couple different workflow tasks for resource and performance management.
+Commonly used subclasses of Item include the Model and Job Launcher classes,
+which can be  used to create workflow plugins for input generation and workflow
+execution, respectively. Composite Items are special Items that are built of
+compositions of other Items. Composite Items are commonly used for workflow
+Items that can be executed in parallel or to tightly couple different workflow
+tasks for resource and performance management.
 
@@
 This design is very important. First, it means that all workflows in
-ICE, regardless of their actual details and functions, can only behave in
+ICE, regardless of their actual details and functions, can behave only in
 a specific set of known and predictable ways, and this predictability 
@@
 
-ICE contains a collection of common data structures that are useful for representing data needed modeling and simulation workflows.
-Figure \ref{data-arch} shows some of these classes and their relationship.
-All data structures (and Items) in ICE are uniquely identifiable and behave in predictable ways: they receive and dispatch updates, can be visited to determine type information, etc.
-\textit{Components} in the data sense, not the class sense, represent a special data structure that forms a child of a Form.
-Forms themselves are components and hierarchically aggregate other components.
+ICE contains a collection of common data structures that are useful for
+representing data needed modeling and simulation workflows. Figure
+\ref{data-arch} shows some of these classes and their relationship. All data
+structures (and Items) in ICE are uniquely identifiable and behave in
+predictable ways: they receive and dispatch updates, can be visited to determine
+type information, etc. \textit{Components} in the data sense, not the class
+sense, represent a special data structure that forms a child of a Form. Forms
+themselves are components and hierarchically aggregate other components.
 
-The name ``Component'' in the context of ICE's data structures refers to a unique and reusable collection of data, not a class or component in the object oriented sense.
-Components that hold data do very little of their own work but strongly scope the interfacial contract of their clients.
+The name ``Component'' in the context of ICE's data structures refers to a
+unique and reusable collection of data, not a class or component in the object
+oriented sense. Components that hold data do very little of their own work but
+strongly scope the interfacial contract of their clients.
 
@@
 the workflow and available in the project directory of the workspace.
-Likewise, if the output is small enough (less than 50 megabytes), ICE will automatically move it back
-to the local directory. By convention, all paths in ICE's Forms are
-relative to the workspace root path. Workspace directories are specified
-by the user and are fully functional Eclipse workspaces.
+Likewise, if the output is small enough (less than 50 megabytes), ICE will
+automatically move it back to the local directory. By convention, all paths in
+ICE's Forms are relative to the workspace root path. Workspace directories are
+specified by the user and are fully functional Eclipse workspaces.
 
@@
 could replace the XML-based provider since it is registered as a dynamic 
-service and a JAX-P based provider has been used in the past.
+service and a JAXP based provider has been used in the past.
 
@@
 
-ICE is an Eclipse Rich Client Platform (RCP) application
-\cite{mcaffer_eclipse_2010} and has a plugin architecture based on 
-Equinox, which is the reference implementation of the Open Service Gateway Initiative (OSGi)
-framework specification \cite{mcaffer_osgi_2010}.
-It is most appropriate to think of Eclipse ICE as an alternative flavor of any other Eclipse development environment because like those environments it is just a collection of Eclipse plugins with a well-defined purpose and brand.
-ICE uses more than 1,200 additional packages from the Eclipse ecosystem to provide services like language
-support and visualization. Each unique element of ICE described
-in this work---including the Client, Core, Items, and data structures---is 
-provided as plugins to Equinox. Most plugins are managed
-dynamically and provided as services that can be obtained as dynamic OSGi Declarative Services. File I/O in ICE, with only a few exceptions,
-interacts with the RCP's Resources plugin and the standard Eclipse Workspace. This also includes remote resources that are managed with Eclipse PTP.
+ICE is an Eclipse RCP application \cite{mcaffer_eclipse_2010} and has a plugin
+architecture based on Equinox, which is the reference implementation of the Open
+Service Gateway Initiative (OSGi) framework specification
+\cite{mcaffer_osgi_2010}. It is most appropriate to think of Eclipse ICE as an
+alternative flavor of any other Eclipse development environment because like
+those environments it is just a collection of Eclipse plugins with a
+well-defined purpose and brand. ICE uses more than 1,200 additional packages
+from the Eclipse ecosystem to provide services like language support and
+visualization. Each unique element of ICE described in this work---including the
+Client, Core, Items, and data structures---is provided as plugins to Equinox.
+Most plugins are managed dynamically and provided as services that can be
+obtained as dynamic OSGi Declarative Services. File input/output in ICE, with
+only a few exceptions, interacts with the RCP's Resources plugin and the
+standard Eclipse Workspace. This also includes remote resources that are
+managed with Eclipse PTP.
 
-ICE plugins are created used normal Eclipse development tools and installed into either the running instance of ICE or published in a newly built version.
-In either case, the running platform of ICE can only use the plugins that are actually installed and at least a small amount of code must be written in Java for each plugin.
-This extension method may seem odd to the novice user or developer, especially if they do not know Java very well, but
-this design was chosen because it is an easy, fast, and precise way to create workflows.
+ICE plugins are created using normal Eclipse development tools and are installed
+into either the running instance of ICE or published in a newly built version.
+In either case, the running platform of ICE can use only the plugins that are
+actually installed and at least a small amount of code must be written in Java
+for each plugin. This extension method may seem odd to the novice user or
+developer, especially if they do not know Java very well, but this design was
+chosen because it is an easy, fast, and precise way to create workflows.
 
-ICE provides built-in development tools to automatically generate empty but ready to compile classes (``stubs'') of plugins that can then be installed into the framework as services.
-These tools are based on other code generation tools in the Eclipse platform.
-This
-``self-hosting'' makes it possible for new users to create complex,
-sophisticated workflows very quickly because they are not required to
-know how to interact with the framework. Development of new workflows is streamlined because ICE provides a
-rich API that exposes all workflow management functionality, documentation, tutorials, and tools to further simplify the process.
-These are shared through the self-hosted environment by code completion tools, help menus, and documentation overlays.
-The close proximity of the workflow environment with the development platform for modeling and simulation codes is also beneficial because, as a self-hosted entity, workflows can be co-developed with the code.
+ICE provides built-in development tools to automatically generate empty but
+ready to compile classes (``stubs'') of plugins that can then be installed into
+the framework as services. These tools are based on other code generation tools
+in the Eclipse platform. This ``self-hosting'' makes it possible for new users
+to create complex, sophisticated workflows very quickly because they are not
+required to know how to interact with the framework. Development of new
+workflows is streamlined because ICE provides a rich API that exposes all
+workflow management functionality, documentation, tutorials, and tools to
+further simplify the process. These are shared through the self-hosted
+environment by code completion tools, help menus, and documentation overlays.
+The proximity of the workflow environment with the development platform
+for modeling and simulation codes is also beneficial because, as a self-hosted
+entity, workflows can be codeveloped with the code.
 
@@
 API. The web API is also used as the primary means of providing real-time 
-feedback and monitoring support in ICE, and it is published as an OSGi service as well. These services can also be consumed as OSGi Remote Services.
+feedback and monitoring support in ICE, and it is published as an OSGi service
+as well. These services can also be consumed as OSGi Remote Services.
 
@@
 Jython, and Python. This also makes it possible to extend the
-environment by adding Items in these languages.
-Specifically, scripts in Javascript and Python are written and executed in simple shell that is part of the workbench.
-Calling other languages, such as C or Fortran, is typically accomplished by adding workflow Items for the executables in these languages and performing local workflow job launches.
-C languages routines have been called from ICE through the Java Native Interface (JNI), but this is not a technique that is widely used with the platform because of its complexity.
+environment by adding Items in these languages. Specifically, scripts in
+Javascript and Python are written and executed in simple shell that is part of
+the workbench. Calling other languages, such as C or Fortran, is typically
+accomplished by adding workflow Items for the executables in these languages
+and performing local workflow job launches. C language routines have been
+called from ICE through the Java Native Interface (JNI), but this is not a
+technique that is widely used with the platform because of its complexity.
 
@@
 
-Outside of the development team, ICE is commonly deployed as a
-sophisticated user environment for computational science projects 
-(see Section \ref{impact}) and as a visualization tool. The ICE source code originally contained a
-significant amount of visualization support, but at the request of users
-in the community, that support was ``spun off'' in early 2016 as the 
-Eclipse Advanced Visualization Project (EAVP)~\cite{billings_eclipse_2015}.
+Outside of the development team, ICE is commonly deployed as a sophisticated
+user environment for computational science projects (see Section \ref{impact})
+and as a visualization tool. The ICE source code originally contained a
+significant amount of visualization support, but at the request of users in the
+community, that support was ``spun off'' in early 2016 as the Eclipse Advanced
+Visualization Project (EAVP)~\cite{billings_eclipse_2015}.
 
@@
 
-There are more than 300 MOOSE-based applications, and it is very
-easy to create new ones. The ICE development team uses ICE
-and MOOSE to quickly solve energy science problems with HPC resources 
-and to deploy domain-specific workbenches.
-ICE provides features for automatic installation, configuration, and optimization of scientific development environments.
-In the context of MOOSE, ICE includes support for automatically downloading and building MOOSE from MOOSE's GitHub
-repository. This integration enables users to immediately begin developing
-complex multiphysics applications using the preinstalled Eclipse C Development 
-Tools. Once the new MOOSE-based application is built, it will automatically work with
-the MOOSE workflow tools in ICE, although developers can also create
-customized workflow tools as needed.
+There are more than 300 MOOSE-based applications, and it is very easy to create
+new ones. The ICE development team uses ICE and MOOSE to quickly solve energy
+science problems with HPC resources and to deploy domain-specific workbenches.
+ICE provides features for automatic installation, configuration, and
+optimization of scientific development environments. In the context of MOOSE,
+ICE includes support for automatically downloading and building MOOSE from
+MOOSE's GitHub repository. This integration enables users to immediately begin
+developing complex multiphysics applications using the preinstalled Eclipse C
+Development Tools. Once the new MOOSE-based application is built, it will
+automatically work with the MOOSE workflow tools in ICE, although developers can
+also create customized workflow tools as needed.
 
@@
 Figure \ref{binder} shows an ICE-based workbench for performing simulations of
-this process with visualizations of the pre- and post-simulation
+this process with visualizations of the pre- and postsimulation
 properties of a central body with eight cantilevers. The primary
@@
 
-The impact of software tools like ICE is difficult to quantify. However,
-there are several examples of when ICE has significantly assisted its
-development team and others.
+The impact of software tools like ICE is difficult to quantify. However, there
+are several examples of ICE significantly assisting the development team and
+others.
 
 One pressing area of interest and impact is that of interoperability
-between workflow systems. There have been significant prior efforts in combining
-large workflow management systems (e.g., Mandal et al.
+between workflow systems. Significant prior efforts have been made to
+combine large workflow management systems (e.g., Mandal et al.
 \cite{mandal_integrating_2007}), but the end goal of gaining the greatest
@@
 possible to integrate multiple systems in a straightforward way. This
-allows it to connect to other workflow environments, such as Triquetrum,
+allows ICE to connect to other workflow environments, such as Triquetrum,
 quite easily \cite{brooks_introducing_2016}. Triquetrum, like Kepler in
@@
 with ICE might not invent something radically new, but they tend to
-streamline interactions with those tools. Many ICE users, and certainly
+streamline interactions within those tools. Many ICE users, and certainly
 the development team, have experienced improvements in their software
@@
 RNET Technologies, Inc., out of Dayton, Ohio, in response to a Small Business Innovation 
-Research award from the US Department of Energy. This web-based version of 
+Research award from the DOE. This web-based version of 
 ICE will continue ICE's support for nuclear energy and will integrate with cloud 
 computing solutions like Amazon Web Services and ORNL's Compute and Data
-Environment for Science (CADES). Additionally, while ICE has not directly led to
-any ``spin-off'' companies, ICE source code has been used
+Environment for Science (CADES). Additionally, although ICE has not directly led
+to any ``spin-off'' companies, ICE source code has been used
 in two spin-off projects: (1) EAVP (mentioned earlier) for advanced
@@
 \url{https://github.com/eclipse/ice/tree/master/examples}. ICE also includes an
-extensive suite of unit, integration, and UI tests, which are
-also excellent examples of how to work with the platform. Tutorial and demonstration videos are available on YouTube at \url{https://goo.gl/nxCzRD}.
+extensive suite of unit, integration, and user interface tests, which are
+also excellent examples of how to work with the platform. Tutorial and
+demonstration videos are available on YouTube at \url{https://goo.gl/nxCzRD}.
 
@@
 differences in architecture between a workflow management system focused
-on modeling and simulation compared with those focused on grids. ICE's broad
-applicability across many topics in energy science suggests that
+on modeling and simulation compared with systems focused on grids. ICE's broad
+applicability across many topics in energy science suggests
 there are opportunities for these systems in general. Finally, one 
@@
 simulation workflows to address greater challenges.
-
-\section*{Acknowledgments}\label{acknowledgments}
-\addcontentsline{toc}{section}{Acknowledgments}
-
-The authors are grateful for the assistance and support of the following
-people and institutions without whom this work would not have been
-possible. This includes many people who directly contributed to the
-project, either in its early days as ``NiCE'' or once it moved to
-Eclipse, including Ronald Allen, Andrew Belt, David E.
-Bernholdt, Tim Bohn, Erica Grant, Mike Guidry, John M. Hetrick III, Forest Hull, 
-Sebastien Jourdain, JiSoo Kim, Allison Koenecke, Fangzhou Lin, Eric J. Lingerfelt, Greg
-Lyon, Tony McCrary, Elizabeth Piersall, Neeti
-Pokhriyal, Adrian Sanchez, Claire Saunders, Nick Stanish, Matthew Wang, and
-Scott Wittenberg. The support of both the Nuclear Energy Advanced Modeling and Simulation (NEAMS) and Consortium for Simulation of Light Water Reactors (CASL) programs is also
-greatly appreciated. The authors would like to acknowledge the special
-contribution of the Eclipse Foundation, the Eclipse Community, the
-Eclipse Science Working Group, and our many colleagues who use and
-contribute to open-source projects in the Eclipse ecosystem.
-
-Finally, the development team is especially grateful to Barney Maccabe,
-David Pointer, and John Turner of ORNL for their
-endless support and advocacy for this work.
-
-This work has been supported by the US Department of Energy, Offices of
-Nuclear Energy (DOE-NE) and Energy Efficiency and Renewable Energy
-(DOE-EERE) and by the ORNL Undergraduate Research Participation
-Program, which is sponsored by ORNL and administered jointly by ORNL and
-the Oak Ridge Institute for Science and Education (ORISE). This work was
-also supported in part by the ORNL Director's
-Research and Development Fund. ORNL is managed by UT-Battelle, LLC, for
-the US Department of Energy under contract no. DE-AC05-00OR22725. ORISE
-is managed by Oak Ridge Associated Universities for the US Department of
-Energy under contract no. DE-AC05-00OR22750.
-
-\section*{Required Metadata}\label{required-metadata}
-\addcontentsline{toc}{section}{Required Metadata}
-
-\section*{Current Code Version}\label{current-code-version}
-\addcontentsline{toc}{section}{Current code version}
-
-See Table \ref{codeTable}.
-
-\begin{table}[H]
-\begin{tabularx}{\textwidth}{|l|X|X|}
-\hline
-C1 & Current code version & `next'\tabularnewline\hline
-C2 & Permanent link to code/repository used for this code version &
-\url{https://github.com/eclipse/ice/tree/next}
-\tabularnewline\hline
-C3 & Legal code license & Eclipse public license 1.0 \tabularnewline\hline
-C4 & Code versioning system used & Git \tabularnewline\hline
-C5 & Software code languages, tools, and services used & Java, OSGi, Eclipse RCP,
-and Maven \tabularnewline\hline
-C6 & Compilation requirements, operating environments and dependencies & Java 1.8 or greater, Maven, and
-an internet connection for dependencies \tabularnewline\hline 
-C7 & If available, link to developer documentation/manual &
-\url{https://wiki.eclipse.org/ICE} \tabularnewline\hline 
-C8 & Support email for questions & ice-dev@eclipse.org \tabularnewline\hline
-\end{tabularx}
-\caption{Current Code Version}
-\label{codeTable}
-\end{table}
-
-\section*{Current Executable Software
-Version}\label{current-executable-software-version}
-\addcontentsline{toc}{section}{Current Executable Software Version}
-
-See Table \ref{execTable}.
-
-\begin{table}[H]
-\begin{tabularx}{\textwidth}{|l|X|X|}
-\hline
-S1 & Current code version & 2.2.1 \tabularnewline\hline
-S2 & Permanent link to executables of this version &
-\url{https://www.eclipse.org/downloads/download.php?file=/ice/builds/2.2.1/}
- \tabularnewline\hline 
-S3 & Legal software license & Eclipse public license 1.0 \tabularnewline\hline
-S4 & Computing platforms/operating systems & Windows (32/64-bit), Mac OS/X,
-Linux (32/64-bit) \tabularnewline\hline 
-S5 & Installation requirements and dependencies & Java 1.8 or
-greater \tabularnewline\hline
-S6 & If available, link to user manual. If formally published, include a
-reference to the publication in the reference list &
-\url{https://wiki.eclipse.org/ICE} \tabularnewline\hline 
-S7 & Support email for questions & ice-users@eclipse.org \tabularnewline\hline
-\end{tabularx}
-\caption{Current Executable Software}
-\label{execTable}
-\end{table}

### 2019-07-24 src/ack.tex
Committing first draft of ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>
Added separate acknowledgements file.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
-\section{Acknowledgements}
-The authors are grateful for the assistance and support of the following people
-and institutions without which this work would not have been possible.
+The authors are grateful for the assistance and support of the following
+people and institutions without whom this work would not have been
+possible. This includes many people who directly contributed to the
+project, either in its early days as ``NiCE'' or once it moved to
+Eclipse, including Ronald Allen, Andrew Belt, David E.
+Bernholdt, Tim Bohn, Erica Grant, Mike Guidry, John M. Hetrick III, Forest Hull, 
+Sebastien Jourdain, JiSoo Kim, Allison Koenecke, Fangzhou Lin, Eric J. Lingerfelt, Greg
+Lyon, Tony McCrary, Elizabeth Piersall, Neeti
+Pokhriyal, Adrian Sanchez, Claire Saunders, Nick Stanish, Matthew Wang, and
+Scott Wittenberg. The support of both the Nuclear Energy Advanced Modeling and
+Simulation (NEAMS) and Consortium for Simulation of Light Water Reactors (CASL)
+programs is also greatly appreciated. The authors would like to acknowledge the
+special contribution of the Eclipse Foundation, the Eclipse Community, the
+Eclipse Science Working Group, and our many colleagues who use and contribute
+to open-source projects in the Eclipse ecosystem.
 
-\textbf{FIXME!}
+Finally, the development team is especially grateful to Barney Maccabe,
+David Pointer, and John Turner of ORNL for their
+endless support and advocacy for this work.
 
-This work has been supported by the US Department of Energy, Offices of Nuclear
-Energy (DOE-NE) and Energy Efficiency and Renewable Energy (DOE-EERE), and by
-the ORNL Undergraduate Research Participation Program, which is sponsored by
-ORNL and administered jointly by ORNL and the Oak Ridge Institute for Science
-and Education (ORISE). This work was also supported in part by the Oak Ridge
-National Laboratory Director's Research and Development Fund. ORNL is managed by
-UT-Battelle, LLC, for the US Department of Energy under contract no.
-DE-AC05-00OR22725. ORISE is managed by Oak Ridge Associated Universities for
-the US Department of Energy under contract no. DE-AC05-00OR22750.
-
-\textbf{LDRD ACK?!}
+This work has been supported by the DOE, Offices of
+Nuclear Energy (DOE-NE) and Energy Efficiency and Renewable Energy
+(DOE-EERE) and by the ORNL Undergraduate Research Participation
+Program, which is sponsored by ORNL and administered jointly by ORNL and
+the Oak Ridge Institute for Science and Education (ORISE). This work was
+also supported in part by the ORNL Laboratory Directed
+Research and Development Program. ORNL is managed by UT-Battelle LLC for under
+contract DE-AC05-00OR22725. ORISE is managed by Oak Ridge Associated
+Universities for the US Department of Energy under contract no.
+DE-AC05-00OR22750.

### 2019-07-28 src/conclusions.tex
Moved conclusions to separate file.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

--- 2019-07-23 src/content.tex
@@
-\section{Motivation and Significance}\label{motivation-and-significance}
-
-In previous work, Billings et al. interviewed modeling and simulation subject
-matter experts to compile a list of requirements for implementing and using
-these kinds of applications. In the process, they discovered that many of the
-difficulties inherent in using high-performance modeling and simulation
-software fall into five distinct categories \cite{billings_designing_2009}.
-These activities, detailed in Section \ref{workflow-model}, include (1)
-creating input, (2) executing jobs, (3) analyzing results, (4) managing data,
-and (5) modifying code. There are many tools that address these problems
-individually, but the same research found that the excess number and
-specialization of these tools also contribute to the learning curve.
-
-Previous efforts to address these five issues have resulted in general-purpose
-scientific workflow tools like Kepler \cite{ludascher_scientific_2006} or
-myopic tools that satisfy only a single set of requirements for a single piece
-of software or a single platform. These are opposite extremes, but a
-middle-of-the-road solution is also possible. A workflow engine could be
-developed that limits its scope to high-performance computing (HPC) and to the
-set of possible workflows associated with the five previously mentioned
-activities. With only minor additional development, a rich application
-programming interface (API) could be exposed so that highly customized
-solutions could still be made based on this limited workflow engine.
-
-It is not clear which, if any, of these solutions is better than the
-others, and practical requirements will ultimately dictate the path of a
-project's progress. This work considers a middle ground solution and
-presents the Eclipse Integrated Computational Environment (ICE) as proof
-that it is possible to create such a system. Specifically, the work
-described here shows that
-
-\begin{itemize}
-\item
-  modeling and simulation activities can be described in a succinct
-  workflow model (see \S \ref{workflow-model}),
-\item
-  an architecture for such a workflow system can satisfy the model of
-  workflows in an extensible way (see \S \ref{software-architecture}), and 
-\item
-  such a system is applicable to a suite of problems in energy science,
-  including virtual battery simulations and additive manufacturing, 
-  among others (see \S \ref{illustrative-examples}).
-\end{itemize}
-
-This section concludes with an introduction to the ICE workflow model. Section \ref{software-description} details the software
-from an architectural perspective, and Section \ref{illustrative-examples}
-provides a set of comprehensive examples. A
-presentation of the impact is included in Section \ref{impact}, and details on obtaining sample 
-code are provided in Section \ref{sample-code-tutorials-and-other-resources}.
-
-\subsection{Workflow Model}\label{workflow-model}
-
-ICE's workflow model is based on making it easier for scientists to create
-input, launch jobs, analyze results, manage data, and modify code. Many
-scientists would most likely find these activities difficult for all codes with
-which they lack experience, whereas with their own codes---or those with which
-they are most familiar---these tasks may be so simple that they are taken for
-granted. Any particular combination of these activities across one or more
-scientific software package or code results in a unique workflow. Such a
-workflow is normally, but not always, requested by a human user and
-orchestrated by a workflow management system.
-
-The most obvious workflow for any individual simulation code or
-collection of codes is to string the activities together, where the user's
-workflow is to create the input, launch the job, perform some analysis,
-and manage the data---possibly modifying the code in the process. However, 
-there are many other combinations, including re-running jobs with
-conditions or modifications or analyzing someone else's data.\footnote{The
-authors have identified many unique combinations that
-define workflow ``classes.'' When possible, every effort is made to give the
-classes colloquial names such as ``The Re-Run'' or ``The Graduate Student.''}
-
-\textbf{Creating input} is the process of describing the physical model
-or state of a system that will be simulated. This could include creating
-an input file(s) or making calls to an external process to configure a
-running program. In most situations, a computational scientist will
-modify existing input or create new input from a template. ``Input''
-generally includes run time parameters for the simulation framework
-(e.g., tolerances); configuration options (e.g., data locations, output
-locations, module configurations); properties of the materials to be
-simulated; and a discretization of the simulation space (e.g., mesh,
-grid, particle distribution). The collection of all required input can
-be quite large and can go by many names, including ``input set,''
-``input package,'' ``problem,'' or, simply, ``input.'' Often, the set of
-input files will be described in a ``main'' input file that acts as a
-kind of manifest to describe---and provide links to---all necessary
-information for a given problem.
-
-In this work, it should be assumed---unless otherwise noted---that
-``input'' refers to the entire set of input, not to a single file.
-
-\textbf{Executing jobs}, or ``running the workflow'' in this context, is
-the process of performing calculations using a simulation code or
-framework based on known variables from the input. These are typically run locally for small jobs or for development. Large
-simulations, on the other hand, typically require a large amount of
-hardware resources. These resources are usually off-site (i.e.,
-physically unavailable to the user) and are accessed remotely
-through Secure Shell (SSH) connections or similar protocols. Remote
-execution requires moving the input in advance of the execution and
-copying or moving the output to the user's machine. In many cases,
-though, the output is too large to move to the user's local machine.
-
-Local and remote jobs are often monitored to ascertain a job's status.
-This monitoring could be a simple check as to whether or not the execution
-has completed, or it could involve monitoring the output of individual
-quantities to examine the calculation state. The latter is often used to
-detect calculation errors that will result in incorrect results. If such
-problems are found, the job is typically cancelled (``killed'') to save
-compute resources and is then re-run later.
-
-Local jobs in ICE are executed using standard Java system calls. Remote jobs
-are launched only through SSH connections on remote machines. This includes
-direct SSH command execution on clusters and proxy connections through a pilot
-service on large leadership-class supercomputers. Services such as Globus GRAM
-and Bosco are not supported, but the SSH command execution includes extensive
-support for numerous batch and queuing systems. The Eclipse Parallel Tools
-Platform (PTP) is used to create all remote SSH connections, regardless of the
-target machine \cite{tibbitts_integrated_2009}.
-
-In this work, it should be assumed---unless otherwise noted---that
-``executing a job'' includes monitoring that job in one or more ways,
-possibly including real-time updates to visualizations. It is also important to
-note that executing a job is not the same as executing a workflow. Executing
-jobs specifically refers to launching simulations, whereas executing a workflow
-could be something different such as generating input or postprocessing
-results. This is an important distinction because ICE's workflows are all
-executed locally, but simulations and work can be distributed remotely
-depending on the implementation of the workflow plugin.
-
-\textbf{Analyzing results} includes executing special jobs to transform
-data in one or more prescribed ways and producing artifacts with
-scientific significance from the transformed data. This could include, for
-example, postprocessing results and visualizing the new data with
-dedicated visualization tools. For many types of scientific computing,
-this includes viewing the results of a simulation on a mesh or grid and
-extracting publication-quality images or movies from that data. Other
-cases might include analyzing results in preparation for follow-on
-simulations or performing feature extraction, classification, or
-activities for machine learning and data mining.
-
-Although this is similar to executing a job, it is distinctly
-different because the activity changes focus to satisfy the needs of a
-human operator. Simple data reduction, where the exact reduction is
-known, certainly qualifies as executing a job; however, analysis of
-modeling and simulation results is far from simple data reduction and is
-generally far more interactive for scientists.
-
-\textbf{Managing data} includes moving, copying, storing, sharing, or
-otherwise interacting with data for or from simulations. This activity
-is the most pervasive because each of the other activities requires
-interacting with data in some way. In many cases, though, data is still
-managed for its own purposes, without performing a simulation,
-generating new input, or analyzing results. Examples include archiving
-data, packaging data for publications, and updating values manually or through
-scripts (often in light of new information from publications).
-
-\textbf{Modifying code} is not typically considered a part of a
-scientific computing workflow. However, modeling and simulation use
-cases often require users to explicitly modify code before execution or to
-issue special build instructions. This is true, for example, with the
-computational fluid dynamics code Nek5000, which requires modification of code
-before compilation and special build instructions using the \textit{makenek}
-shell script \cite{the_nek5000_team_nek5000_2014}.
-Many scientists consider ``their workflow'' to be re-running
-software after modifications for purely exploratory purposes. This might
-be required if the model the author is modifying cannot be
-configured directly as part of the input but can be easily accomplished by
-manipulating the source code.
-
-\subsection{Related Work}\label{comparison-to-other-models}
-
-ICE's model of workflows differs significantly from many other
-efforts in workflow science because it defines workflows in terms of high-level
-activities that are meant to guide workflow implementers and users. Many other
-workflow models in the literature define a workflow as a collection of
-computing processes. For example, Yu and Buyya define grid workflows as ``a
-collection of tasks that are processed on distributed resources in a
-well-defined order to accomplish a specific goal'' \cite{yu_taxonomy_2005}.
-Others, such as Pizzi et al., subscribe to similar definitions
-\cite{pizzi_aiida:_2016}. This ``process'' view is acceptable where the
-workflow is static and does not require additional human input or ``human in
-the loop'' behavior after all the initial human input is provided. However,
-workflows within ICE are fully interactive with regular callbacks to humans. It
-is simpler to discuss ``activities'' than it is to create a distinction between
-``human processes'' and ``computer processes.'' Focusing on activities over
-processes (human or computer) also has the benefit of removing concrete
-elements such as hardware or software properties that distract from details of
-workflows and workflow management systems. That is, considerations such as
-memory usage and raw performance are important, but questions about the
-abstract workflow or what the workflow management system should do are far more
-important in this context.
-
-There are other workflow engines that have their own concepts of activities,
-with various similarities and differences compared with ICE's model. For
-example, Taverna has a concept of activities \cite{wolstencroft_taverna_2013}.
-Activities in Taverna are defined as invocable activities within a workflow,
-which is closely related to a lower-level class in ICE called Actions (see \S
-\ref{item}). On the other hand, ICE's activities loosely describe what can be
-done conceptually and the workflows that are implemented provide the Actions
-that carry out these activities.
-
-ICE and Taverna can both natively execute Java code, but ICE 2.0 cannot
-natively invoke Web Service Definition Language (WSDL) web services. ICE uses
-regular Java-based libraries to interact with web services, such as Jersey, and
-requires that developers write the code to do this directly. Shim services in
-Taverna are provided in ICE as separate services in the framework but are
-otherwise very similar.
-
-Chiron, an algebraic workflow engine, has a concept of activities that is
-closer to ICE's than Taverna's but still very strongly related to
-implementation \cite{ogasawara_chiron_2014}. Activities in Chiron are
-combinations of the program or expression to execute, plus the input schema,
-plus the output schema. This is a close match to the design of the Item class
-in ICE. ICE's Items (see Section \ref{item}) implement the high-level
-activities, such as launching a job or creating a model. The major difference
-between Chiron's activities and ICE's Items appears to be scope. A Chiron
-activity such as Map or Reduce would normally be implemented as an Action in
-ICE, whereas an Item in ICE can be tasked with executing multiple Actions to
-enact a workflow.
-
-One significant difference between ICE and many other systems is that it uses a
-language-based approach to defining workflows but with a standard language,
-Java, as opposed to a custom workflow definition language. Pizzi et al. do this
-with Aiida and Python, and the Fireworks Workflow Engine also uses Python. The
-advantage of this approach is that compilation is not a problem. ICE also
-differs from other workflow engines because it is specifically focused on
-modeling and simulation instead of grid workflows. Grid workflows are almost
-always defined as workflows based on trees without humans in the loop, but
-modeling and simulation workflows are much more interactive and undirected
-\cite{billings_toward_2017}.
-
-\section{Software Description}\label{software-description}
-
-ICE was specifically created to address hands-on workflows for scientists, as
-described in \S \ref{illustrative-examples}. Users download and execute ICE
-locally, and ICE in turn orchestrates local or remote workflows as required. It
-provides a comprehensive workbench for modeling and simulation that includes
-tools for workflows, visualization, data management, and software development.
-
-\subsection{Software Architecture}\label{software-architecture}
-
-\begin{figure}[htbp] \centering
-\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-1.jpg}
-\caption{High-level architecture of ICE showing the relationships and rough
-division of responsibility between the five primary components of ICE. The ICE
-Core is responsible for the workflow management and delegations instructions
-and data to the Item and data structures, respectively. User input is received
-from the client or through headless interactions, while persistence of large
-amounts of data is delegated to a persistence service. The ``1'' and ``*''
-represent the cardinality of the aggregation relationship.}
-\label{highlevel-arch}
-\end{figure}
-
-Workflows and tasks in ICE are not explicitly treated as trees or
-directed acyclic graphs (DAGS), as is common with grid workflow tools
-\cite{yu_taxonomy_2005}. Instead, ICE's design is inspired by representational
-state transfer (REST), and the workflow engine is implemented as services in an
-Eclipse Rich Client Platform (RCP) application
-\cite{fielding_architectural_2000} \cite{mcaffer_eclipse_2010}.
-
-Figure \ref{highlevel-arch} shows the five primary components of ICE and their
-relationships to each other. Users initiate requests to create, edit, update, or
-delete workflows from the ``ICE Client'' (the workbench) or through headless
-interactions using web or language programming interfaces. The list of available
-workflows that can be created is provided dynamically to the ICE Client by the
-``ICE Core,'' which acts as a server and is the primary component responsible
-for workflow orchestration. Workflow information is provided dynamically because
-it often changes at run time based on both the configuration of available
-workflow components in the registry and on persisted workflows users have
-saved in their workspace. Workflow task enactment and execution is performed by
-services called ``Items.'' Information about workflows is provided to the Client
-by the Core through common data structures rooted in a stateless ``Form'' tree.
-Forms describe the workflow and provide all the necessary information to
-understand \emph{what} should process the workflow (but not \emph{how} it should
-be processed). Once users modify the description of the workflow in the Form to
-provide their specific details, the Client dispatches a request to the Core to
-modify and/or process the workflow. The Core then uses the information from the
-Form to perform a service lookup to identify the correct Item to process the
-workflow.
-
-\subsubsection{ICE Core}
-
-\begin{figure}[htbp]
-\centering
-\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-2.jpg}
-\caption{Architecture of the ICE Core and its dependencies. The ICE Core class
-handles communications between workflow Items and common data structures but
-delegates construction of workflow Items to builders.}
-\label{core-arch}
-\end{figure}
-
-The primary purpose of the ICE Core is to orchestrate workflows and services for
-the platform. Figure \ref{core-arch} shows the primary classes that interact
-with the ICE Core. It is the ``core'' control component of ICE where all other
-component interactions converge. It is the middle tier of ICE's architecture and
-brokers communications between Items and Clients (graphical or not) by sharing
-Forms that contain workflow data. The ICE Core class delegates construction and
-management of Items to the Item Manager.
-
-The Item Manager acts as a container and factory for Items created by the ICE
-Core. Items are constructed using the Builder pattern, with concrete
-construction handled by realizations of the ItemBuilder interface.
-
-ICE 2.0 includes a graphical client based on the Eclipse Workbench, which is
-common for Eclipse applications. The workflow management capabilities of the
-core can be accessed through languages and a web-based programming interface as
-well (see Section \ref{framework}).
-
-\subsubsection{Items}
-\label{item}
-\label{item-states}
-
-\begin{figure}[htbp]
-\centering
-\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-3.jpg}
-\caption{The class hierarchy of ICE Items showing the relationships between the
-Item, its subclasses, and services that it uses. Vibe Launcher and MOOSE
-Launcher are examples of special Job Launch Items for executing jobs, and their
-applications are discussed in \S \ref{illustrative-examples}.}
-\label{item-arch}
-\end{figure}
-
-Each workflow Item in ICE is an independent service, and each workflow type is a
-subclass of the Item base class or another Item subclass. Items are registered
-dynamically through a service registry in ICE (see Section \ref{framework}) and
-provide collections of workflow data ---Forms--- for the ICE Core and Client.
-Since ICE's design is highly object oriented, it is easiest to think of the Item class
-as a description of an abstract workflow and an Item object (an instance of the
-class) as a concrete workflow with all required execution details specified in
-its Form.
-
-Figure \ref{item-arch} shows the class hierarchy of the Item class and its
-collaborators.
-Individual components of workflows (i.e., workflow ``tasks'' or ``nodes'') are
-either encoded directly in the workflow's subclass of Item or provided as
-``Actions'' that are dynamically registered with an ``Action Factory'' and
-obtained at run time. Common data structures that are shared across Items, the
-Client, and the Core are provided by the data structures component. Table 1
-describes the differences between Items, Actions, and Forms.\footnote{An
-upcoming update to the API will include the formal introduction of IWorkflow,
-IWorkflowTask, and IWorkflowEngine interfaces to bring ICE's API language closer
-to other systems such as Triquetrum. However, this must be done carefully to
-preserve backwards compatibility.}
-
-\begin{table*}[t]
-\begin{tabularx}{\textwidth}{|l|X|l|}
-\hline
-Class & Class Description & Object Description\tabularnewline\hline
-Item & Java class with code to execute an abstract workflow. Provides a
-Form. & Concrete workflow executor.\tabularnewline\hline
-Form & Description and template of the data needed for the Item to
-process the workflow. & User-modified workflow data.\tabularnewline\hline
-Action & Java class for executing a specific task in the workflow. Used
-by Items. & Concrete workflow task executor.\tabularnewline\hline
-\end{tabularx}
-\caption{Class descriptions for Items, Forms, and Actions.}
-\end{table*}
-
-Commonly used subclasses of Item include the Model and Job Launcher classes,
-which can be  used to create workflow plugins for input generation and workflow
-execution, respectively. Composite Items are special Items that are built of
-compositions of other Items. Composite Items are commonly used for workflow
-Items that can be executed in parallel or to tightly couple different workflow
-tasks for resource and performance management.
-
-All Items in ICE are finite state machines where the states represent
-the abstract state of the workflow. For example, when an Item is first
-created, it enters the ``Form Ready'' state to indicate that it could,
-in theory, be processed after a user reviews it. After that review, it
-enters the ``Ready to Process'' state before it is processed and 
-the ``Processed'' state after it is processed. There are several additional 
-states for errors.
-
-This design is very important. First, it means that all workflows in
-ICE, regardless of their actual details and functions, can behave only in
-a specific set of known and predictable ways, and this predictability 
-simplifies the way the Core manages and interacts with Items. Second, by
-formalizing state and error checks, ICE explicitly delineates which workflows 
-can be executed from those that must receive additional configuration. 
-Finally, it allows developers implementing Items and
-Actions to specify by contract what is required before proceeding to the
-next task, processing the workflow, or declaring a successful execution.
-
-\subsubsection{Data Structures}
-
-ICE contains a collection of common data structures that are useful for
-representing data needed modeling and simulation workflows. Figure
-\ref{data-arch} shows some of these classes and their relationship. All data
-structures (and Items) in ICE are uniquely identifiable and behave in
-predictable ways: they receive and dispatch updates, can be visited to determine
-type information, etc. \textit{Components} in the data sense, not the class
-sense, represent a special data structure that forms a child of a Form. Forms
-themselves are components and hierarchically aggregate other components.
-
-The name ``Component'' in the context of ICE's data structures refers to a
-unique and reusable collection of data, not a class or component in the object
-oriented sense. Components that hold data do very little of their own work but
-strongly scope the interfacial contract of their clients.
-
-\begin{figure}[htbp]
-\centering
-\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-4.jpg}
-\caption{Common data structures and their relationships in ICE.}
-\label{data-arch}
-\end{figure}
-
-\subsubsection{Persistence and
-Workspaces}\label{persistence-and-workspaces}
-
-When workflows are created and modified, ICE saves permanent copies of 
-Forms to disk in a special directory called a ``workspace.''
-Workspaces can contain projects, folders, and files, including data,
-code, input, and output. ICE automatically manages local and remote (or
-even local \emph{to} remote) transfers of data files when executing
-workflows if the files are detected in the same directory of the
-workspace as the workflow itself. For example, when executing a remote
-job, ICE will automatically move the input file if it is specified in
-the workflow and available in the project directory of the workspace.
-Likewise, if the output is small enough (less than 50 megabytes), ICE will
-automatically move it back to the local directory. By convention, all paths in
-ICE's Forms are relative to the workspace root path. Workspace directories are
-specified by the user and are fully functional Eclipse workspaces.
-
-ICE handles persistence using a ``persistence provider.'' The
-default persistence provider uses JAX-RS to write Forms to 
-XML~\cite{burke_restful_2010}. In principle, other persistence providers 
-could replace the XML-based provider since it is registered as a dynamic 
-service and a JAXP based provider has been used in the past.
-
-\subsubsection{Relationship to Other Eclipse Technologies}\label{framework}
-
-ICE is an Eclipse RCP application \cite{mcaffer_eclipse_2010} and has a plugin
-architecture based on Equinox, which is the reference implementation of the Open
-Service Gateway Initiative (OSGi) framework specification
-\cite{mcaffer_osgi_2010}. It is most appropriate to think of Eclipse ICE as an
-alternative flavor of any other Eclipse development environment because like
-those environments it is just a collection of Eclipse plugins with a
-well-defined purpose and brand. ICE uses more than 1,200 additional packages
-from the Eclipse ecosystem to provide services like language support and
-visualization. Each unique element of ICE described in this work---including the
-Client, Core, Items, and data structures---is provided as plugins to Equinox.
-Most plugins are managed dynamically and provided as services that can be
-obtained as dynamic OSGi Declarative Services. File input/output in ICE, with
-only a few exceptions, interacts with the RCP's Resources plugin and the
-standard Eclipse Workspace. This also includes remote resources that are
-managed with Eclipse PTP.
-
-ICE plugins are created using normal Eclipse development tools and are installed
-into either the running instance of ICE or published in a newly built version.
-In either case, the running platform of ICE can use only the plugins that are
-actually installed and at least a small amount of code must be written in Java
-for each plugin. This extension method may seem odd to the novice user or
-developer, especially if they do not know Java very well, but this design was
-chosen because it is an easy, fast, and precise way to create workflows.
-
-ICE provides built-in development tools to automatically generate empty but
-ready to compile classes (``stubs'') of plugins that can then be installed into
-the framework as services. These tools are based on other code generation tools
-in the Eclipse platform. This ``self-hosting'' makes it possible for new users
-to create complex, sophisticated workflows very quickly because they are not
-required to know how to interact with the framework. Development of new
-workflows is streamlined because ICE provides a rich API that exposes all
-workflow management functionality, documentation, tutorials, and tools to
-further simplify the process. These are shared through the self-hosted
-environment by code completion tools, help menus, and documentation overlays.
-The proximity of the workflow environment with the development platform
-for modeling and simulation codes is also beneficial because, as a self-hosted
-entity, workflows can be codeveloped with the code.
-
-ICE can be run as a headless web server with a remote service interface and a web
-API. The web API is also used as the primary means of providing real-time 
-feedback and monitoring support in ICE, and it is published as an OSGi service
-as well. These services can also be consumed as OSGi Remote Services.
-
-There are many situations where configuring workflows graphically or serially is
-unacceptable, such as when a very large number of workflows will be
-executed or the type of information required is very fine grained. In
-these cases, it is often necessary to provide scripts to the workflow
-management system. ICE includes the Eclipse Advanced Scripting
-Environment (EASE)~\cite{pontesegger_eclipse_2015} for scripting because it
-provides a way to script Eclipse RCP projects natively in Javascript,
-Jython, and Python. This also makes it possible to extend the
-environment by adding Items in these languages. Specifically, scripts in
-Javascript and Python are written and executed in simple shell that is part of
-the workbench. Calling other languages, such as C or Fortran, is typically
-accomplished by adding workflow Items for the executables in these languages
-and performing local workflow job launches. C language routines have been
-called from ICE through the Java Native Interface (JNI), but this is not a
-technique that is widely used with the platform because of its complexity.
-
-\subsection{Functionality}\label{software-functionalities}
-
-The most important function of ICE is to serve as an easily extended
-workflow management system for scientists in support of
-the activities described previously. In practice, it is most often used as a
-combination of workflow management system and development environment
-since it contains a significant amount of Eclipse's software development
-tooling in addition to the workflow tools. The project has many users,
-but it is most heavily used by the development team to support workflow
-science and software development for energy science projects. The
-development team regularly uses the platform to quickly deploy new
-domain-specific workbenches in a matter of hours for small collections
-of workflows that are easy to encode.
-
-Outside of the development team, ICE is commonly deployed as a sophisticated
-user environment for computational science projects (see Section \ref{impact})
-and as a visualization tool. The ICE source code originally contained a
-significant amount of visualization support, but at the request of users in the
-community, that support was ``spun off'' in early 2016 as the Eclipse Advanced
-Visualization Project (EAVP)~\cite{billings_eclipse_2015}.
-
-\section{Illustrative Examples}\label{illustrative-examples}
-
-The role that ICE plays as a workflow tool is best illustrated by the
-various ways in which it has been deployed, as shown in the following 
-examples.
-
-\subsection{Virtual Battery
-Simulations}\label{virtual-battery-simulations}
-
-Pannala et al. developed a Virtual Integrated Battery Environment (VIBE)
-as part of their research into safety and performance characteristics of
-lithium ion batteries \cite{pannala_multiscale_2015}. VIBE includes ICE
-as part of its distribution, and new workflows were added to ICE to enable users
-to add multiple types of input, configure the simulation software, and launch
-simulations of virtual batteries. Interactive 3D visualizations of the
-results were embedded in the launcher so that users can quickly find
-their results. Figure \ref{vibe} shows a (simulated) prismatic-cell battery's temperature
-distribution during discharge.
-
-\begin{figure}[htbp]
-\centering
-\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/vibe_20151016.png}
-\caption{ICE workbench for VIBE analysis.}
-\label{vibe}
-\end{figure}
-
-VIBE 1.0 is available as a virtual machine (for convenient deployment) in which the simulation
-software and ICE are provided side by side. The VIBE team's more recent 
-efforts for VIBE~1.1 include providing the simulation
-software in Docker containers so that users can download the latest,
-native version of ICE for their machine while simultaneously benefiting
-from a smaller virtual machine for the simulator.
-
-\subsection{Multiphysics Simulations with
-MOOSE}\label{multiphysics-simulations-with-moose}
-
-The MOOSE Framework is a powerful, easy-to-use multiphysics framework
-developed at Idaho National Laboratory \cite{gaston_moose:_2009}. ICE
-provides workflow tools for MOOSE as well as specialized class
-generation utilities for developing custom MOOSE kernels. Many of the
-MOOSE tools in ICE were developed closely with the MOOSE team to
-reproduce various aspects of MOOSE's user interface, known as ``Peacock.'' 
-Figure \ref{moose} shows an example of the ICE workbench for a simple structural mechanics
-problem solved using the MOOSE framework \cite{mccaskey_scientific_2015}.
-
-\begin{figure}[htbp]
-\centering
-\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ice-moose.png}
-\caption{ICE workbench for MOOSE workflows.}
-\label{moose}
-\end{figure}
-
-There are more than 300 MOOSE-based applications, and it is very easy to create
-new ones. The ICE development team uses ICE and MOOSE to quickly solve energy
-science problems with HPC resources and to deploy domain-specific workbenches.
-ICE provides features for automatic installation, configuration, and
-optimization of scientific development environments. In the context of MOOSE,
-ICE includes support for automatically downloading and building MOOSE from
-MOOSE's GitHub repository. This integration enables users to immediately begin
-developing complex multiphysics applications using the preinstalled Eclipse C
-Development Tools. Once the new MOOSE-based application is built, it will
-automatically work with the MOOSE workflow tools in ICE, although developers can
-also create customized workflow tools as needed.
-
-\subsection{Binder Jet Modeling}\label{binder-jet-modeling}
-
-Solid-state sintering of parts printed using binder jetting
-significantly increases part strength by decreasing the part porosity
-and eliminating voids. However, this process does cause the resulting
-product to shrink and warp from its original layout. An ideal near-net-shape 
-process would combine binder jetting with solid-state sintering and account
-for warpage and deformation in the part's design phase. 
-Figure \ref{binder} shows an ICE-based workbench for performing simulations of
-this process with visualizations of the pre- and postsimulation
-properties of a central body with eight cantilevers. The primary
-deformation in this type of geometry is bending or drooping of the
-cantilevers due to sintering and thermal creep.
-
-\begin{figure}[H]
-\centering
-\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ice-bjm.png}
-\caption{ICE workbench for binder jet modeling.}
-\label{binder}
-\end{figure}
-
-\subsection{Neutron Reflectivity}\label{neutron-reflectivity}
-
-ICE also includes a small utility for simulating neutron reflectivity and
-comparing the results with other data \cite{billings_brand_2015}. This 
-utility was developed in collaboration with a team at ORNL's Spallation Neutron 
-Source to replace an older utility that was originally written in Visual Basic and distributed via Excel macros. The new utility, developed in ICE, is shown in Figure \ref{reflectivity}.
-
-\begin{figure}[H]
-\centering
-\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/reflectivity-screenshot.png}
-\caption{ICE workbench for neutron reflectivity.}
-\label{reflectivity}
-\end{figure}
-
-\subsection{Quantum Computing}\label{quantum-computing}
-
-As quantum computing grows, the need for sophisticated
-software that can use quantum hardware or perform calculations on
-simulated quantum hardware becomes more pressing. Humble et al. created a simulator for
-adiabatic quantum computers where workflows were added to ICE to support
-interactions with the simulator and to process large sets of
-quadratic binary optimization problems \cite{humble_integrated_2014}. Figure \ref{jade} shows the workbench for this project.
-
-\begin{figure}[H]
-\centering
-\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/jaded.png}
-\caption{ICE workbench in the Jade Adiabatic Development Environment (JADE) for quantum computing simulations.}
-\label{jade}
-\end{figure}
-
-%ICE also supports other quantum computing projects, including the
-%eXtreme-scale ACCelerator (XACC) effort
-%\cite{mccaskey_ornl-qci/xacc_2016}. XACC is a programming framework for
-%extreme-scale, post-exascale accelerator architectures that can be
-%integrated alongside existing, conventional applications.
-
-\subsection{Nuclear Energy}\label{nuclear-energy}
-
-There are many examples of ICE's role in modeling and simulation
-projects for nuclear energy, but for an example of the level of
-customization that is possible in ICE, readers are referred to the work outlined in
-\cite{billings_domain-specific_2015}. Support for the ``Reactor
-Analyzer'' was dropped in ICE 2.1.8, but it demonstrated ICE's capability
-to integrate many different nuclear energy tools for complex analyses.
-
-\section{Impact}\label{impact}
-
-The impact of software tools like ICE is difficult to quantify. However, there
-are several examples of ICE significantly assisting the development team and
-others.
-
-One pressing area of interest and impact is that of interoperability
-between workflow systems. Significant prior efforts have been made to
-combine large workflow management systems (e.g., Mandal et al.
-\cite{mandal_integrating_2007}), but the end goal of gaining the greatest
-advantage by using the best capabilities from multiple systems remains unrealized.
-ICE's unique perspective on workflows and its well-defined API make it
-possible to integrate multiple systems in a straightforward way. This
-allows ICE to connect to other workflow environments, such as Triquetrum,
-quite easily \cite{brooks_introducing_2016}. Triquetrum, like Kepler in
-\cite{mandal_integrating_2007}, is a Ptolemy-based workflow engine
-\cite{brooks_triquetrum:_2015}.
-
-It is widely known that tools that enable researchers to be more productive tend
-to improve the pursuit of new research. The high extensibility of
-ICE and the tools that it combines from the larger Eclipse ecosystem
-have made it possible for researchers on the development team to quickly
-deploy new simulation environments for their research problems. Other tools created
-with ICE might not invent something radically new, but they tend to
-streamline interactions within those tools. Many ICE users, and certainly
-the development team, have experienced improvements in their software
-development efforts because of the tools that ICE provides or have learned
-new technologies because access to new tooling was as simple as
-installing more plugins through the Eclipse Marketplace.
-
-The ICE development team does not track ICE's user base, as useful as
-that would be, because of the extra work involved. However, various
-sources such as the VIBE mailing list, ICE's own mailing lists, and
-website download statistics suggest that ICE has been used by more than 350
-people at one time or another and currently has about 20
-``superusers,'' including the development team.
-
-A new cloud-based development tool based on ICE is under development by
-RNET Technologies, Inc., out of Dayton, Ohio, in response to a Small Business Innovation 
-Research award from the DOE. This web-based version of 
-ICE will continue ICE's support for nuclear energy and will integrate with cloud 
-computing solutions like Amazon Web Services and ORNL's Compute and Data
-Environment for Science (CADES). Additionally, although ICE has not directly led
-to any ``spin-off'' companies, ICE source code has been used
-in two spin-off projects: (1) EAVP (mentioned earlier) for advanced
-visualizations and (2) the Eclipse January project for scientific data
-structures \cite{graham_eclipse_2016}. ICE was also one of the founding
-projects of the Eclipse Science Working Group.
-
-Eclipse ICE is an open-source project, and the authors welcome and encourage
-engagement and contributions from users. Interested parties may inquire by
-contacting the corresponding author or visiting the ICE website.
-
-\section{Sample Code, Tutorials, and Other
-Resources}\label{sample-code-tutorials-and-other-resources}
-
-The primary resource for information on ICE is the project 
-website~\cite{billings_eclipse_2016}. The ``Resources'' menu includes links to
-detailed tutorials and user documentation. Examples of how to create
-new workflow Items are available at
-\url{https://github.com/eclipse/ice/tree/master/org.eclipse.ice.demo}.
-Examples of how to use the scripting engine are available at
-\url{https://github.com/eclipse/ice/tree/master/examples}. ICE also includes an
-extensive suite of unit, integration, and user interface tests, which are
-also excellent examples of how to work with the platform. Tutorial and
-demonstration videos are available on YouTube at \url{https://goo.gl/nxCzRD}.
-
-\section{Conclusions}\label{conclusions}
-
-Modeling and simulation workflows for scientists differ
-greatly from those of experimentalists or those who primarily interact with
-grid-based workflow management systems. The Eclipse ICE effort described here 
-has been used to address interdisciplinary problems in 
-modeling and simulation for energy science. Of particular interest are the
-differences in architecture between a workflow management system focused
-on modeling and simulation compared with systems focused on grids. ICE's broad
-applicability across many topics in energy science suggests
-there are opportunities for these systems in general. Finally, one 
-interesting avenue of future exploration is coupling or integrating ICE 
-with other workflow tools such as Aiida, Triquetrum, Kepler, and Pegasus,
-which would make it possible to combine the best of grid and modeling workflows and
+Modeling and simulation workflows for computational scientists differ greatly
+from those of experimentalists or those who primarily interact with grid-based workflow
+management systems. The Eclipse ICE effort described here has been used to
+address interdisciplinary problems in modeling and simulation for energy
+science. Of particular interest are the differences in architecture between a
+workflow management system focused on modeling and simulation compared with
+systems focused on grids. ICE's broad applicability across many topics in energy
+science suggests there are opportunities for these systems in general. Finally,
+one interesting avenue of future exploration is coupling or integrating ICE with
+other workflow tools such as Aiida, Triquetrum, Kepler, and Pegasus, which would
+make it possible to combine the best of grid and modeling workflows and
 simulation workflows to address greater challenges.

### 2019-07-28 src/content.tex
Moved conclusions to separate file.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 demonstration videos are available on YouTube at \url{https://goo.gl/nxCzRD}.
-
-\section{Conclusions}\label{conclusions}
-
-Modeling and simulation workflows for scientists differ
-greatly from those of experimentalists or those who primarily interact with
-grid-based workflow management systems. The Eclipse ICE effort described here 
-has been used to address interdisciplinary problems in 
-modeling and simulation for energy science. Of particular interest are the
-differences in architecture between a workflow management system focused
-on modeling and simulation compared with systems focused on grids. ICE's broad
-applicability across many topics in energy science suggests
-there are opportunities for these systems in general. Finally, one 
-interesting avenue of future exploration is coupling or integrating ICE 
-with other workflow tools such as Aiida, Triquetrum, Kepler, and Pegasus,
-which would make it possible to combine the best of grid and modeling workflows and
-simulation workflows to address greater challenges.

### 2019-07-31 src/content.tex
Fixed references.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 software fall into five distinct categories \cite{billings_designing_2009}.
-These activities, detailed in Section \ref{workflow-model}, include (1)
-creating input, (2) executing jobs, (3) analyzing results, (4) managing data,
-and (5) modifying code. There are many tools that address these problems
+These activities, detailed in Section \ref{workflow-model}, include (i)
+creating input, (ii) executing jobs, (iii) analyzing results, (iv) managing
+data, and (v) modifying code. There are many tools that address these problems
 individually, but the same research found that the excess number and
@@
 community, that support was ``spun off'' in early 2016 as the Eclipse Advanced
-Visualization Project (EAVP)~\cite{billings_eclipse_2015}.
+Visualization Project (EAVP) \cite{billings_eclipse_2015}.
 

### 2019-07-31 src/content.tex
Addressed spelling errors.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 detect calculation errors that will result in incorrect results. If such
-problems are found, the job is typically cancelled (``killed'') to save
+problems are found, the job is typically canceled (``killed'') to save
 compute resources and is then re-run later.
@@
 jobs specifically refers to launching simulations, whereas executing a workflow
-could be something different such as generating input or postprocessing
+could be something different such as generating input or post-processing
 results. This is an important distinction because ICE's workflows are all
@@
 Figure \ref{binder} shows an ICE-based workbench for performing simulations of
-this process with visualizations of the pre- and postsimulation
+this process with visualizations of the pre- and post-simulation
 properties of a central body with eight cantilevers. The primary

### 2019-08-06 src/content.tex
Addressed comments from Mike Guidry.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

@@
 others, and practical requirements will ultimately dictate the path of a
-project's progress. This work considers a middle ground solution and
+project's progress. This chapter considers a middle ground solution and
 presents the Eclipse Integrated Computational Environment (ICE) as proof
@@
 conditions or modifications or analyzing someone else's data.\footnote{The
-authors have identified many unique combinations that
+author has identified many unique combinations that
 define workflow ``classes.'' When possible, every effort is made to give the
@@
 
-Eclipse ICE is an open-source project, and the authors welcome and encourage
-engagement and contributions from users. Interested parties may inquire by
-contacting the corresponding author or visiting the ICE website.
-
 \section{Sample Code, Tutorials, and Other
